### 2020-08-01 paper/dcpo_gender_roles.Rmd
initial commit

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles"
thanks: "Corresponding author: [frederick-solt@uiowa.edu](mailto:frederick-solt@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:

abstract: ""
keywords: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
nocite: |
  @Solt2020a
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 300)

# If `DCPOtools` is not yet installed:
# remotes::install_github("fsolt/DCPOtools")

library(DCPOtools)
library(DCPO)
library(tidyverse)

set.seed(324)
```

# The Source Data

The first step towards remedying this problem is collecting the available public opinion data on gender egalitarian attitudes.

```{r dcpo_input_raw}
surveys_egr <- read_csv("data-raw/surveys_egr.csv", col_types = "cccc")[1:244,]

dcpo_input_raw <- DCPOtools::dcpo_setup(vars = surveys_egr,
                                        file = "data/dcpo_input_raw.csv")
```

```{r obs_by_item, echo=FALSE, fig.cap = "Items with the Most Observations in the Source Data \\label{items_by_obs}"}
dcpo_input_raw %>%
  distinct(country, year, item) %>%
  count(item) %>%
  arrange(desc(n)) %>% 
  head(12) %>% 
  ggplot(aes(forcats::fct_reorder(item, n, .desc = TRUE), n)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  theme(axis.title.x = element_blank() ) +
  ylab("Country-Year-Item Observations")

polileader4_cy <- dcpo_input_raw %>% filter(item == "polileader4") %>% distinct(country, year) %>% nrow()

polileader4_surveys <- dcpo_input_raw %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)

total_cy <- (max(dcpo_input_raw$year) - min(dcpo_input_raw$year))*(dcpo_input_raw %>% distinct(country) %>% nrow())

housewifefull4_cy <- dcpo_input_raw %>% filter(item == "housewifefull4") %>% distinct(country, year) %>% nrow()
```

The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
Employed by the Americas Barometer, the Arab Barometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
That this constitutes only `r sprintf("%2.1f", (polileader4_cy*100/total_cy))`% of the `r total_cy` total possible country-years covered underscores just how sparse the available public opinion data is on this topic.

```{r obs_by_country, echo=FALSE, fig.cap = "Countries with the Most Observations in the Source Data \\label{countries_by_obs}"}
dcpo_input_raw %>%
  mutate(country = if_else(stringr::str_detect(country, "United"),
                           stringr::str_replace(country, "((.).*) ((.).*)", "\\2.\\4."),
                           country)) %>% 
  distinct(country, year, item) %>% 
  count(country) %>%
  arrange(desc(n)) %>% 
  head(12) %>% 
  ggplot(aes(forcats::fct_reorder(country, n, .desc = TRUE), n)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  theme(axis.title.x = element_blank() ) +
  ylab("Country-Year-Item Observations")

# uk_nas <- {1 + max(swiid_source$year) - min(swiid_source$year) - 
# {swiid_source %>% filter(country == "United Kingdom") %>% pull(year) %>% unique() %>% length()}} %>%
# wordify_numeral()
# 
# iran_obs <- swiid_source %>% filter(country == "Iran") %>% pull(year) %>% unique() %>% length()
# 
# med_cy <- swiid_source %>% count(country, year) %>% count(country, name = "nn") %>% pull(nn) %>% median() %>% wordify_numeral()
```

```{r years_by_country, echo=FALSE, fig.cap="Country-Year Coverage in the Source Data \\label{countries_by_years}"}
library(patchwork)

dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
  with_min_yrs(2)

cby_plot <- dcpo_input_raw1 %>%
  mutate(country = if_else(stringr::str_detect(country, "United"),
                           stringr::str_replace(country, "((.).*) ((.).*)", "\\2.\\4."),
                           country)) %>% 
  distinct(country, year) %>%
  count(country) %>% 
  arrange(desc(n)) %>% 
  head(12) %>% 
  ggplot(aes(forcats::fct_reorder(country, n, .desc = TRUE), n)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  theme(axis.title.x = element_blank(),
        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
  ylab("Years Observed")

ybc_plot <- dcpo_input_raw1 %>%
  mutate(country = if_else(stringr::str_detect(country, "United"),
                           stringr::str_replace(country, "((.).*) ((.).*)", "\\2.\\4."),
                           country)) %>%
  distinct(country, year) %>%
  count(year, name = "nn") %>%
  ggplot(aes(year, nn)) +
  geom_line() +
  theme_bw() +
  scale_x_continuous(breaks = seq(1960, 2020, 10)) +
  theme(axis.title.x = element_blank(),
        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
  ylab("Countries Observed")

cby_plot + ybc_plot
```

```{r dcpo_input}
dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
  with_min_yrs(2)

dcpo_input <- DCPOtools::format_dcpo(dcpo_input_raw1,
                                     scale_q = "church_lb",
                                     scale_cp = 2)
save(dcpo_input, file = here::here("data", "dcpo_input.rda"))
```

# Estimating Gender Egalitarianism

The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].

```{r dcpo, eval=FALSE}
iter <- 3000

dcpo_output <- dcpo(dcpo_input,
                    iter = iter,
                    chains = 4,
                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))

save(dcpo_output, file = here::here("data", "dcpo_output.rda"))

dcpo_theta <- rstan::extract(dcpo_output, pars = "theta")

save(dcpo_theta, file = here::here("data", "dcpo_theta.rda"))

dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")

save(dcpo_input, dcpo_y_r_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
```

# Conclusion

\pagebreak

### 2020-08-01 paper/dcpo_gender_roles.Rmd
set up cache options; write up descriptives re surveys_egr; pivot plot axis text

@@
 
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 300)
+knitr::opts_chunk$set(cache = TRUE, echo = FALSE, fig.width=6.5, fig.height=2.5)
 
@@
 
-# The Source Data
+# The Source Data on Gender Egalitarian Attitudes
+
+```{r dcpo_input_raw, include=FALSE, cache.extra = tools::md5sum(here::here("data-raw", "surveys_egr.csv"))}
+surveys_egr <- read_csv(here::here("data-raw", "surveys_egr.csv"),
+                        col_types = "cccc")[1:244,]
+
+dcpo_input_raw <- DCPOtools::dcpo_setup(vars = surveys_egr,
+                                        datapath = here::here("..", "data", "dcpo_surveys"),
+                                        file = here::here("data", "dcpo_input_raw.csv"))
+
+n_surveys <- surveys_egr %>%
+  distinct(survey) %>% 
+  nrow()
+
+n_items <- surveys_egr %>%
+  distinct(item) %>% 
+  nrow()
+
+n_countries <- dcpo_input_raw %>%
+  distinct(country) %>% 
+  nrow()
+
+year_range <- paste(summary(dcpo_input_raw$year)[6]-summary(dcpo_input_raw$year)[1],
+                    "years, from",
+                    summary(dcpo_input_raw$year)[1],
+                    "to",
+                    summary(dcpo_input_raw$year)[6])
+
+```
 
 The first step towards remedying this problem is collecting the available public opinion data on gender egalitarian attitudes.
+We draw on data from `r n_surveys` survey datasets, in which we identified `r n_items` distinct relevant survey items.
+Together, these survey items were asked in `r n_countries` different countries over `r year_range`.
 
-```{r dcpo_input_raw}
-surveys_egr <- read_csv("data-raw/surveys_egr.csv", col_types = "cccc")[1:244,]
-
-dcpo_input_raw <- DCPOtools::dcpo_setup(vars = surveys_egr,
-                                        file = "data/dcpo_input_raw.csv")
-```
-
-```{r obs_by_item, echo=FALSE, fig.cap = "Items with the Most Observations in the Source Data \\label{items_by_obs}"}
+```{r obs_by_item, fig.cap = "Items with the Most Observations in the Source Data \\label{items_by_obs}"}
 dcpo_input_raw %>%
@@
   theme_bw() +
-  theme(axis.title.x = element_blank() ) +
+  theme(axis.title.x = element_blank(),
+        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
   ylab("Country-Year-Item Observations")
@@
 
+Figure&nbsp;\ref{items_by_obs} displays in how many country-years each of most-commonly asked items are available.
 The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
 Employed by the Americas Barometer, the Arab Barometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
-That this constitutes only `r sprintf("%2.1f", (polileader4_cy*100/total_cy))`% of the `r total_cy` total possible country-years covered underscores just how sparse the available public opinion data is on this topic.
+That this--again, which represents the _most common_ survey item--constitutes only `r sprintf("%2.1f", (polileader4_cy*100/total_cy))`% of the `r total_cy` total possible country-years covered underscores just how sparse the available public opinion data is on this topic.
 
-```{r obs_by_country, echo=FALSE, fig.cap = "Countries with the Most Observations in the Source Data \\label{countries_by_obs}"}
+Which countries are most data-rich?
+Figure&nbsp;\ref{countries_by_obs} below shows the dozen countries with the highest count of country-year-item observations.
+
+```{r obs_by_country, fig.cap = "Countries with the Most Observations in the Source Data \\label{countries_by_obs}"}
 dcpo_input_raw %>%
@@
 
-```{r years_by_country, echo=FALSE, fig.cap="Country-Year Coverage in the Source Data \\label{countries_by_years}"}
+```{r years_by_country, fig.cap="Country-Year Coverage in the Source Data \\label{countries_by_years}", cache.extra = tools::md5sum(here::here("data", "dcpo_input_raw.csv"))}
 library(patchwork)
 
-dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
+dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"),
+                            col_types = "cdcddcd") %>% 
   with_min_yrs(2)
@@
 ```{r dcpo_input}
-dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
-  with_min_yrs(2)
-
 dcpo_input <- DCPOtools::format_dcpo(dcpo_input_raw1,
-                                     scale_q = "church_lb",
+                                     scale_q = "polileader4",
                                      scale_cp = 2)

### 2020-08-02 paper/dcpo_gender_roles.Rmd
add bit on n_cyi

@@
                                         file = here::here("data", "dcpo_input_raw.csv"))
+```
 
+```{r egr_summary_stats}
 n_surveys <- surveys_egr %>%
@@
 
+n_cyi <- dcpo_input_raw %>% 
+  distinct(country, year, item) %>% 
+  nrow() %>% 
+  scales::comma()
 ```
@@
 We draw on data from `r n_surveys` survey datasets, in which we identified `r n_items` distinct relevant survey items.
-Together, these survey items were asked in `r n_countries` different countries over `r year_range`.
+Together, these survey items were asked in `r n_countries` different countries over `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
 
@@
 Employed by the Americas Barometer, the Arab Barometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
-That this--again, which represents the _most common_ survey item--constitutes only `r sprintf("%2.1f", (polileader4_cy*100/total_cy))`% of the `r total_cy` total possible country-years covered underscores just how sparse the available public opinion data is on this topic.
+That this constitutes only `r sprintf("%2.1f", (polileader4_cy*100/total_cy))`% of the `r total_cy` total possible country-years covered---and again, `polileader4` is the _most common_ survey item---underscores just how sparse the available public opinion data is on this topic.
 

### 2020-08-02 paper/dcpo_gender_roles.Rmd
more descriptives

@@
 
-year_range <- paste(summary(dcpo_input_raw$year)[6]-summary(dcpo_input_raw$year)[1],
-                    "years, from",
+n_years <- as.integer(summary(dcpo_input_raw$year)[6]-summary(dcpo_input_raw$year)[1])
+
+total_cy <- {n_countries * n_years} %>% 
+  scales::comma()
+
+year_range <- paste("from",
                     summary(dcpo_input_raw$year)[1],
@@
 We draw on data from `r n_surveys` survey datasets, in which we identified `r n_items` distinct relevant survey items.
-Together, these survey items were asked in `r n_countries` different countries over `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
+Together, these survey items were asked in `r n_countries` different countries over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
+Considering that observations for every year in each country surveyed would number `r total_cy` and so a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations, the available data is clearly very, very sparse.
 
@@
 
-total_cy <- (max(dcpo_input_raw$year) - min(dcpo_input_raw$year))*(dcpo_input_raw %>% distinct(country) %>% nrow())
-
 housewifefull4_cy <- dcpo_input_raw %>% filter(item == "housewifefull4") %>% distinct(country, year) %>% nrow()
@@
 Employed by the Americas Barometer, the Arab Barometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
-That this constitutes only `r sprintf("%2.1f", (polileader4_cy*100/total_cy))`% of the `r total_cy` total possible country-years covered---and again, `polileader4` is the _most common_ survey item---underscores just how sparse the available public opinion data is on this topic.
+That this constitutes only `r round(polileader4_cy*100/(n_countries * n_years))`% of the `r total_cy` total possible country-years covered---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.
 

### 2020-08-04 paper/dcpo_gender_roles.Rmd
include allbus and eb631; apply descriptives to dcpo_input_raw1 (2+ years per country; 5+ cy per item)

@@
 
-knitr::opts_chunk$set(cache = TRUE, echo = FALSE, fig.width=6.5, fig.height=2.5)
+knitr::opts_chunk$set(cache = TRUE, echo = FALSE, fig.width=6.5, fig.height=2.5, cache.extra = tools::md5sum(here::here("data", "dcpo_input_raw.csv")))
 
@@
 surveys_egr <- read_csv(here::here("data-raw", "surveys_egr.csv"),
-                        col_types = "cccc")[1:244,]
+                        col_types = "cccc")[1:308,]
 
@@
 ```{r egr_summary_stats}
+dcpo_input_raw1 <- dcpo_input_raw %>% 
+  with_min_yrs(2) %>% 
+  with_min_cy(5) %>% 
+  group_by(country) %>% 
+  mutate(cc_rank = n()) %>% 
+  ungroup() %>% 
+  arrange(-cc_rank)
+
 n_surveys <- surveys_egr %>%
@@
 
-n_items <- surveys_egr %>%
+n_items <- dcpo_input_raw1 %>%
   distinct(item) %>% 
@@
 
-n_countries <- dcpo_input_raw %>%
+n_countries <- dcpo_input_raw1 %>%
   distinct(country) %>% 
@@
 
-n_years <- as.integer(summary(dcpo_input_raw$year)[6]-summary(dcpo_input_raw$year)[1])
+n_years <- as.integer(summary(dcpo_input_raw1$year)[6]-summary(dcpo_input_raw1$year)[1])
 
@@
 year_range <- paste("from",
-                    summary(dcpo_input_raw$year)[1],
+                    summary(dcpo_input_raw1$year)[1],
                     "to",
-                    summary(dcpo_input_raw$year)[6])
+                    summary(dcpo_input_raw1$year)[6])
 
-n_cyi <- dcpo_input_raw %>% 
+n_cyi <- dcpo_input_raw1 %>% 
   distinct(country, year, item) %>% 
@@
 The first step towards remedying this problem is collecting the available public opinion data on gender egalitarian attitudes.
-We draw on data from `r n_surveys` survey datasets, in which we identified `r n_items` distinct relevant survey items.
-Together, these survey items were asked in `r n_countries` different countries over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
+We draw on data from `r n_surveys` survey datasets, in which we identified `r n_items` distinct relevant survey items that were asked in no fewer than five country-years.
+Together, these survey items were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
 Considering that observations for every year in each country surveyed would number `r total_cy` and so a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations, the available data is clearly very, very sparse.
@@
 ```{r obs_by_item, fig.cap = "Items with the Most Observations in the Source Data \\label{items_by_obs}"}
-dcpo_input_raw %>%
+dcpo_input_raw1 %>%
   distinct(country, year, item) %>%
@@
 
-Figure&nbsp;\ref{items_by_obs} displays in how many country-years each of most-commonly asked items are available.
+Figure&nbsp;\ref{items_by_obs} displays in how many country-years each of the twelve most-commonly asked items are available.
 The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
-Employed by the Americas Barometer, the Arab Barometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
+Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
 That this constitutes only `r round(polileader4_cy*100/(n_countries * n_years))`% of the `r total_cy` total possible country-years covered---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.
 
-Which countries are most data-rich?
+Which countries are the most data-rich?
 Figure&nbsp;\ref{countries_by_obs} below shows the dozen countries with the highest count of country-year-item observations.
@@
 ```{r obs_by_country, fig.cap = "Countries with the Most Observations in the Source Data \\label{countries_by_obs}"}
-dcpo_input_raw %>%
+dcpo_input_raw1 %>%
   mutate(country = if_else(stringr::str_detect(country, "United"),
@@
         axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
-  ylab("Country-Year-Item Observations")
+  ylab("Country-Years Observed")
 
@@
 
-```{r years_by_country, fig.cap="Country-Year Coverage in the Source Data \\label{countries_by_years}", cache.extra = tools::md5sum(here::here("data", "dcpo_input_raw.csv"))}
+```{r years_by_country, fig.cap="Country-Year Coverage in the Source Data \\label{countries_by_years}"}
 library(patchwork)
-
-dcpo_input_raw1 <- read_csv(here::here("data", "dcpo_input_raw.csv"),
-                            col_types = "cdcddcd") %>% 
-  with_min_yrs(2)
 
@@
   ggplot(aes(year, nn)) +
-  geom_line() +
+  geom_bar(stat = "identity") +
   theme_bw() +
-  scale_x_continuous(breaks = seq(1960, 2020, 10)) +
   theme(axis.title.x = element_blank(),

### 2020-08-05 paper/dcpo_gender_roles.Rmd
clean up
update

@@
 surveys_egr <- read_csv(here::here("data-raw", "surveys_egr.csv"),
-                        col_types = "cccc")[1:308,]
+                        col_types = "cccc")[1:354,]
 
@@
 
-```{r obs_by_item, fig.cap = "Items with the Most Observations in the Source Data \\label{items_by_obs}"}
+```{r obs_by_item, fig.height=3, fig.cap = "Items with the Most Observations in the Source Data \\label{items_by_obs}"}
 dcpo_input_raw1 %>%
@@
         axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
-  ylab("Country-Year-Item Observations")
+  ylab("Country-Years Observed")
 
-polileader4_cy <- dcpo_input_raw %>% filter(item == "polileader4") %>% distinct(country, year) %>% nrow()
+polileader4_cy <- dcpo_input_raw1 %>% filter(item == "polileader4") %>% distinct(country, year) %>% nrow()
 
-polileader4_surveys <- dcpo_input_raw %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)
+polileader4_surveys <- dcpo_input_raw1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)
 
-housewifefull4_cy <- dcpo_input_raw %>% filter(item == "housewifefull4") %>% distinct(country, year) %>% nrow()
+housewifefull4_cy <- dcpo_input_raw1 %>% filter(item == "housewifefull4") %>% distinct(country, year) %>% nrow()
 ```
@@
         axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
-  ylab("Country-Years Observed")
+  ylab("Year-Items Observed")
 
@@
                            stringr::str_replace(country, "((.).*) ((.).*)", "\\2.\\4."),
-                           country)) %>% 
+                           country),
+         country = stringr::str_replace(country, "South", "S.")) %>% 
   distinct(country, year) %>%
@@
 ybc_plot <- dcpo_input_raw1 %>%
-  mutate(country = if_else(stringr::str_detect(country, "United"),
-                           stringr::str_replace(country, "((.).*) ((.).*)", "\\2.\\4."),
-                           country)) %>%
   distinct(country, year) %>%
@@
 ```{r dcpo, eval=FALSE}
-iter <- 3000
+iter <- 4000
 
@@
 
+dcpo_sigma <- rstan::extract(dcpo_output, pars = "sigma")
+
+save(dcpo_theta, file = here::here("data", "dcpo_sigma.rda"))
+
 dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")

### 2020-08-07 paper/dcpo_gender_roles.Rmd
update

@@
 surveys_egr <- read_csv(here::here("data-raw", "surveys_egr.csv"),
-                        col_types = "cccc")[1:354,]
+                        col_types = "cccc")
 

### 2020-08-17 paper/dcpo_gender_roles.Rmd
add cs plot

@@
 
+```{r cs_plot, fig.cap="Egalitarian Gender Attitudes, 2020 \\label{cs_2020}", fig.height=8, warning=FALSE}
+load(here::here("data", "dcpo_input.rda"))
+load(here::here("data", "dcpo_output.rda"))
+
+theta_results <- DCPO::summarize_dcpo_results(dcpo_input,
+                                              dcpo_output,
+                                              "theta")
+
+sigma_results <- DCPO::summarize_dcpo_results(dcpo_input,
+                                              dcpo_output,
+                                              "sigma")
+
+p1_data <- theta_results %>%
+    group_by(country) %>%
+    top_n(1, year) %>%
+    ungroup() %>%
+    arrange(-mean) %>%
+    mutate(half = ntile(mean, 2))
+
+p1_data_a <- p1_data %>% filter(half==2) %>% mutate(ranked = as.factor(row_number(mean)))
+p1_data_b <- p1_data %>% filter(half==1) %>% mutate(ranked = as.factor(row_number(mean)))
+
+p1a <- ggplot(p1_data_a, aes(x = mean,
+                             y = ranked)) +
+    geom_segment(aes(x = `10%`, xend = `90%`,
+                     y = ranked, yend = as.factor(ranked)),
+                 na.rm = TRUE) +
+    geom_point(fill = "black", shape = 21, size = 1.1, na.rm = TRUE) +
+    theme_bw() + theme(legend.position="none",
+                       axis.text.x  = element_text(size=8),
+                       axis.text.y  = element_text(size=8),
+                       axis.title.x = element_text(face="bold", size=8),
+                       legend.text = element_text(size = 7),
+                       legend.title = element_text(size=7, face = "bold"),
+                       legend.key.size = unit(.5, "line"),
+                       legend.background = element_rect(linetype = "solid",
+                                                        color = "grey80",
+                                                        size = .25),
+                       legend.key = element_rect(colour = "white")) +
+    scale_y_discrete(breaks = p1_data_a$ranked, labels=p1_data_a$country) +
+    coord_cartesian(xlim=c(0, 1)) +
+    labs(x = NULL, y = NULL)
+
+p1b <- ggplot(p1_data_b, aes(x = mean,
+                             y = ranked)) +
+    geom_segment(aes(x = `10%`, xend = `90%`,
+                     y = ranked, yend = ranked),
+                 na.rm = TRUE) +
+    geom_point(fill = "black", shape = 21, size = 1.1, na.rm = TRUE) +
+    theme_bw() + theme(legend.position="none",
+                       axis.text.x  = element_text(size=8),
+                       axis.text.y  = element_text(size=8),
+                       axis.title.x = element_text(face="bold", size=8)) +
+    scale_y_discrete(breaks = p1_data_b$ranked, labels=p1_data_b$country) +
+    coord_cartesian(xlim=c(0, 1)) +
+    labs(x = NULL, y = NULL)
+
+p1a + p1b
+
+```
+
 # Conclusion

### 2020-08-30 paper/dcpo_gender_roles(Intro).Rmd
I add Intro portion to the previous rmd.

---

output:

  pdf_document:

    citation_package: natbib

    keep_tex: true

    fig_caption: true

    latex_engine: pdflatex

    template: svm-latex-ms2.tex

title: "[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles"

thanks: "Corresponding author: [frederick-solt@uiowa.edu](mailto:frederick-solt@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."

author:

abstract: ""

keywords: ""

date: "`r format(Sys.time(), '%B %d, %Y')`"

fontsize: 11pt

spacing: double

bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}

# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl

biblio-style: apsr

citecolor: black

linkcolor: black

endnote: no

header-includes:

      - \usepackage{array}

      - \usepackage{caption}

      - \usepackage{graphicx}

      - \usepackage{siunitx}

      - \usepackage{colortbl}

      - \usepackage{multirow}

      - \usepackage{hhline}

      - \usepackage{calc}

      - \usepackage{tabularx}

      - \usepackage{threeparttable}

      - \usepackage{wrapfig}

nocite: |

  @Solt2020a

---

```{r setup, include=FALSE}

options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(cache = TRUE, echo = FALSE, fig.width=6.5, fig.height=2.5, cache.extra = tools::md5sum(here::here("data", "dcpo_input_raw.csv")))

# If `DCPOtools` is not yet installed:

# remotes::install_github("fsolt/DCPOtools")

library(DCPOtools)

library(DCPO)

library(tidyverse)

set.seed(324)

```

#Introduction
Much of the comparative public opinion literature that does consider gender places its importance at the individual level. Such scholarship focuses on how men and women express significantly different opinions in various issue areas such as public policy preferences [@kellstedt2010macro], the use of military force [@brooks2011war; @eichenberg2016gender], and female political leadership [@badas2019michelle] to name a few. While such research has produced interesting and important findings by asking how gender affects public opinion, it ignores a second equally relevant piece of the puzzle that our data is better equipped to address – that is, how does public opinion affect gender? This analytical reframing is important, because without it, the literature loses sight of gender as not only a variable indicating part of an individual’s identity, but also as a macrolevel process that groups of people produce, experience, and challenge as part of their political lives. By measuring cross-national time-variant attitudes toward gender egalitarianism, our data positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender.
Gender egalitarian attitudes have been grown over decades not only in developed countries but also in developing societies [@boehnke2011gender]. With the affluent variance in the gender egalitarian attitudes around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants. For example, the association between gender egalitarian attitudes and women’s political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women’s descriptive representation in parliaments [@paxton2003women] have been examined. However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes. Very few cross-national time-series measures of gender egalitarianism exist and there is no consensus on the measures. Even though a gender egalitarian index developed by @mcdaniel2008measuring  exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004.
The newly developed gender egalitarian index enables scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, build new theories with the preliminary statistical analysis, etc. As the very first step, the index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors. Also, we can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public’s views on the gender role. Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women’s mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women] with our index. Further, the broad time span of our index enables scholars to test causality and the direction of the relationship.
	One example of how our data might be used to investigate these macrolevel processes is researching how public opinion regarding gender roles affects the makeup of national militaries. The comparative public opinion literature has completely neglected this connection, despite scholarly interest in how public opinion affects policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], the relationship between public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and how gender affects public opinion toward military actions [@brooks2011war; @eichenberg2016gender; @lizotte2017gender]. If there exists a strong correlation between countries that largely hold traditionalist views toward gender roles and countries that exclude women from participating in the state military, then this would support a theory that national military policies tend to be congruent with public opinion. One could theorize that this is because of incentive structures military policy-makers face, and perhaps the level of congruence between public opinion and military policy is conditioned by other factors such as regime type. 
However, it would be just as interesting to discover that there is no correlation between public opinion on gender roles and women’s inclusion/exclusion from state militaries. If the countries with largely egalitarian views toward gender roles are no more likely to incorporate women into the national military than more traditionalist countries, then this would reveal important patterns in the gendered makeup of national militaries. Perhaps these typically male-dominated institutions have shifted over time from being male-dominated as a norm to being male-dominated as an active resistance to public demands for change – in which case, national militaries have developed an identity as not just masculine institutions, but as preservers of traditional masculinity. Regardless of what results might unfold from this avenue of research, using our data on attitudes toward gender egalitarianism to test theories regarding macroprocesses of gender will help move the comparative public opinion literature beyond just identifying how male and female survey respondents differ from one another.

# The Source Data on Gender Egalitarian Attitudes

```{r dcpo_input_raw, include=FALSE, cache.extra = tools::md5sum(here::here("data-raw", "surveys_egr.csv"))}

surveys_egr <- read_csv(here::here("data-raw", "surveys_egr.csv"),

                        col_types = "cccc")

dcpo_input_raw <- DCPOtools::dcpo_setup(vars = surveys_egr,

                                        datapath = here::here("..", "data", "dcpo_surveys"),

                                        file = here::here("data", "dcpo_input_raw.csv"))

```

```{r egr_summary_stats}

dcpo_input_raw1 <- dcpo_input_raw %>%

  with_min_yrs(2) %>%

  with_min_cy(5) %>%

  group_by(country) %>%

  mutate(cc_rank = n()) %>%

  ungroup() %>%

  arrange(-cc_rank)

n_surveys <- surveys_egr %>%

  distinct(survey) %>%

  nrow()

n_items <- dcpo_input_raw1 %>%

  distinct(item) %>%

  nrow()

n_countries <- dcpo_input_raw1 %>%

  distinct(country) %>%

  nrow()

n_years <- as.integer(summary(dcpo_input_raw1$year)[6]-summary(dcpo_input_raw1$year)[1])

total_cy <- {n_countries * n_years} %>%

  scales::comma()

year_range <- paste("from",

                    summary(dcpo_input_raw1$year)[1],

                    "to",

                    summary(dcpo_input_raw1$year)[6])

n_cyi <- dcpo_input_raw1 %>%

  distinct(country, year, item) %>%

  nrow() %>%

  scales::comma()

```

The first step towards remedying this problem is collecting the available public opinion data on gender egalitarian attitudes.

We draw on data from `r n_surveys` survey datasets, in which we identified `r n_items` distinct relevant survey items that were asked in no fewer than five country-years.

Together, these survey items were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.

Considering that observations for every year in each country surveyed would number `r total_cy` and so a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations, the available data is clearly very, very sparse.

```{r obs_by_item, fig.height=3, fig.cap = "Items with the Most Observations in the Source Data \\label{items_by_obs}"}

dcpo_input_raw1 %>%

  distinct(country, year, item) %>%

  count(item) %>%

  arrange(desc(n)) %>%

  head(12) %>%

  ggplot(aes(forcats::fct_reorder(item, n, .desc = TRUE), n)) +

  geom_bar(stat = "identity") +

  theme_bw() +

  theme(axis.title.x = element_blank(),

        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +

  ylab("Country-Years Observed")

polileader4_cy <- dcpo_input_raw1 %>% filter(item == "polileader4") %>% distinct(country, year) %>% nrow()

polileader4_surveys <- dcpo_input_raw1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)

housewifefull4_cy <- dcpo_input_raw1 %>% filter(item == "housewifefull4") %>% distinct(country, year) %>% nrow()

```

Figure&nbsp;\ref{items_by_obs} displays in how many country-years each of the twelve most-commonly asked items are available.

The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.

Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.

That this constitutes only `r round(polileader4_cy*100/(n_countries * n_years))`% of the `r total_cy` total possible country-years covered---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.

Which countries are the most data-rich?

Figure&nbsp;\ref{countries_by_obs} below shows the dozen countries with the highest count of country-year-item observations.

```{r obs_by_country, fig.cap = "Countries with the Most Observations in the Source Data \\label{countries_by_obs}"}

dcpo_input_raw1 %>%

  mutate(country = if_else(stringr::str_detect(country, "United"),

                           stringr::str_replace(country, "((.).*) ((.).*)", "\\2.\\4."),

                           country)) %>%

  distinct(country, year, item) %>%

  count(country) %>%

  arrange(desc(n)) %>%

  head(12) %>%

  ggplot(aes(forcats::fct_reorder(country, n, .desc = TRUE), n)) +

  geom_bar(stat = "identity") +

  theme_bw() +

  theme(axis.title.x = element_blank(),

        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +

  ylab("Year-Items Observed")

# uk_nas <- {1 + max(swiid_source$year) - min(swiid_source$year) -

# {swiid_source %>% filter(country == "United Kingdom") %>% pull(year) %>% unique() %>% length()}} %>%

# wordify_numeral()

#

# iran_obs <- swiid_source %>% filter(country == "Iran") %>% pull(year) %>% unique() %>% length()

#

# med_cy <- swiid_source %>% count(country, year) %>% count(country, name = "nn") %>% pull(nn) %>% median() %>% wordify_numeral()

```

```{r years_by_country, fig.cap="Country-Year Coverage in the Source Data \\label{countries_by_years}"}

library(patchwork)

cby_plot <- dcpo_input_raw1 %>%

  mutate(country = if_else(stringr::str_detect(country, "United"),

                           stringr::str_replace(country, "((.).*) ((.).*)", "\\2.\\4."),

                           country),

         country = stringr::str_replace(country, "South", "S.")) %>%

  distinct(country, year) %>%

  count(country) %>%

  arrange(desc(n)) %>%

  head(12) %>%

  ggplot(aes(forcats::fct_reorder(country, n, .desc = TRUE), n)) +

  geom_bar(stat = "identity") +

  theme_bw() +

  theme(axis.title.x = element_blank(),

        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +

  ylab("Years Observed")

ybc_plot <- dcpo_input_raw1 %>%

  distinct(country, year) %>%

  count(year, name = "nn") %>%

  ggplot(aes(year, nn)) +

  geom_bar(stat = "identity") +

  theme_bw() +

  theme(axis.title.x = element_blank(),

        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +

  ylab("Countries Observed")

cby_plot + ybc_plot

```

```{r dcpo_input}

dcpo_input <- DCPOtools::format_dcpo(dcpo_input_raw1,

                                     scale_q = "polileader4",

                                     scale_cp = 2)

save(dcpo_input, file = here::here("data", "dcpo_input.rda"))

```

# Estimating Gender Egalitarianism

The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].

```{r dcpo, eval=FALSE}

iter <- 4000

dcpo_output <- dcpo(dcpo_input,

                    iter = iter,

                    chains = 4,

                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total

                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))

save(dcpo_output, file = here::here("data", "dcpo_output.rda"))

dcpo_theta <- rstan::extract(dcpo_output, pars = "theta")

save(dcpo_theta, file = here::here("data", "dcpo_theta.rda"))

dcpo_sigma <- rstan::extract(dcpo_output, pars = "sigma")

save(dcpo_theta, file = here::here("data", "dcpo_sigma.rda"))

dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")

save(dcpo_input, dcpo_y_r_pred, file = here::here("data", "dcpo_y_r_pred.rda"))

```

```{r cs_plot, fig.cap="Egalitarian Gender Attitudes, 2020 \\label{cs_2020}", fig.height=8, warning=FALSE}

load(here::here("data", "dcpo_input.rda"))

load(here::here("data", "dcpo_output.rda"))

theta_results <- DCPO::summarize_dcpo_results(dcpo_input,

                                              dcpo_output,

                                              "theta")

sigma_results <- DCPO::summarize_dcpo_results(dcpo_input,

                                              dcpo_output,

                                              "sigma")

p1_data <- theta_results %>%

    group_by(country) %>%

    top_n(1, year) %>%

    ungroup() %>%

    arrange(-mean) %>%

    mutate(half = ntile(mean, 2))

p1_data_a <- p1_data %>% filter(half==2) %>% mutate(ranked = as.factor(row_number(mean)))

p1_data_b <- p1_data %>% filter(half==1) %>% mutate(ranked = as.factor(row_number(mean)))

p1a <- ggplot(p1_data_a, aes(x = mean,

                             y = ranked)) +

    geom_segment(aes(x = `10%`, xend = `90%`,

                     y = ranked, yend = as.factor(ranked)),

                 na.rm = TRUE) +

    geom_point(fill = "black", shape = 21, size = 1.1, na.rm = TRUE) +

    theme_bw() + theme(legend.position="none",

                       axis.text.x  = element_text(size=8),

                       axis.text.y  = element_text(size=8),

                       axis.title.x = element_text(face="bold", size=8),

                       legend.text = element_text(size = 7),

                       legend.title = element_text(size=7, face = "bold"),

                       legend.key.size = unit(.5, "line"),

                       legend.background = element_rect(linetype = "solid",

                                                        color = "grey80",

                                                        size = .25),

                       legend.key = element_rect(colour = "white")) +

    scale_y_discrete(breaks = p1_data_a$ranked, labels=p1_data_a$country) +

    coord_cartesian(xlim=c(0, 1)) +

    labs(x = NULL, y = NULL)

p1b <- ggplot(p1_data_b, aes(x = mean,

                             y = ranked)) +

    geom_segment(aes(x = `10%`, xend = `90%`,

                     y = ranked, yend = ranked),

                 na.rm = TRUE) +

    geom_point(fill = "black", shape = 21, size = 1.1, na.rm = TRUE) +

    theme_bw() + theme(legend.position="none",

                       axis.text.x  = element_text(size=8),

                       axis.text.y  = element_text(size=8),

                       axis.title.x = element_text(face="bold", size=8)) +

    scale_y_discrete(breaks = p1_data_b$ranked, labels=p1_data_b$country) +

    coord_cartesian(xlim=c(0, 1)) +

    labs(x = NULL, y = NULL)

p1a + p1b

```

# Conclusion

\pagebreak

### 2020-09-06 paper/dcpo_gender_roles(Intro).Rmd
Update dcpo_gender_roles(Intro).Rmd

@@
 ---
-
+title: '[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward
+  Egalitarian Gender Roles'
+author: "null"
+date: "`r format(Sys.time(), '%B %d, %Y')`"
 output:
-
+  word_document: default
   pdf_document:
-
     citation_package: natbib
-
-    keep_tex: true
-
-    fig_caption: true
-
+    fig_caption: yes
+    keep_tex: yes
     latex_engine: pdflatex
-
     template: svm-latex-ms2.tex
-
-title: "[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles"
-
-thanks: "Corresponding author: [frederick-solt@uiowa.edu](mailto:frederick-solt@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
-
-author:
-
-abstract: ""
-
-keywords: ""
-
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-
+citecolor: black
+biblio-style: apsr
+endnote: no
 fontsize: 11pt
-
+header-includes:
+- \usepackage{array}
+- \usepackage{caption}
+- \usepackage{graphicx}
+- \usepackage{siunitx}
+- \usepackage{colortbl}
+- \usepackage{multirow}
+- \usepackage{hhline}
+- \usepackage{calc}
+- \usepackage{tabularx}
+- \usepackage{threeparttable}
+- \usepackage{wrapfig}
+keywords: ''
+linkcolor: black
+nocite: |2
+  @Solt2020a
+bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive
+  = TRUE))`}
 spacing: double
-
-bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
-
-# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
-
-biblio-style: apsr
-
-citecolor: black
-
-linkcolor: black
-
-endnote: no
-
-header-includes:
-
-      - \usepackage{array}
-
-      - \usepackage{caption}
-
-      - \usepackage{graphicx}
-
-      - \usepackage{siunitx}
-
-      - \usepackage{colortbl}
-
-      - \usepackage{multirow}
-
-      - \usepackage{hhline}
-
-      - \usepackage{calc}
-
-      - \usepackage{tabularx}
-
-      - \usepackage{threeparttable}
-
-      - \usepackage{wrapfig}
-
-nocite: |
-
-  @Solt2020a
-
+thanks: 'Corresponding author: [frederick-solt@uiowa.edu](mailto:frederick-solt@uiowa.edu).  Current
+  version: `r format(Sys.time(), ''%B %d, %Y'')`.'
+abstract: ''
 ---
@@
 #Introduction
-Much of the comparative public opinion literature that does consider gender places its importance at the individual level.
-Such scholarship focuses on how men and women express significantly different opinions in various issue areas such as public policy preferences [@kellstedt2010macro], the use of military force [@brooks2011war; @eichenberg2016gender], and female political leadership [@badas2019michelle] to name a few.
-While such research has produced interesting and important findings by asking how gender affects public opinion, it ignores a second equally relevant piece of the puzzle that our data is better equipped to address – that is, how does public opinion affect gender?
-This analytical reframing is important, because without it, the literature loses sight of gender as not only a variable indicating part of an individual’s identity, but also as a macrolevel process that groups of people produce, experience, and challenge as part of their political lives.
-By measuring cross-national time-variant attitudes toward gender egalitarianism, our data positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender.
-Gender egalitarian attitudes have been grown over decades not only in developed countries but also in developing societies [@boehnke2011gender].
-With the affluent variance in the gender egalitarian attitudes around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants.
-For example, the association between gender egalitarian attitudes and women’s political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women’s descriptive representation in parliaments [@paxton2003women] have been examined.
+
+Gender egalitarian attitude has been grown over the decades not only in developed countries but also in developing societies [@boehnke2011gender].
+With the affluent variance in the gender egalitarian attitude around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants.
+For example, the association between gender egalitarian attitudes and women's political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women's descriptive representation in parliaments [@paxton2003women] have been examined.
 However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes.
@@
 Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004.
-The newly developed gender egalitarian index enables scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, build new theories with the preliminary statistical analysis, etc.
-As the very first step, the index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors.
-Also, we can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public’s views on the gender role.
-Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women’s mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women] with our index.
-Further, the broad time span of our index enables scholars to test causality and the direction of the relationship.
-	One example of how our data might be used to investigate these macrolevel processes is researching how public opinion regarding gender roles affects the makeup of national militaries.
-The comparative public opinion literature has completely neglected this connection, despite scholarly interest in how public opinion affects policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], the relationship between public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and how gender affects public opinion toward military actions [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
-If there exists a strong correlation between countries that largely hold traditionalist views toward gender roles and countries that exclude women from participating in the state military, then this would support a theory that national military policies tend to be congruent with public opinion.
-One could theorize that this is because of incentive structures military policy-makers face, and perhaps the level of congruence between public opinion and military policy is conditioned by other factors such as regime type.
-However, it would be just as interesting to discover that there is no correlation between public opinion on gender roles and women’s inclusion/exclusion from state militaries.
-If the countries with largely egalitarian views toward gender roles are no more likely to incorporate women into the national military than more traditionalist countries, then this would reveal important patterns in the gendered makeup of national militaries.
-Perhaps these typically male-dominated institutions have shifted over time from being male-dominated as a norm to being male-dominated as an active resistance to public demands for change – in which case, national militaries have developed an identity as not just masculine institutions, but as preservers of traditional masculinity.
-Regardless of what results might unfold from this avenue of research, using our data on attitudes toward gender egalitarianism to test theories regarding macroprocesses of gender will help move the comparative public opinion literature beyond just identifying how male and female survey respondents differ from one another.
+
+  To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view through the DCPO package for R [@Solt2020a].
+(Quick Review of our Index can be included).
+
+  The newly developed gender egalitarian index enables scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
+The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors.
+We also can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public opinion on the gender role.
+Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women].
+Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
+
+  This article proceeds with the following order. (Brief summaries about the rest of sections will be provided)
 
@@
 
-Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
+Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobar처metro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
 

### 2020-09-25 paper/dcpo_gender_roles.Rmd
add separate dcpo_input_raw_*.csv for each classification; add dcpo_input_public.rda

@@
 ```{r dcpo_input_raw, include=FALSE, cache.extra = tools::md5sum(here::here("data-raw", "surveys_egr.csv"))}
-surveys_egr <- read_csv(here::here("data-raw", "surveys_egr.csv"),
-                        col_types = "cccc")
+surveys_egr <- read_csv(here::here("data-raw", "surveys_egr_classification.csv"),
+                        col_types = "ccccnnn")
 
-dcpo_input_raw <- DCPOtools::dcpo_setup(vars = surveys_egr,
-                                        datapath = here::here("..", "data", "dcpo_surveys"),
-                                        file = here::here("data", "dcpo_input_raw.csv"))
+surveys_egr_public <- surveys_egr %>% 
+  filter(agreed == 1)
+
+surveys_egr_private <- surveys_egr %>% 
+  filter(agreed == 2)
+
+surveys_egr_balance <- surveys_egr %>% 
+  filter(agreed == 3)
+
+surveys_egr_dominance <- surveys_egr %>% 
+  filter(agreed == 4)
+
+dcpo_input_raw_public <- DCPOtools::dcpo_setup(vars = surveys_egr_public,
+                                               datapath = here::here("..",
+                                                                     "data", "dcpo_surveys"),
+                                               file = here::here("data",
+                                                                 "dcpo_input_raw_public.csv"))
+
+dcpo_input_raw_private <- DCPOtools::dcpo_setup(vars = surveys_egr_private,
+                                               datapath = here::here("..",
+                                                                     "data", "dcpo_surveys"),
+                                               file = here::here("data",
+                                                                 "dcpo_input_raw_private.csv"))
+
+dcpo_input_raw_balance <- DCPOtools::dcpo_setup(vars = surveys_egr_balance,
+                                               datapath = here::here("..",
+                                                                     "data", "dcpo_surveys"),
+                                               file = here::here("data",
+                                                                 "dcpo_input_raw_balance.csv"))
+
+dcpo_input_raw_dominance <- DCPOtools::dcpo_setup(vars = surveys_egr_dominance,
+                                               datapath = here::here("..",
+                                                                     "data", "dcpo_surveys"),
+                                               file = here::here("data",
+                                                                 "dcpo_input_raw_dominance.csv"))
 ```
@@
 ```{r egr_summary_stats}
-dcpo_input_raw1 <- dcpo_input_raw %>% 
+dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"))
+
+process_dcpo_input_raw <- function(dcpo_input_raw_df) {
+  dcpo_input_raw_df %>% 
   with_min_yrs(2) %>% 
@@
   arrange(-cc_rank)
+}
+
+dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public)
+dcpo_input_raw_private1 <- process_dcpo_input_raw(dcpo_input_raw_private)
+dcpo_input_raw_balance1 <- process_dcpo_input_raw(dcpo_input_raw_balance)
+dcpo_input_raw_dominance1 <- process_dcpo_input_raw(dcpo_input_raw_dominance)
 
@@
 
-```{r dcpo_input}
-dcpo_input <- DCPOtools::format_dcpo(dcpo_input_raw1,
+```{r dcpo_input_public}
+dcpo_input_public <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
                                             scale_q = "polileader4",
                                             scale_cp = 2)
-save(dcpo_input, file = here::here("data", "dcpo_input.rda"))
+save(dcpo_input_public, file = here::here("data", "dcpo_input_public.rda"))
 ```

### 2020-09-29 paper/dcpo_gender_roles.Rmd
update using dcpo_input_raw_public

@@
 spacing: double
-bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
+bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "s.bib$", recursive = TRUE))`}
 # csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
@@
 ```{r egr_summary_stats}
-dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"))
+dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
+                                  col_types = "cdcddcd")
 
@@
 
-n_items <- dcpo_input_raw1 %>%
+n_items <- dcpo_input_raw_public1 %>%
   distinct(item) %>% 
@@
 
-n_countries <- dcpo_input_raw1 %>%
+n_countries <- dcpo_input_raw_public1 %>%
   distinct(country) %>% 
@@
 
-n_years <- as.integer(summary(dcpo_input_raw1$year)[6]-summary(dcpo_input_raw1$year)[1])
+n_years <- as.integer(summary(dcpo_input_raw_public1$year)[6]-summary(dcpo_input_raw_public1$year)[1])
 
@@
 year_range <- paste("from",
-                    summary(dcpo_input_raw1$year)[1],
+                    summary(dcpo_input_raw_public1$year)[1],
                     "to",
-                    summary(dcpo_input_raw1$year)[6])
+                    summary(dcpo_input_raw_public1$year)[6])
 
-n_cyi <- dcpo_input_raw1 %>% 
+n_cyi <- dcpo_input_raw_public1 %>% 
   distinct(country, year, item) %>% 
@@
 ```{r obs_by_item, fig.height=3, fig.cap = "Items with the Most Observations in the Source Data \\label{items_by_obs}"}
-dcpo_input_raw1 %>%
+dcpo_input_raw_public1 %>%
   distinct(country, year, item) %>%
@@
 
-polileader4_cy <- dcpo_input_raw1 %>% filter(item == "polileader4") %>% distinct(country, year) %>% nrow()
+polileader4_cy <- dcpo_input_raw_public1 %>% filter(item == "polileader4") %>% distinct(country, year) %>% nrow()
 
-polileader4_surveys <- dcpo_input_raw1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)
+polileader4_surveys <- dcpo_input_raw_public1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)
 
-housewifefull4_cy <- dcpo_input_raw1 %>% filter(item == "housewifefull4") %>% distinct(country, year) %>% nrow()
+housewifefull4_cy <- dcpo_input_raw_public1 %>% filter(item == "housewifefull4") %>% distinct(country, year) %>% nrow()
 ```
@@
 ```{r obs_by_country, fig.cap = "Countries with the Most Observations in the Source Data \\label{countries_by_obs}"}
-dcpo_input_raw1 %>%
+dcpo_input_raw_public1 %>%
   mutate(country = if_else(stringr::str_detect(country, "United"),
@@
 
-cby_plot <- dcpo_input_raw1 %>%
+cby_plot <- dcpo_input_raw_public1 %>%
   mutate(country = if_else(stringr::str_detect(country, "United"),
@@
 
-ybc_plot <- dcpo_input_raw1 %>%
+ybc_plot <- dcpo_input_raw_public1 %>%
   distinct(country, year) %>%

### 2020-09-29 paper/dcpo_gender_roles.Rmd
add the introduction

@@
 ```
+
+# Introduction
+
+Gender egalitarian attitude has been grown over the decades not only in developed countries but also in developing societies [@boehnke2011gender].
+With the affluent variance in the gender egalitarian attitude around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants.
+For example, the association between gender egalitarian attitudes and women's political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women's descriptive representation in parliaments [@paxton2003women] have been examined.
+However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes.
+Very few cross-national time-series measures of gender egalitarianism exist and there is no consensus on the measures.
+Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004.
+ To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view through the DCPO package for R [@Solt2020a].
+(Quick Review of our Index can be included).
+ The newly developed gender egalitarian index enables scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
+The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors.
+We also can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public opinion on the gender role.
+Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women].
+Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
+ This article proceeds with the following order. (Brief summaries about the rest of sections will be provided)
 

### 2020-10-01 paper/dcpo_gender_roles.Rmd
Separate Lines.
Adding Sentences for the four dimensions.

@@
 Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004.
+
 To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view through the DCPO package for R [@Solt2020a].
 (Quick Review of our Index can be included).
+
 The newly developed gender egalitarian index enables scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
@@
 Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
+
 This article proceeds with the following order. (Brief summaries about the rest of sections will be provided)
+
+# Below sentences are to explain four dimensions and the dimension we will concentrate (needed to be reviewed and modified)
+
+We examine all questionnaires asking opinions about gender roles from series of cross-national surveys such as World Value Surveys (WVS) and surveys conducted in individual countries or regions.
+After collecting the all questionnaires, we classify them into four categories: egarlitarian gender roles in the public sector which has been donimated by male, those in private sector where the role of female has been emphasized, the balance of female role in private and public sector, and male dominance over women.
 

### 2020-10-01 paper/dcpo_gender_roles.Rmd
add sentences

--- 2020-09-29 paper/dcpo_gender_roles.Rmd
@@
 Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
+
 This article proceeds with the following order. (Brief summaries about the rest of sections will be provided)
+
+# Below sentences are to explain four dimensions and the dimension we will concentrate (needed to be reviewed and modified)
+
+We examine all questionnaires asking opinions about gender roles from series of cross-national surveys such as World Value Surveys (WVS) and surveys conducted in individual countries or regions.
+After collecting the all questionnaires, we classify them into four categories: egalitarian gender roles in the public sector which has been dominated by male, those in private sector where the role of female has been emphasized, the balance of female role in private and public sector, and male dominance over women.
+
+(How about adding some sentences or table to show what kind of questionnaires are classified into the four categories?)
+
+Even though questionnaires in the four categories are asking about opinions about gender roles, generating estimates about egalitarian gender roles without the classification may cause multi-dimensionality problem.
 

### 2020-10-01 paper/dcpo_gender_roles.Rmd
keep updating.

--- 2020-09-29 paper/dcpo_gender_roles.Rmd
@@
 Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
+
 This article proceeds with the following order. (Brief summaries about the rest of sections will be provided)
+
+# Below sentences are to explain four dimensions and the dimension we will concentrate (needed to be reviewed and modified)
+
+We examine all questionnaires asking opinions about gender roles from series of cross-national surveys such as World Value Surveys (WVS) and surveys conducted in individual countries or regions.
+After collecting the all questionnaires, we classify them into four categories: egalitarian gender roles in the public sector which has been generally dominated by male, those in private sector where the role of female has been emphasized, the balance of female role in private and public sector, and male dominance over women.
+
+(How about adding some sentences or table to show what kind of questionnaires are classified into the four categories?)
+
+Even though questionnaires in the four categories are asking about opinions about gender roles, generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
+For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
 

### 2020-10-19 paper/dcpo_gender_roles.Rmd
adding lines
add lines

@@
 
-To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view through the DCPO package for R [@Solt2020a].
-(Quick Review of our Index can be included).
+To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a].
+(Quick Review of our Index can be included - number of countries and years, unit of analysis, number of surveys and questionnaires will be introduced).
 
@@
 For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
+Given that the number of questionnaires about gender roles is relatively high compared to others (I think adding the actual numbers will be helpful), we focus on the opinions about gender role in public sectors to generate our estimate of egalitarian gender role.
 

### 2020-10-19 paper/dcpo_gender_roles.Rmd
adding lines

@@
 To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a]. 
-(Quick Review of our Index can be included - number of countries and years, unit of analysis, number of surveys and questionnaires will be introduced).
-
-The newly developed gender egalitarian index enables scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
+Our new index is based on data from 62 survey datasets from 1972 to 2020, which includes 224,640 observations. 
+The newly developed gender egalitarian index provides opportunities for scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
 The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors.
@@
 
-This article proceeds with the following order. (Brief summaries about the rest of sections will be provided)
+This article proceeds with the following order. First, we
 
-# Below sentences are to explain four dimensions and the dimension we will concentrate (needed to be reviewed and modified)
+# Multi-Dimensionality of Egalitarian Gender Role
 

### 2020-10-19 paper/dcpo_gender_roles.Rmd
add lines

@@
 
-This article proceeds with the following order. First, we
+This article proceeds with the following order.
+First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector.
+Next, we illustrate the data source we used to build our index.
+Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced.
+Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.
 
-# Multi-Dimensionality of Egalitarian Gender Role
+# Multi-Dimensionality in Egalitarian Gender Role
 

### 2020-10-19 paper/dcpo_gender_roles.Rmd
add lines

@@
 
-We examine all questionnaires asking opinions about gender roles from series of cross-national surveys such as World Value Surveys (WVS) and surveys conducted in individual countries or regions.
-After collecting the all questionnaires, we classify them into four categories: egalitarian gender roles in the public sector which has been generally dominated by male, those in private sector where the role of female has been emphasized, the balance of female role in private and public sector, and male dominance over women.
+Gender egalitarianism does not have only one dimension but a multi-dimension.
+Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
+For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
+To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework.
+Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting.
+If we disregard this kind of multi-dimensionality, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.
+The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions.
+However, given that there are some variations of gender
 
-(How about adding some sentences or table to show what kind of questionnaires are classified into the four categories?)
+After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc.,
 
-Even though questionnaires in the four categories are asking about opinions about gender roles, generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
-For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
 Given that the number of questionnaires about gender roles is relatively high compared to others (I think adding the actual numbers will be helpful), we focus on the opinions about gender role in public sectors to generate our estimate of egalitarian gender role.
+
+egalitarian gender roles in the public sector which has been generally dominated by male, those in private sector where the role of female has been emphasized, the balance of female role in private and public sector, and male dominance over women.
 

### 2020-10-19 paper/dcpo_gender_roles.Rmd
adding lines

@@
 Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting.
-If we disregard this kind of multi-dimensionality, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.
 The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions.
-However, given that there are some variations of gender
+However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.
 
-After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc.,
+After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc., we classify them into four categories: 1) egalitarian gender roles in the public sector which has been generally dominated by male, 2) those in private sector where the role of female has been emphasized, 3) the balance of female role in private and public sector, and 4) male dominance over women.
 
 Given that the number of questionnaires about gender roles is relatively high compared to others (I think adding the actual numbers will be helpful), we focus on the opinions about gender role in public sectors to generate our estimate of egalitarian gender role.
-
-egalitarian gender roles in the public sector which has been generally dominated by male, those in private sector where the role of female has been emphasized, the balance of female role in private and public sector, and male dominance over women.
 

### 2020-10-19 paper/dcpo_gender_roles.Rmd
adding lines

@@
 After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc., we classify them into four categories: 1) egalitarian gender roles in the public sector which has been generally dominated by male, 2) those in private sector where the role of female has been emphasized, 3) the balance of female role in private and public sector, and 4) male dominance over women.
+Questionnaires related to the first dimension are asking respondents about the role of women or perspective on women in the public sector.
+For example, "On the whole, men make better business executives than women do", "Would you say that most men are better suited emotionally for politics than are most women, that men and women are equally suited, or that women are better suited than men in this area?", "When jobs are scarce, men have more right to a job than women", "Some say that in general, men are better political leaders than women.
+Do you strongly agree, agree, disagree or strongly disagree?", and other similar questionnaires are classified as the first dimension.
+Questionnaires about childcare or housework such as "A man can be responsible for looking after the home and children just as well while the woman works full-time" or "A father should be as heavily involved in the care of his children as the mother" are classified as the second dimension.
 

### 2020-10-19 paper/dcpo_gender_roles.Rmd
adding lines

@@
 Questionnaires about childcare or housework such as "A man can be responsible for looking after the home and children just as well while the woman works full-time" or "A father should be as heavily involved in the care of his children as the mother" are classified as the second dimension.
+The rest of questionnaires are classifed into the third or fourth dimensions.
+While questionnaires such as "A working mother can establish just as warm and secure a relationship with her children as a mother who does not work" and "A pre-school child is likely to suffer if his or her mother works" are about the third dimension, others including "View on Change of Surname at Marriage" and "A woman can travel abroad by herself if she wishes" are related to the fourth dimension.
 

### 2020-11-07 paper/dcpo_gender_roles.Rmd
Update dcpo_gender_roles.Rmd
revise title, work at intro, add some validation text

--- 2020-10-19 paper/dcpo_gender_roles.Rmd
@@
     template: svm-latex-ms2.tex
-title: "[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles"
+title: "Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere"
 thanks: "Corresponding author: [frederick-solt@uiowa.edu](mailto:frederick-solt@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
@@
 abstract: ""
-keywords: ""
+keywords: "gender inequality, public opinion, measurement"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
       - \usepackage{wrapfig}
-nocite: |
-  @Solt2020a
 ---
@@
 
-# Introduction
-
-Gender egalitarian attitude has been grown over the decades not only in developed countries but also in developing societies [@boehnke2011gender].
-With the affluent variance in the gender egalitarian attitude around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants.
-For example, the association between gender egalitarian attitudes and women's political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women's descriptive representation in parliaments [@paxton2003women] have been examined.
-However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes.
-Very few cross-national time-series measures of gender egalitarianism exist and there is no consensus on the measures.
-Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004.
-
-To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a]. 
-Our new index is based on data from 62 survey datasets from 1972 to 2020, which includes 224,640 observations. 
-The newly developed gender egalitarian index provides opportunities for scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
-The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors.
-We also can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public opinion on the gender role.
-Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women].
-Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
-
-This article proceeds with the following order.
-First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector.
-Next, we illustrate the data source we used to build our index.
-Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced.
-Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.
-
-# Multi-Dimensionality in Egalitarian Gender Role
-
-Gender egalitarianism does not have only one dimension but a multi-dimension.
-Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
-For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
-To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework.
-Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting.
-The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions.
-However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.
-
-After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc., we classify them into four categories: 1) egalitarian gender roles in the public sector which has been generally dominated by male, 2) those in private sector where the role of female has been emphasized, 3) the balance of female role in private and public sector, and 4) male dominance over women.
-
-Given that the number of questionnaires about gender roles is relatively high compared to others (I think adding the actual numbers will be helpful), we focus on the opinions about gender role in public sectors to generate our estimate of egalitarian gender role.
+We classified the available survey items on gender egalitarian attitudes into four categories.  
+The first of these categories consists of questions asking respondents' views on women gaining opportunities in the traditionally masculine public sphere of education, paid work, and politics.
+The second category, in turn, encompasses questions focusing on whether and to what degree men should take on responsibilities in the traditionally feminine private sphere of housework and childcare.
+A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is virtually never included in surveys.
+The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames to the recognition of sexual harassment and the justifiability of intimate partner violence committed by husbands.
+To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only questions from the first category, gender egalitarianism in the public sphere.
+Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
 
@@
 
-# Estimating Gender Egalitarianism
+# Estimating Public Gender Egalitarianism
 
@@
 
+# Validating Public Gender Egalitarianism
+
+# Using the Public Gender Egalitarianism Index
+
+One aspect of latent-variable estimates of public opinion like the PGE that is easy for researchers to overlook is the uncertainty in the estimates.
+But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
+Therefore, taking the uncertainty in the PGE index into account is crucial to reaching well-grounded conclusions.
+
+The PGE download includes pre-formatted data to facilitate incorporating the uncertainty in the index.
+In R, the functions of the \texttt{purrr} package [@Henry2019, also included in the widely-used \texttt{tidyverse} package [@Wickham2017a]] make it entirely straightforward to incorporate the uncertainty of the PGE estimates.
+In Stata, the \texttt{mi estimate:} command prefix originally developed for analyzing multiply imputed data can be used to automate the process of building uncertainty into nearly any analysis.
+Step-by-step instructions on how to use these tools, complete with examples, are included in the data download.
+
 # Conclusion

### 2020-11-07 paper/dcpo_gender_roles.Rmd

--- 2020-10-19 paper/dcpo_gender_roles.Rmd
@@
 
-Given that the number of questionnaires about gender roles is relatively high compared to others (I think adding the actual numbers will be helpful), we focus on the opinions about gender role in public sectors to generate our estimate of egalitarian gender role.
+We classified the available survey items on gender egalitarian attitudes into four categories.  
+The first of these categories consists of questions asking respondents' views on women gaining opportunities in the traditionally masculine public sphere of education, paid work, and politics.
+The second category, in turn, encompasses questions focusing on whether and to what degree men should take on responsibilities in the traditionally feminine private sphere of housework and childcare.
+A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is virtually never included in surveys.
+The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames to the recognition of sexual harassment and the justifiability of intimate partner violence committed by husbands.
+To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only questions from the first category, gender egalitarianism in the public sphere.
+Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
 

### 2020-11-21 paper/dcpo_gender_roles.Rmd
revise paragraphs on classification

@@
 
-After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc., we classify them into four categories: 1) egalitarian gender roles in the public sector which has been generally dominated by male, 2) those in private sector where the role of female has been emphasized, 3) the balance of female role in private and public sector, and 4) male dominance over women.
-Questionnaires related to the first dimension are asking respondents about the role of women or perspective on women in the public sector.
-For example, "On the whole, men make better business executives than women do", "Would you say that most men are better suited emotionally for politics than are most women, that men and women are equally suited, or that women are better suited than men in this area?", "When jobs are scarce, men have more right to a job than women", "Some say that in general, men are better political leaders than women.
-Do you strongly agree, agree, disagree or strongly disagree?", and other similar questionnaires are classified as the first dimension.
-Questionnaires about childcare or housework such as "A man can be responsible for looking after the home and children just as well while the woman works full-time" or "A father should be as heavily involved in the care of his children as the mother" are classified as the second dimension.
-The rest of questionnaires are classifed into the third or fourth dimensions.
-While questionnaires such as "A working mother can establish just as warm and secure a relationship with her children as a mother who does not work" and "A pre-school child is likely to suffer if his or her mother works" are about the third dimension, others including "View on Change of Surname at Marriage" and "A woman can travel abroad by herself if she wishes" are related to the fourth dimension.
-
 We classified the available survey items on gender egalitarian attitudes into four categories.  
@@
 The second category, in turn, encompasses questions focusing on whether and to what degree men should take on responsibilities in the traditionally feminine private sphere of housework and childcare.
-A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is virtually never included in surveys.
-The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames to the recognition of sexual harassment and the justifiability of intimate partner violence committed by husbands.
-To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only questions from the first category, gender egalitarianism in the public sphere.
-Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
-
-# The Source Data on Gender Egalitarian Attitudes
+A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only very rarely included in surveys.
+The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition of various forms of sexual harassment to the justifiability of intimate partner violence committed by husbands.
 
@@
 
-The first step towards remedying this problem is collecting the available public opinion data on gender egalitarian attitudes.
-We draw on data from `r n_surveys` survey datasets, in which we identified `r n_items` distinct relevant survey items that were asked in no fewer than five country-years.
+To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.
+Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
+In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years; these items were drawn from `r n_surveys` different survey datasets.
+We describe these source data in detail in the next section.
+
+# The Source Data on Gender Egalitarian Attitudes
+
 Together, these survey items were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.

### 2020-11-25 paper/dcpo_gender_roles.Rmd
fix caption of cs_plot (most recent available year rather than 2020); include year in axis tick label

@@
 
-```{r cs_plot, fig.cap="Egalitarian Gender Attitudes, 2020 \\label{cs_2020}", fig.height=8, warning=FALSE}
-load(here::here("data", "dcpo_input.rda"))
+```{r cs_plot, fig.cap="Egalitarian Gender Attitudes, Most Recent Available Year \\label{cs_2020}", fig.height=8, warning=FALSE}
+load(here::here("data", "dcpo_input_public.rda"))
 load(here::here("data", "dcpo_output.rda"))
@@
     arrange(-mean) %>%
-    mutate(half = ntile(mean, 2))
+    mutate(half = ntile(mean, 2),
+           country = paste0(country, " (", year, ")"))
 
-p1_data_a <- p1_data %>% filter(half==2) %>% mutate(ranked = as.factor(row_number(mean)))
-p1_data_b <- p1_data %>% filter(half==1) %>% mutate(ranked = as.factor(row_number(mean)))
+p1_data_a <- p1_data %>% 
+  filter(half==2) %>% 
+  mutate(ranked = as.factor(row_number(mean)))
+p1_data_b <- p1_data %>%
+  filter(half==1) %>%
+  mutate(ranked = as.factor(row_number(mean)))
 

### 2020-11-25 paper/dcpo_gender_roles.Rmd
add footnote with counterexample of question re men balancing public and private spheres

@@
 The second category, in turn, encompasses questions focusing on whether and to what degree men should take on responsibilities in the traditionally feminine private sphere of housework and childcare.
-A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only very rarely included in surveys.
+A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only very rarely included in surveys.^[One laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly gaining popularity, is the item asking respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
 The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition of various forms of sexual harassment to the justifiability of intimate partner violence committed by husbands.
@@
   distinct(country) %>% 
+  nrow()
+
+n_cy <- dcpo_input_raw_public1 %>%
+  distinct(country, year) %>% 
   nrow()

### 2020-11-28 paper/dcpo_gender_roles.Rmd
update

--- 2020-11-25 paper/dcpo_gender_roles.Rmd
@@
 
-knitr::opts_chunk$set(cache = TRUE, echo = FALSE, fig.width=6.5, fig.height=2.5, cache.extra = tools::md5sum(here::here("data", "dcpo_input_raw.csv")))
+knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, fig.width=6.5, fig.height=2.5, cache.extra = tools::md5sum(here::here("data", "dcpo_input_raw.csv")))
 
@@
 
-Gender egalitarian attitude has been grown over the decades not only in developed countries but also in developing societies [@boehnke2011gender].
-With the affluent variance in the gender egalitarian attitude around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants.
-For example, the association between gender egalitarian attitudes and women's political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women's descriptive representation in parliaments [@paxton2003women] have been examined.
-However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes.
-Very few cross-national time-series measures of gender egalitarianism exist and there is no consensus on the measures.
-Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004.
+<!-- Gender egalitarian attitude has been grown over the decades not only in developed countries but also in developing societies [@boehnke2011gender]. -->
+<!-- With the affluent variance in the gender egalitarian attitude around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants.
+-->
+<!-- For example, the association between gender egalitarian attitudes and women's political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women's descriptive representation in parliaments [@paxton2003women] have been examined.
+-->
+<!-- However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes. -->
+<!-- Very few cross-national time-series measures of gender egalitarianism exist and there is no consensus on the measures. -->
+<!-- Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004.
+-->
 
-To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a]. 
-Our new index is based on data from 62 survey datasets from 1972 to 2020, which includes 224,640 observations. 
-The newly developed gender egalitarian index provides opportunities for scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
-The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors.
-We also can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public opinion on the gender role.
-Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women].
-Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
+<!-- To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a].  -->
+<!-- Our new index is based on data from 62 survey datasets from 1972 to 2020, which includes 224,640 observations.  -->
+<!-- The newly developed gender egalitarian index provides opportunities for scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
+-->
+<!-- The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors.
+-->
+<!-- We also can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public opinion on the gender role.
+-->
+<!-- Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women].
+-->
+<!-- Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
+-->
 
-This article proceeds with the following order. 
-First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector.
-Next, we illustrate the data source we used to build our index.
-Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced.
-Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.
+<!-- This article proceeds with the following order.  -->
+<!-- First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector. -->
+<!-- Next, we illustrate the data source we used to build our index. -->
+<!-- Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced. -->
+<!-- Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.     -->
 
-# Multi-Dimensionality in Egalitarian Gender Role
+# Multi-Dimensionality in Gender Egalitarianism
 
@@
 However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.
-
-We classified the available survey items on gender egalitarian attitudes into four categories.  
-The first of these categories consists of questions asking respondents' views on women gaining opportunities in the traditionally masculine public sphere of education, paid work, and politics.
-The second category, in turn, encompasses questions focusing on whether and to what degree men should take on responsibilities in the traditionally feminine private sphere of housework and childcare.
-A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only very rarely included in surveys.
-The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition of various forms of sexual harassment to the justifiability of intimate partner violence committed by husbands.
 
@@
 
+n_cy <- dcpo_input_raw_public1 %>%
+  distinct(country, year) %>% 
+  nrow() %>% 
+  scales::comma()
+
 n_years <- as.integer(summary(dcpo_input_raw_public1$year)[6]-summary(dcpo_input_raw_public1$year)[1])
+
+spanned_cy <- dcpo_input_raw_public1 %>% 
+  group_by(country) %>% 
+  summarize(years = max(year) - min(year)) %>% 
+  summarize(n = sum(years)) %>% 
+  pull(n) %>% 
+  scales::comma()
 
@@
 
-To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.
+We classified the available survey items on gender egalitarian attitudes into four categories.  
+The first of these categories consists of questions asking respondents' views of gender equality in the traditionally masculine public sphere of education, paid work, and politics.
+The second category, in turn, encompasses questions focusing on gender equality in the traditionally feminine private sphere of housework and childcare.
+A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only rarely included in surveys.^[One laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly becoming more common, is the item querying respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
+The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.
+
+To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE index.
+The complete list of gender egalitarianism items is included in the Appendix.]
 Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
@@
 polileader4_surveys <- dcpo_input_raw_public1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)
-
-housewifefull4_cy <- dcpo_input_raw_public1 %>% filter(item == "housewifefull4") %>% distinct(country, year) %>% nrow()
 ```
@@
 Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
-That this constitutes only `r round(polileader4_cy*100/(n_countries * n_years))`% of the `r total_cy` total possible country-years covered---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.
+That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the `r spanned_cy` country-years spanned by our data---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.
 
@@
 ```{r dcpo, eval=FALSE}
-iter <- 4000
+iter <- 3000
+
+dcpo_input <- dcpo_input_public
 
@@
                     pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+
+save(dcpo_input, file = here::here("data", "dcpo_input.rda"))
 
@@
 
-```{r cs_plot, fig.cap="Egalitarian Gender Attitudes, Most Recent Available Year \\label{cs_2020}", fig.height=8, warning=FALSE}
-load(here::here("data", "dcpo_input_public.rda"))
+```{r cs_plot, fig.cap="Public Gender Egalitarianism, Most Recent Available Year \\label{cs_mry}", fig.height=8, warning=FALSE}
+load(here::here("data", "dcpo_input.rda"))
 load(here::here("data", "dcpo_output.rda"))
@@
   filter(half==1) %>%
-  mutate(ranked = as.factor(row_number(mean)))
+  mutate(ranked = as.factor(row_number(mean)),
+         country = str_replace(country, "’", "'"))
 

### 2020-12-08 paper/dcpo_gender_roles.Rmd
add validation

@@
 
-knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, fig.width=6.5, fig.height=2.5, cache.extra = tools::md5sum(here::here("data", "dcpo_input_raw.csv")))
+knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE,
+                      fig.width=7, fig.height=2.5)
 
@@
 library(tidyverse)
+library(countrycode)
+library(patchwork)
+library(rsdmx)
 
@@
   scales::comma()
+
+back_to_numeric <- function(string_number) {
+  string_number %>% 
+    str_replace(",", "") %>% 
+    as.numeric()
+}
 ```
@@
 Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
-In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years; these items were drawn from `r n_surveys` different survey datasets.
+In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.
 We describe these source data in detail in the next section.
@@
 Together, these survey items were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
-Considering that observations for every year in each country surveyed would number `r total_cy` and so a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations, the available data is clearly very, very sparse.
+Considering that observations for every year in each country surveyed would number `r total_cy` and so a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations.
+Viewed from this perspective of complete data, the available data can be seen to be very, very sparse.
+From a more optimistic standpoint, we note there there are `r n_cy` country-years in which we have at least _some_ information about the public gender egalitarianism of the population, that is, some `r {back_to_numeric(n_cy)/back_to_numeric(spanned_cy) * 100} %>% round()`% of the `r spanned_cy` country-years spanned by the data we collected.
+But there is no gainsaying that the many different survey items employed renders these data difficult to use together.
 
-```{r obs_by_item, fig.height=3, fig.cap = "Items with the Most Observations in the Source Data \\label{items_by_obs}"}
-dcpo_input_raw_public1 %>%
+```{r item_and_country_plots, fig.height=3, fig.cap = "Items and Countries with the Most Observations in the Source Data \\label{item_country_plots}"}
+items_plot <- dcpo_input_raw_public1 %>%
   distinct(country, year, item) %>%
@@
   theme(axis.title.x = element_blank(),
-        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
-  ylab("Country-Years Observed")
+        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  ylab("Country-Years Observed") +
+  ggtitle("Items")
 
@@
 polileader4_surveys <- dcpo_input_raw_public1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)
-```
 
-Figure&nbsp;\ref{items_by_obs} displays in how many country-years each of the twelve most-commonly asked items are available.
-The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
-Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
-That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the `r spanned_cy` country-years spanned by our data---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.
-
-Which countries are the most data-rich?
-Figure&nbsp;\ref{countries_by_obs} below shows the dozen countries with the highest count of country-year-item observations.
-
-```{r obs_by_country, fig.cap = "Countries with the Most Observations in the Source Data \\label{countries_by_obs}"}
-dcpo_input_raw_public1 %>%
+countries_plot <- dcpo_input_raw_public1 %>%
   mutate(country = if_else(stringr::str_detect(country, "United"),
@@
   theme(axis.title.x = element_blank(),
-        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
-  ylab("Year-Items Observed")
+        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  ylab("Year-Items Observed") +
+  ggtitle("Countries")
 
-# uk_nas <- {1 + max(swiid_source$year) - min(swiid_source$year) - 
-# {swiid_source %>% filter(country == "United Kingdom") %>% pull(year) %>% unique() %>% length()}} %>%
-# wordify_numeral()
-# 
-# iran_obs <- swiid_source %>% filter(country == "Iran") %>% pull(year) %>% unique() %>% length()
-# 
-# med_cy <- swiid_source %>% count(country, year) %>% count(country, name = "nn") %>% pull(nn) %>% median() %>% wordify_numeral()
+us_obs <- dcpo_input_raw_public1 %>% 
+  distinct(country, year, item) %>%
+  count(country) %>%
+  filter(country == "United States") %>%
+  pull(n)
+
+others <- dcpo_input_raw_public1 %>%
+  distinct(country, year, item) %>%
+  count(country) %>%
+  arrange(desc(n)) %>%
+  slice(2:5) %>%
+  pull(country) %>% 
+  paste(collapse = ", ") %>% 
+  str_replace(", (\\w+)$", ", and \\1")
+
+data_poorest <- dcpo_input_raw_public1 %>%
+  distinct(country, year, item) %>%
+  count(country) %>%
+  arrange(n) %>%
+  filter(n == 2) %>%
+  pull(country) %>% 
+  paste(collapse = ", ") %>% 
+  str_replace(", (\\w+)$", ", and \\1")
+
+wordify_numeral <- function(x) setNames(c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen", " seventeen", "eighteen", "nineteen"), 1:19)[x]
+
+n_data_poorest <- {data_poorest %>%
+    str_split(",") %>% 
+    first()} %>% 
+  length() %>% 
+  wordify_numeral()
+
+items_plot + countries_plot
 ```
 
+The left panel of Figure&nbsp;\ref{item_country_plots} displays in how many country-years each of the twelve most-commonly asked survey items are available.
+The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
+Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
+That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
+
+Which countries are the most data-rich?
+The right panel of Figure&nbsp;\ref{item_country_plots} shows the dozen countries with the highest count of country-year-item observations.
+The United States, with `r us_obs` observations, is far and away the best represented country in the source data, followed by `r others`.
+At the other end of the spectrum, `r n_data_poorest` countries---`r data_poorest`---have only the minimum two observations required to be included in the source dataset at all.
+
 ```{r years_by_country, fig.cap="Country-Year Coverage in the Source Data \\label{countries_by_years}"}
-library(patchwork)
-
 cby_plot <- dcpo_input_raw_public1 %>%
@@
   theme(axis.title.x = element_blank(),
-        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
-  ylab("Years Observed")
+        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  ylab("Years Observed") +
+  ggtitle("Countries")
 
@@
   theme(axis.title.x = element_blank(),
-        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95)) +
-  ylab("Countries Observed")
+        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  ylab("Countries Observed") +
+  ggtitle("Years")
 
@@
                     pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+```
+
+```{r dcpo_results}
+load(here::here("data", "polileader4_2_4k_11-27.rda"))
 
@@
 
-```{r cs_plot, fig.cap="Public Gender Egalitarianism, Most Recent Available Year \\label{cs_mry}", fig.height=8, warning=FALSE}
+```{r cs_plot, fig.cap="PGE Mean and Polarization Scores, Most Recent Available Year \\label{cs_mry}", fig.height=8}
 load(here::here("data", "dcpo_input.rda"))
@@
 # Validating Public Gender Egalitarianism
+We turn now to the validity of the PGE Mean scores.
+Like @Caughey2019 [684-685], we provide evidence of our new measure's validity through tests of both convergent validation and construct validation.
+
+```{r extract_res}
+dat <- dcpo_input$data
+
+qcodes <- dat %>%
+  dplyr::group_by(question) %>%
+  dplyr::summarize(qq = first(qq) %>%
+                     as.numeric())
+
+kcodes <- dat %>%
+  dplyr::group_by(country) %>%
+  dplyr::summarize(kk = first(kk) %>%
+                     as.numeric())
+
+tcodes <- dat %>%
+  dplyr::group_by(year) %>%
+  dplyr::summarize(tt = first(tt))
+
+ktcodes <- dat %>%
+  dplyr::group_by(country) %>%
+  dplyr::summarize(first_yr = min(year),
+                   last_yr = max(year))
+
+theta_res <- rstan::extract(dcpo_output, pars = "theta") %>%
+        dplyr::first() %>%
+        purrr::array_branch(1) %>%
+        purrr::map(function(x) {
+          tibble::as_tibble(x) %>%
+          dplyr::mutate(tt = row_number()) %>%
+            dplyr::left_join(tcodes, by = "tt") %>%
+            tidyr::pivot_longer(cols = starts_with("V"),
+                                names_to = "kk",
+                                values_to = "pge_mean") %>%
+            dplyr::mutate(year = if_else(tt == 1,
+                                         year, min(year, na.rm = TRUE) + tt - 1),
+                          kk = str_replace(kk, "V", "") %>% as.numeric()) %>%
+            dplyr::left_join(kcodes, by = "kk") %>%
+            dplyr::left_join(ktcodes, by = "country") %>%
+            dplyr::filter(year >= first_yr & year <= last_yr) %>%
+            dplyr::arrange(kk, tt) %>%
+            dplyr::select(country, year, pge_mean)
+        })
+
+sigma_res <- rstan::extract(dcpo_output, pars = "sigma") %>%
+        dplyr::first() %>%
+        purrr::array_branch(1) %>%
+        purrr::map(function(x) {
+          tibble::as_tibble(x) %>%
+          dplyr::mutate(tt = row_number()) %>%
+            dplyr::left_join(tcodes, by = "tt") %>%
+            tidyr::pivot_longer(cols = starts_with("V"),
+                                names_to = "kk",
+                                values_to = "pge_polarization") %>%
+            dplyr::mutate(year = if_else(tt == 1,
+                                         year, min(year, na.rm = TRUE) + tt - 1),
+                          kk = str_replace(kk, "V", "") %>% as.numeric()) %>%
+            dplyr::left_join(kcodes, by = "kk") %>%
+            dplyr::left_join(ktcodes, by = "country") %>%
+            dplyr::filter(year >= first_yr & year <= last_yr) %>%
+            dplyr::arrange(kk, tt) %>%
+            dplyr::select(country, year, pge_polarization)
+        })
+
+pge <- map2(theta_res, sigma_res, function(theta, sigma) {
+  left_join(theta, sigma, by = c("country", "year"))
+})
+
+save(pge, file = here::here("data", "pge.rda"))
+```
+
+```{r convergent, fig.cap="Convergent Validation: Correlations Between PGE Mean Scores and Individual Public Gender Equality Survey Items \\label{conv_plot}", fig.height=4}
+
+internal_dat <- dcpo_input$data %>% 
+  filter(item == "polileader4 3 or higher") %>% 
+  mutate(prop = 1 - y_r/n_r,
+         se = sqrt((prop*(1-prop))/n),
+         prop_90 = prop + qnorm(.9)*se,
+         prop_10 = prop - qnorm(.9)*se) %>% 
+  left_join(theta_results %>% select(-kk, -tt), by = c("country", "year"))
+
+pge_polileader <- pge %>% 
+  map(. %>% right_join(dcpo_input$data %>% 
+                         filter(item == "polileader4 3 or higher") %>% 
+                         rowwise() %>% 
+                         transmute(country = country,
+                                   year = year,
+                                   prop = 1 - y_r/n_r,
+                                   se = sqrt((prop*(1-prop))/n),
+                                   polileader = rnorm(1, mean = prop, sd = se)), 
+                       by = c("country", "year")))
+
+internal_cor <- map(pge_polileader, function(x) with(x, cor(pge_mean, polileader))) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2) %>% 
+  paste0("R = ", .)
+
+internal_label <- tibble(mean = .78, prop = .99, label = internal_cor)
+
+internal_plot <- internal_dat %>% 
+  ggplot(aes(x = mean,
+             y = prop * 100)) +
+  geom_segment(aes(x = `10%`, xend = `90%`,
+                   y = prop * 100, yend = prop * 100),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_segment(aes(x = mean, xend = mean,
+                   y = prop_90 * 100, yend = prop_10 * 100),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_smooth(method = 'lm', se = FALSE) +
+  theme_bw() +
+  theme(legend.position="none",
+        axis.text  = element_text(size=8),
+        axis.title = element_text(size=9),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  coord_cartesian(ylim=c(0,100)) +
+  scale_x_continuous(breaks=seq(.1, .9, 0.2)) +
+  labs(x = "PGE Mean Score", 
+       y = '% Agreeing That "On the Whole, Men\nMake Better Political Leaders than Women Do"') + 
+  ggtitle("All Country-Years") +
+  geom_label(data = internal_label, aes(label = label), size = 3)
+
+## Cross-sectional
+internal_poliequal <- dcpo_input$data %>% 
+  filter(item == "poliequal3 2 or higher" & year == 2007) %>% 
+  mutate(iso2c = countrycode::countrycode(country,
+                             origin = "country.name",
+                             destination = "iso2c"),
+         prop = 1 - y_r/n_r,
+         se = sqrt((prop*(1-prop))/n),
+         prop_90 = prop + qnorm(.9)*se,
+         prop_10 = prop - qnorm(.9)*se) %>% 
+  left_join(theta_results %>% select(-kk, -tt), by = c("country", "year"))
+
+pge_poliequal <- pge %>% 
+  map(. %>% right_join(dcpo_input$data %>% 
+                         filter(item == "poliequal3 2 or higher" & year == 2007) %>% 
+                         rowwise() %>% 
+                         transmute(country = country,
+                                   year = year,
+                                   prop = 1 - y_r/n_r,
+                                   se = sqrt((prop*(1-prop))/n),
+                                   poliequal = rnorm(1, mean = prop, sd = se)), 
+                       by = c("country", "year")))
+
+internal_cs_cor <- map(pge_poliequal, 
+                       function(x) with(x, cor(pge_mean, poliequal))) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2) %>% 
+  paste0("R = ", .)
+
+internal_cs_label <- tibble(mean = .7, prop = .77, label = internal_cs_cor)
+
+internal_cs_plot <- internal_poliequal %>% 
+  ggplot(aes(x = mean,
+             y = prop * 100)) +
+  geom_segment(aes(x = `10%`, xend = `90%`,
+                   y = prop * 100, yend = prop * 100),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_segment(aes(x = mean, xend = mean,
+                   y = prop_90 * 100, yend = prop_10 * 100),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_text(aes(label = iso2c), size = 2) +
+  geom_smooth(method = 'lm', se = FALSE) +
+  theme_bw() +
+  theme(legend.position="none",
+        axis.text  = element_text(size=8),
+        axis.title = element_text(size=9),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  labs(x = "PGE Mean Score", 
+       y = '% Opining That "Men Generally Make\nBetter Political Leaders Than Women"') + 
+  ggtitle("Pew Global Spring 2007") +
+  geom_label(data = internal_cs_label, aes(label = label), size = 3)
+
+# Longitudinal
+internal_us <- dcpo_input$data %>% 
+  filter(item == "emopoli2 2 or higher") %>% 
+  mutate(prop = y_r/n_r,
+         se = sqrt((prop*(1-prop))/n),
+         prop_90 = prop + qnorm(.9)*se,
+         prop_10 = prop - qnorm(.9)*se) %>% 
+  right_join(theta_results %>% 
+               select(-kk, -tt) %>%
+               filter(country == "United States"),
+             by = c("country", "year"))
+
+pge_emopoli <- pge %>% 
+  map(. %>% right_join(dcpo_input$data %>% 
+                         filter(item == "emopoli2 2 or higher") %>% 
+                         rowwise() %>% 
+                         transmute(country = country,
+                                   year = year,
+                                   prop = y_r/n_r,
+                                   se = sqrt((prop*(1-prop))/n),
+                                   emopoli = rnorm(1, mean = prop, sd = se)), 
+                       by = c("country", "year")))
+
+internal_us_cor <- map(pge_emopoli, function(x) with(x, cor(pge_mean, emopoli))) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2) %>% 
+  paste0("R = ", .)
+
+internal_us_label <- tibble(year = 1980, mean = .82, label = internal_us_cor)
+
+internal_us_plot <- internal_us %>% 
+  ggplot(aes(x = year,
+             y = mean)) +
+  geom_line() +
+  geom_ribbon(aes(ymin = `10%`,
+                  ymax = `90%`,
+                  linetype = NA),
+               alpha = .2) +
+  geom_point(aes(y = prop),
+             na.rm = TRUE) +
+  geom_path(aes(y = prop),
+            linetype = 3,
+            na.rm = TRUE,
+            alpha = .7) +
+  geom_segment(aes(x = year, xend = year,
+                   y = prop_90, yend = prop_10),
+               na.rm = TRUE,
+               alpha = .2) +
+  annotate("text", x = 1979, y = .72, size = 2,
+           label = 'emopoli2,\nU.S. GSS') +
+  annotate("text", x = 2012, y = .60, size = 2,
+           label = "PGE Mean") +
+  labs(x = "Year", 
+       y = "Score") +
+  theme_bw() +
+  theme(legend.position="none",
+        axis.text  = element_text(size=8),
+        axis.title = element_text(size=9),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  ggtitle("United States") +
+  geom_label(data = internal_us_label, aes(label = label), size = 3)
+
+internal_plot + internal_cs_plot + internal_us_plot
+```
+
+Figure&nbsp;\ref{conv_plot} displays our tests of convergent validation.
+Convergent validation refers to demonstrating that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
+Here, we compare PGE Mean scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
+In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women."
+Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders."
+Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country.
+The U.S. General Social Survey asked this question 25 times from 1972 to 2016.
+It asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women"; to facilitate visual comparison of the longitudinal relationship, we plot the estimated population proportion that disagreed with the statement.
+In every case, the correlations---estimated taking into account the uncertainty in the measures^[The uncertainty in the PGE Mean score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the `polileader4` question, but failing to account for this uncertainty would overstate the correlation with the Pew `poliequal3` item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S.
+GSS `emopoli2` item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`.
+We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.]---are in the expected direction and very strong.
+
+```{r construct_validation_survey, fig.cap="Construct Validation: Correlations Between PGE Mean Scores and Individual 'Balancing' Gender Equality Survey Items \\label{surv_const_plot}", fig.height=4}
+dcpo_input_balance <- DCPOtools::format_dcpo(dcpo_input_raw_balance1,
+                                            scale_q = "familywoman4",
+                                            scale_cp = 2)
+
+wantch <- dcpo_input_balance$data %>% 
+  filter(item == "wantch4 3 or higher") %>% 
+  mutate(iso2c = countrycode::countrycode(country,
+                             origin = "country.name",
+                             destination = "iso2c"),
+         prop = 1 - y_r/n_r,
+         se = sqrt((prop*(1-prop))/n),
+         prop_90 = prop + qnorm(.9)*se,
+         prop_10 = prop - qnorm(.9)*se) %>% 
+  left_join(theta_results %>% select(-kk, -tt), by = c("country", "year"))
+
+pge_wantch <- pge %>% 
+  map(. %>% right_join(wantch %>% 
+                         rowwise() %>% 
+                         transmute(country = country,
+                                   year = year,
+                                   prop = 1 - y_r/n_r,
+                                   se = sqrt((prop*(1-prop))/n),
+                                   wantch = rnorm(1, mean = prop, sd = se)), 
+                       by = c("country", "year")))
+
+wantch_cor <- map(pge_wantch, function(x) 
+  with(x, cor(pge_mean, wantch))) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2) %>% 
+  paste0("R = ", .)
+
+wantch_label <- tibble(mean = .76, prop = .97, label = wantch_cor)
+
+wantch_plot <- wantch %>% 
+  ggplot(aes(x = mean,
+             y = prop * 100)) +
+  geom_segment(aes(x = `10%`, xend = `90%`,
+                   y = prop * 100, yend = prop * 100),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_segment(aes(x = mean, xend = mean,
+                   y = prop_90 * 100, yend = prop_10 * 100),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_smooth(method = 'lm', se = FALSE) +
+  theme_bw() +
+  theme(legend.position="none",
+        axis.text  = element_text(size=8),
+        axis.title = element_text(size=9),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  coord_cartesian(ylim=c(0,100)) +
+  labs(x = "PGE Mean Score", 
+       y = '% Agreeing That "A Job is Alright But What\nMost Women Really Want is a Home and Children"') + 
+  ggtitle("All Country-Years") +
+  geom_label(data = wantch_label, aes(label = label), size = 3)
+
+# cross-section
+familywoman <- dcpo_input_balance$data %>% 
+  filter(item == "familywoman4 3 or higher") %>% 
+  mutate(iso2c = countrycode::countrycode(country,
+                             origin = "country.name",
+                             destination = "iso2c"),
+         prop = 1 - y_r/n_r,
+         se = sqrt((prop*(1-prop))/n),
+         prop_90 = prop + qnorm(.9)*se,
+         prop_10 = prop - qnorm(.9)*se) %>% 
+  left_join(theta_results %>% select(-kk, -tt), by = c("country", "year"))
+
+pge_familywoman <- pge %>% 
+  map(. %>% right_join(familywoman %>% 
+                         rowwise() %>% 
+                         transmute(country = country,
+                                   year = year,
+                                   prop = 1 - y_r/n_r,
+                                   se = sqrt((prop*(1-prop))/n),
+                                   familywoman = rnorm(1, mean = prop, sd = se)), 
+                       by = c("country", "year")))
+
+familywoman_cor <- map(pge_familywoman, function(x) 
+  with(x, cor(pge_mean, familywoman))) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2) %>% 
+  paste0("R = ", .)
+
+familywoman_label <- tibble(mean = .8, prop = .97, label = familywoman_cor)
+
+familywoman_plot <- familywoman %>% 
+  ggplot(aes(x = mean,
+             y = prop * 100)) +
+  geom_segment(aes(x = `10%`, xend = `90%`,
+                   y = prop * 100, yend = prop * 100),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_segment(aes(x = mean, xend = mean,
+                   y = prop_90 * 100, yend = prop_10 * 100),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_text(aes(label = iso2c), size = 2) +
+  geom_smooth(method = 'lm', se = FALSE) +
+  theme_bw() +
+  theme(legend.position="none",
+        axis.text  = element_text(size=8),
+        axis.title = element_text(size=9),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  coord_cartesian(ylim=c(0,100)) +
+  labs(x = "PGE Mean Score", 
+       y = '% Agreeing That "The Most Important Role of a\nWoman is to Take Care of Her Home and Family"') + 
+  ggtitle("Eurobarometer 87.4") +
+  geom_label(data = familywoman_label, aes(label = label), size = 3)
+
+# time series
+psw_de <- dcpo_input_balance$data %>% 
+  filter(item == "preschoolwork4 3 or higher" & country == "Germany") %>% 
+  mutate(prop = y_r/n_r,
+         se = sqrt((prop*(1-prop))/n),
+         prop_90 = prop + qnorm(.9)*se,
+         prop_10 = prop - qnorm(.9)*se) %>% 
+  right_join(theta_results %>% 
+               select(-kk, -tt) %>%
+               filter(country == "Germany"),
+             by = c("country", "year"))
+
+pge_de <- pge %>% 
+  map(. %>% right_join(psw_de %>% 
+                         rowwise() %>% 
+                         transmute(country = country,
+                                   year = year,
+                                   prop = y_r/n_r,
+                                   se = sqrt((prop*(1-prop))/n),
+                                   var = rnorm(1, mean = prop, sd = se)), 
+                       by = c("country", "year")))
+
+psw_de_cor <- map(pge_de, function(x) 
+  with(x, cor(pge_mean, var, use = "pairwise.complete.obs"))) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2) %>% 
+  paste0("R = ", .)
+
+psw_de_label <- tibble(year = 1990, mean = .8, label = psw_de_cor)
+
+psw_de_plot <- psw_de %>% 
+  ggplot(aes(x = year,
+             y = mean)) +
+  geom_line() +
+  geom_ribbon(aes(ymin = `10%`,
+                  ymax = `90%`,
+                  linetype = NA),
+               alpha = .2) +
+  geom_point(aes(y = prop),
+             na.rm = TRUE) +
+  geom_path(aes(y = prop),
+            linetype = 3,
+            na.rm = TRUE,
+            alpha = .7) +
+  geom_segment(aes(x = year, xend = year,
+                   y = prop_90, yend = prop_10),
+               na.rm = TRUE,
+               alpha = .2) +
+  annotate("text", x = 2010, y = .30, size = 2,
+           label = 'preschoolwork4,\nALLBUS, EVS, WVS') +
+  annotate("text", x = 1986, y = .66, size = 2,
+           label = "PGE Mean") +
+  labs(x = "Year", 
+       y = "Score") +
+  theme_bw() +
+  theme(legend.position="none",
+        axis.text  = element_text(size=8),
+        axis.title = element_text(size=9),
+        plot.title = element_text(hjust = 0.5, size = 11)) +
+  ggtitle("Germany") +
+  geom_label(data = psw_de_label, aes(label = label), size = 3)
+
+wantch_plot + familywoman_plot + psw_de_plot
+```
+
+In Figure&nbsp;\ref{surv_const_plot}, we move on to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
+For purposes of construct validation, we turn first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
+Although many of the items in this category are on their face at best only very tangentially related to public gender egalitarianism, others are plausibly causally related.
+Consider `wantch4`, an item asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children."
+As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
+Or, similarly, `familywoman4`, an item from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family."
+Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
+Indeed, the `tradroles` family of questions, which couple the `familywoman` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.
+If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
+In either case, they provide evidence of the validity of the PGE Mean scores.]
+In a slightly different vein, 
+With regard to both the internal and external items, the correlations are negative (as expected given the polarity of these questions) and are very strong.
+
+```{r cons_valid_plot, fig.cap="Construct Validation: Correlations Between PGE Mean Scores and Indicators of Workplace Gender Equality \\label{construct_plot}", fig.height=4}
+
+# https://genderstats.un.org/#/downloads
+lfpr_un <- read_csv(here::here("data", "3b - Labour force participation rate for persons aged 15+  by sex_data.csv"), skip = 1, col_types = "ccdcdcdccccccdddcc") %>% 
+  select(Country, Year, Sex, Value) %>% 
+  pivot_wider(names_from = Sex,
+              values_from = Value) %>% 
+  transmute(country = countrycode::countrycode(Country, 
+                                               origin = "country.name",
+                                               destination = "country.name"),
+            iso2c = countrycode::countrycode(country,
+                                             origin = "country.name",
+                                             destination = "iso2c"),
+            year = Year,
+            flfpr = Female,
+            f2m_ratio = round(Female/Male*100, 2)) %>% 
+  filter(!is.na(country) & !is.na(flfpr)) %>% 
+  left_join(theta_results, by = c("country", "year")) %>% 
+  filter(!is.na(mean))
+
+pge_lfpr <- pge %>% 
+  map(. %>% right_join(lfpr_un, 
+                       by = c("country", "year")))
+
+lfpr_cor <- map(pge_lfpr, function(x) {
+  x %>% 
+    filter(year == 2016) %>% 
+    with(cor(pge_mean, f2m_ratio))
+  }) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2) %>% 
+  paste0("R = ", .)
+
+lfpr_label <- tibble(mean = .15, f2m_ratio = 90, label = lfpr_cor)
+
+# https://stats.oecd.org/index.aspx?queryid=54753
+directors <- rsdmx::readSDMX("https://stats.oecd.org/restsdmx/sdmx.ashx/GetData/GENDER_EMP/.EMP11.WOMEN.TOTAL.2017/all?") %>% 
+  as_tibble() %>% 
+  transmute(country = countrycode::countrycode(COU, "iso3c", "country.name"),
+            iso2c = countrycode::countrycode(country,
+                                          origin = "country.name",
+                                          destination = "iso2c"),
+            year = as.numeric(TIME),
+            directors = obsValue) %>% 
+  filter(!is.na(country)) %>% 
+  inner_join(theta_results, by = c("country", "year"))
+
+directors_cor <- map(pge, function(x) {
+  x %>% 
+    inner_join(directors %>% select(country, year, directors),
+               by = c("country", "year")) %>% 
+    with(cor(pge_mean, directors))
+}) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2) %>% 
+  paste0("R = ", .)
+
+directors_label <- tibble(mean = .37, directors = 40, label = directors_cor)
+
+lfpr_plot <- ggplot(lfpr_un %>% filter(year==2016),
+       aes(x = mean,
+           y = f2m_ratio)) +
+  geom_segment(aes(x = `10%`, xend = `90%`,
+                   y = f2m_ratio, yend = f2m_ratio),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_text(aes(label = iso2c), size = 2) +
+  geom_smooth(method = 'lm', se = FALSE) +
+  theme_bw() + theme(legend.position="none",
+                     axis.text  = element_text(size=8),
+                     axis.title = element_text(size=9)) +
+  coord_cartesian(xlim=c(0, 1)) +
+  labs(x = "Mean Public Gender Egalitarianism, 2016", y = "Female to Male Labor Force Participation Ratio, 2016") +
+  geom_label(data = lfpr_label, aes(label = label))
+
+dir_plot <- ggplot(directors,
+       aes(x = mean,
+           y = directors)) +
+  geom_segment(aes(x = `10%`, xend = `90%`,
+                   y = directors, yend = directors),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_text(aes(label = iso2c), size = 2) +
+  geom_smooth(method = 'lm', se = FALSE) +
+  theme_bw() + theme(legend.position="none",
+                     axis.text  = element_text(size=8),
+                     axis.title = element_text(size=9)) +
+  coord_cartesian(xlim=c(.2, 1)) +
+  labs(x = "Mean Public Gender Egalitarianism, 2017", y = "% Women, Boards of Directors of the \n Largest Publicly Listed Companies, 2017") +
+  geom_label(data = directors_label, aes(label = label))
+
+lfpr_plot + dir_plot
+```
+
+Figure&nbsp;\ref{construct_plot} shows our tests of construct validation.
+Construct validation refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
+Assuming that attitudes toward gender egalitarianism in the public sphere both cause and are caused by women's gains in the workplace, assessing the relationships between the mean PGE and measures of workplace gender equality provides construct validation of our measure.
+In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the mean PGE index to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
+In the right panel, we plot the mean PGE index against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
+Both correlations are strong.
+As with our tests of convergent validation, these tests of construct validation provide reassuring evidence of the validity of the mean PGE.
 
@@
 One aspect of latent-variable estimates of public opinion like the PGE that is easy for researchers to overlook is the uncertainty in the estimates.
-But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
-Therefore, taking the uncertainty in the PGE index into account is crucial to reaching well-grounded conclusions.
+But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the mean PGE index---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
+Therefore, taking the uncertainty in the mean and polarization PGE indexes into account is crucial to reaching well-grounded conclusions.
 
-The PGE download includes pre-formatted data to facilitate incorporating the uncertainty in the index.
+The PGE download includes pre-formatted data to facilitate incorporating the uncertainty in the indexes.
 In R, the functions of the \texttt{purrr} package [@Henry2019, also included in the widely-used \texttt{tidyverse} package [@Wickham2017a]] make it entirely straightforward to incorporate the uncertainty of the PGE estimates.

### 2020-12-08 paper/dcpo_gender_roles.Rmd
fuss with fn re construct vs external convergent validation

@@
 Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
-Indeed, the `tradroles` family of questions, which couple the `familywoman` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.
-If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
-In either case, they provide evidence of the validity of the PGE Mean scores.]
+(Indeed, the `tradroles` series of questions, which couple the `familywoman4` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.)
+If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
+In either case, though, they provide evidence of the validity of the PGE Mean scores.]
 In a slightly different vein, 

### 2020-12-08 paper/dcpo_gender_roles.Rmd
add note re whiskers to validation plots; add to survey construct validation paragraph

@@
 
-internal_plot + internal_cs_plot + internal_us_plot
+internal_plot + internal_cs_plot + internal_us_plot +
+  plot_annotation(caption = "Note: Gray whiskers and shading represent 80% credible intervals.")
 ```
@@
 
-wantch_plot + familywoman_plot + psw_de_plot
+wantch_plot + familywoman_plot + psw_de_plot +
+  plot_annotation(caption = "Note: Gray whiskers and shading represent 80% credible intervals.")
 ```
@@
 In Figure&nbsp;\ref{surv_const_plot}, we move on to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
-For purposes of construct validation, we turn first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
+For purposes of construct validation, we look first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
 Although many of the items in this category are on their face at best only very tangentially related to public gender egalitarianism, others are plausibly causally related.
-Consider `wantch4`, an item asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children."
+Consider `wantch4`, an item depicted in the left pane asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children."
 As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
-Or, similarly, `familywoman4`, an item from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family."
+Or, similarly, `familywoman4`, an item plotted in the center pane from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family."
 Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
@@
 In either case, though, they provide evidence of the validity of the PGE Mean scores.]
-In a slightly different vein, 
-With regard to both the internal and external items, the correlations are negative (as expected given the polarity of these questions) and are very strong.
+In a slightly different vein, `preschoolwork4`, included in the German ALLBUS, the World Values Survey, and the European Values Survey, asked respondents the extent to which they agreed that "a pre-school child is likely to suffer if his or her mother works;" we plot the time series of the proportion of the population of Germany estimated to disagree or disagree strongly with this statement in the right pane.
+The belief that mothers working cause harm to their children should be expected to lead to disfavoring gender equality in workforce to avoid this purported negative consequence. 
+With regard to all of these items, too, the correlations with the PGE Mean scores are strong.
 
@@
 
-lfpr_plot + dir_plot
+lfpr_plot + dir_plot +
+  plot_annotation(caption = "Note: Gray whiskers represent 80% credible intervals.")
 ```

### 2020-12-08 paper/dcpo_gender_roles.Rmd
combine all source data plots together in one figure

@@
 From a more optimistic standpoint, we note there there are `r n_cy` country-years in which we have at least _some_ information about the public gender egalitarianism of the population, that is, some `r {back_to_numeric(n_cy)/back_to_numeric(spanned_cy) * 100} %>% round()`% of the `r spanned_cy` country-years spanned by the data we collected.
-But there is no gainsaying that the many different survey items employed renders these data difficult to use together.
-
-```{r item_and_country_plots, fig.height=3, fig.cap = "Items and Countries with the Most Observations in the Source Data \\label{item_country_plots}"}
+But there can be no gainsaying that the many different survey items employed renders these data difficult to use together.
+
+```{r item_and_country_plots, fig.height = 3.5, fig.cap = "Items, Countries, and Years with the Most Observations in the PGE Source Data \\label{item_country_plots}"}
 items_plot <- dcpo_input_raw_public1 %>%
@@
         axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
+        axis.title.y = element_text(size = 9),
         plot.title = element_text(hjust = 0.5, size = 11)) +
-  ylab("Country-Years Observed") +
+  ylab("Country-Years\nObserved") +
   ggtitle("Items")
@@
         axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
+        axis.title.y = element_text(size = 9),
         plot.title = element_text(hjust = 0.5, size = 11)) +
-  ylab("Year-Items Observed") +
+  ylab("Year-Items\nObserved") +
   ggtitle("Countries")
 
-us_obs <- dcpo_input_raw_public1 %>% 
-  distinct(country, year, item) %>%
-  count(country) %>%
-  filter(country == "United States") %>%
-  pull(n)
-
-others <- dcpo_input_raw_public1 %>%
-  distinct(country, year, item) %>%
-  count(country) %>%
-  arrange(desc(n)) %>%
-  slice(2:5) %>%
-  pull(country) %>% 
-  paste(collapse = ", ") %>% 
-  str_replace(", (\\w+)$", ", and \\1")
-
-data_poorest <- dcpo_input_raw_public1 %>%
-  distinct(country, year, item) %>%
-  count(country) %>%
-  arrange(n) %>%
-  filter(n == 2) %>%
-  pull(country) %>% 
-  paste(collapse = ", ") %>% 
-  str_replace(", (\\w+)$", ", and \\1")
-
-wordify_numeral <- function(x) setNames(c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen", " seventeen", "eighteen", "nineteen"), 1:19)[x]
-
-n_data_poorest <- {data_poorest %>%
-    str_split(",") %>% 
-    first()} %>% 
-  length() %>% 
-  wordify_numeral()
-
-items_plot + countries_plot
-```
-
-The left panel of Figure&nbsp;\ref{item_country_plots} displays in how many country-years each of the twelve most-commonly asked survey items are available.
-The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
-Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
-That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
-
-Which countries are the most data-rich?
-The right panel of Figure&nbsp;\ref{item_country_plots} shows the dozen countries with the highest count of country-year-item observations.
-The United States, with `r us_obs` observations, is far and away the best represented country in the source data, followed by `r others`.
-At the other end of the spectrum, `r n_data_poorest` countries---`r data_poorest`---have only the minimum two observations required to be included in the source dataset at all.
-
-```{r years_by_country, fig.cap="Country-Year Coverage in the Source Data \\label{countries_by_years}"}
 cby_plot <- dcpo_input_raw_public1 %>%
@@
         axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
+        axis.title.y = element_text(size = 9),
         plot.title = element_text(hjust = 0.5, size = 11)) +
-  ylab("Years Observed") +
+  ylab("Years\nObserved") +
   ggtitle("Countries")
@@
         axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
+        axis.title.y = element_text(size = 9),
         plot.title = element_text(hjust = 0.5, size = 11)) +
-  ylab("Countries Observed") +
+  ylab("Countries\nObserved") +
   ggtitle("Years")
 
-cby_plot + ybc_plot
-```
+us_obs <- dcpo_input_raw_public1 %>% 
+  distinct(country, year, item) %>%
+  count(country) %>%
+  filter(country == "United States") %>%
+  pull(n)
+
+others <- dcpo_input_raw_public1 %>%
+  distinct(country, year, item) %>%
+  count(country) %>%
+  arrange(desc(n)) %>%
+  slice(2:5) %>%
+  pull(country) %>% 
+  paste(collapse = ", ") %>% 
+  str_replace(", (\\w+)$", ", and \\1")
+
+data_poorest <- dcpo_input_raw_public1 %>%
+  distinct(country, year, item) %>%
+  count(country) %>%
+  arrange(n) %>%
+  filter(n == 2) %>%
+  pull(country) %>% 
+  paste(collapse = ", ") %>% 
+  str_replace(", (\\w+)$", ", and \\1")
+
+wordify_numeral <- function(x) setNames(c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen", " seventeen", "eighteen", "nineteen"), 1:19)[x]
+
+n_data_poorest <- {data_poorest %>%
+    str_split(",") %>% 
+    first()} %>% 
+  length() %>% 
+  wordify_numeral()
+
+(items_plot + countries_plot) / (cby_plot + ybc_plot)
+```
+
+The left panel of Figure&nbsp;\ref{item_country_plots} displays in how many country-years each of the twelve most-commonly asked survey items are available.
+The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
+Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
+That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
+
+Which countries are the most data-rich?
+The right panel of Figure&nbsp;\ref{item_country_plots} shows the dozen countries with the highest count of country-year-item observations.
+The United States, with `r us_obs` observations, is far and away the best represented country in the source data, followed by `r others`.
+At the other end of the spectrum, `r n_data_poorest` countries---`r data_poorest`---have only the minimum two observations required to be included in the source dataset at all.
 
@@
 
-```{r convergent, fig.cap="Convergent Validation: Correlations Between PGE Mean Scores and Individual Public Gender Equality Survey Items \\label{conv_plot}", fig.height=4}
+```{r convergent, fig.cap="Convergent Validation: Correlations Between PGE Mean Scores and Individual PGE Source Data Survey Items \\label{conv_plot}", fig.height=4}
 
@@
 
-```{r construct_validation_survey, fig.cap="Construct Validation: Correlations Between PGE Mean Scores and Individual 'Balancing' Gender Equality Survey Items \\label{surv_const_plot}", fig.height=4}
+```{r construct_validation_survey, fig.cap="Construct Validation: Correlations Between PGE Mean Scores and Individual 'Balancing' Gender Egalitarianism Survey Items \\label{surv_const_plot}", fig.height=4}
 dcpo_input_balance <- DCPOtools::format_dcpo(dcpo_input_raw_balance1,

### 2020-12-09 paper/dcpo_gender_roles.Rmd
revise covergent validation paragraph for length, keeping more detailed description in comments for convenient reference just in case

@@
 # Validating Public Gender Egalitarianism
-We turn now to the validity of the PGE Mean scores.
-Like @Caughey2019 [684-685], we provide evidence of our new measure's validity through tests of both convergent validation and construct validation.
+We consider now the validity of the PGE Mean scores.
+Like @Caughey2019 [684-685], we provide evidence of our new measures' validity with both convergent validation and construct validation tests.
 
@@
 Here, we compare PGE Mean scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
-In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women."
-Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders."
-Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country.
-The U.S. General Social Survey asked this question 25 times from 1972 to 2016.
-It asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women"; to facilitate visual comparison of the longitudinal relationship, we plot the estimated population proportion that disagreed with the statement.
+In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years.
+<!-- In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women." -->
+Then, in the center panel, we look at the question that provides most data-rich cross-section.
+<!-- Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders." -->
+Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the item with the largest number of observations for a single country. 
+<!-- Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country.
+-->
+<!-- The U.S. General Social Survey asked this question 25 times from 1972 to 2016. -->
+<!-- It asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women"; to facilitate visual comparison of the longitudinal relationship, we plot the estimated population proportion that disagreed with the statement.
+-->
 In every case, the correlations---estimated taking into account the uncertainty in the measures^[The uncertainty in the PGE Mean score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the `polileader4` question, but failing to account for this uncertainty would overstate the correlation with the Pew `poliequal3` item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S.
@@
 
-In Figure&nbsp;\ref{surv_const_plot}, we move on to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
+In Figure&nbsp;\ref{surv_const_plot}, we turn to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
 For purposes of construct validation, we look first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
@@
 
-Figure&nbsp;\ref{construct_plot} shows our tests of construct validation.
-Construct validation refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
+Figure&nbsp;\ref{construct_plot} shows additional tests of construct validation.
 Assuming that attitudes toward gender egalitarianism in the public sphere both cause and are caused by women's gains in the workplace, assessing the relationships between the mean PGE and measures of workplace gender equality provides construct validation of our measure.

### 2020-12-09 paper/dcpo_gender_roles.Rmd
expand convergent validation para a bit; revise construct validation paras for length; clean up

@@
 <!-- Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.     -->
-
-# Multi-Dimensionality in Gender Egalitarianism
-
-Gender egalitarianism does not have only one dimension but a multi-dimension.
-Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
-For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
-To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework.
-Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting.
-The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions.
-However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.
+<!-- Gender egalitarianism does not have only one dimension but a multi-dimension. -->
+<!-- Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
+-->
+<!-- For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not. -->
+<!-- To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework. -->
+<!-- Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting. -->
+<!-- The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions. -->
+<!-- However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.
+-->
+
+# Focusing on Public Opinion Toward Gender Equality in the Public Sphere
 
@@
 
-To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE index.
+To avoid any potential multidimensionality in the Public Gender Egalitarianism data, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE index.
 The complete list of gender egalitarianism items is included in the Appendix.]
-Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
+Thus, the "Public" in the name of the dataset does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
 In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.
@@
 
-# The Source Data on Gender Egalitarian Attitudes
+# The Source Data on Public Gender Egalitarianism
 
@@
 <!-- In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women." -->
-Then, in the center panel, we look at the question that provides most data-rich cross-section.
+Then, in the center panel, we look at the question that provides most data-rich cross-section, the `poliequal3` item in Pew Global's Spring 2007 survey.
 <!-- Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders." -->
-Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the item with the largest number of observations for a single country. 
+Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the item with the largest number of observations for a single country, the `emopoli2` survey item, which asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women."
 <!-- Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country.
@@
 
-In Figure&nbsp;\ref{surv_const_plot}, we turn to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
-For purposes of construct validation, we look first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
-Although many of the items in this category are on their face at best only very tangentially related to public gender egalitarianism, others are plausibly causally related.
-Consider `wantch4`, an item depicted in the left pane asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children."
-As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
-Or, similarly, `familywoman4`, an item plotted in the center pane from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family."
-Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
-(Indeed, the `tradroles` series of questions, which couple the `familywoman4` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.)
-If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
-In either case, though, they provide evidence of the validity of the PGE Mean scores.]
-In a slightly different vein, `preschoolwork4`, included in the German ALLBUS, the World Values Survey, and the European Values Survey, asked respondents the extent to which they agreed that "a pre-school child is likely to suffer if his or her mother works;" we plot the time series of the proportion of the population of Germany estimated to disagree or disagree strongly with this statement in the right pane.
-The belief that mothers working cause harm to their children should be expected to lead to disfavoring gender equality in workforce to avoid this purported negative consequence. 
-With regard to all of these items, too, the correlations with the PGE Mean scores are strong.
+We turn to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
+In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
+Assuming that attitudes that women should prioritize housework and childcare over education, politics, and paid employment---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE Mean score.
+Exemplars of such items across all available country-years ("a job is alright but what most women really want is a home and children" from the WVS and EVS), in cross-section ("the most important role of a woman is to take care of her home and family" from the Eurobarometer 87.4), and in time series ("a pre-school child is likely to suffer if his or her mother works" from the German ALLBUS, WVS, and EVS) all show strong correlations with the PGE Mean scores.
+<!-- Consider `wantch4`, an item depicted in the left pane asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children." -->
+<!-- As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
+-->
+<!-- Or, similarly, `familywoman4`, an item plotted in the center pane from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family."  -->
+<!-- Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
+-->
+<!-- (Indeed, the `tradroles` series of questions, which couple the `familywoman4` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.) -->
+<!-- If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
+-->
+<!-- In either case, though, they provide evidence of the validity of the PGE Mean scores.] -->
+<!-- In a slightly different vein, `preschoolwork4`, included in the German ALLBUS, the World Values Survey, and the European Values Survey, asked respondents the extent to which they agreed that "a pre-school child is likely to suffer if his or her mother works;" we plot the time series of the proportion of the population of Germany estimated to disagree or disagree strongly with this statement in the right pane.
+-->
+<!-- The belief that mothers working cause harm to their children should be expected to lead to disfavoring gender equality in workforce to avoid this purported negative consequence.  -->
+<!-- With regard to all of these items, too, the correlations with the PGE Mean scores are strong. -->
 
@@
 
-Figure&nbsp;\ref{construct_plot} shows additional tests of construct validation.
-Assuming that attitudes toward gender egalitarianism in the public sphere both cause and are caused by women's gains in the workplace, assessing the relationships between the mean PGE and measures of workplace gender equality provides construct validation of our measure.
-In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the mean PGE index to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
-In the right panel, we plot the mean PGE index against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
+Finally, Figure&nbsp;\ref{construct_plot} shows additional tests of construct validation.
+As attitudes toward gender egalitarianism in the public sphere plausibly both cause and are caused by women's gains in the workplace, strong relationships between the PGE Mean scores and measures of workplace gender equality provide construct validation for our measure.
+In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE Mean scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
+In the right panel, we plot the PGE Mean scores against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
 Both correlations are strong.
-As with our tests of convergent validation, these tests of construct validation provide reassuring evidence of the validity of the mean PGE.
-
-# Using the Public Gender Egalitarianism Index
-
-One aspect of latent-variable estimates of public opinion like the PGE that is easy for researchers to overlook is the uncertainty in the estimates.
-But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the mean PGE index---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
-Therefore, taking the uncertainty in the mean and polarization PGE indexes into account is crucial to reaching well-grounded conclusions.
-
-The PGE download includes pre-formatted data to facilitate incorporating the uncertainty in the indexes.
+Together, this evidence of construct validation and convergent validation attests to the validity of the PGE Mean scores as measures of public opinion towards gender equality in the public sphere.
+
+# Using the Public Gender Egalitarianism Dataset
+
+One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the uncertainty in the estimates.
+But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE Mean scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
+Therefore, taking the uncertainty in the PGE Mean and Polarization scores into account is crucial to reaching well-grounded conclusions.
+
+The download includes pre-formatted data to facilitate incorporating the uncertainty in the PGE Mean and Polarization scores.
 In R, the functions of the \texttt{purrr} package [@Henry2019, also included in the widely-used \texttt{tidyverse} package [@Wickham2017a]] make it entirely straightforward to incorporate the uncertainty of the PGE estimates.

### 2020-12-09 paper/dcpo_gender_roles.Rmd
clean up

@@
 
-To avoid any potential multidimensionality in the Public Gender Egalitarianism data, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE index.
+To avoid any potential multidimensionality in the Public Gender Egalitarianism data, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as the `tradroles` questions, "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE source data.
 The complete list of gender egalitarianism items is included in the Appendix.]
@@
 
-# The Source Data on Public Gender Egalitarianism
+# Examining the Source Data on Public Gender Egalitarianism
 

### 2020-12-09 paper/dcpo_gender_roles.Rmd
finish "Using" section

@@
 The complete list of gender egalitarianism items is included in the Appendix.]
-Thus, the "Public" in the name of the dataset does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
+Thus, the "Public" in the name of the dataset does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to its attitudes specifically on this _public_ aspect of gender egalitarianism.
 In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.
@@
 # Using the Public Gender Egalitarianism Dataset
+Version 1.0 of the PGE dataset includes PGE Mean and Polarization scores for `r pge[[1]] %>% distinct(country) %>% nrow()` countries for as many years as possible from 1972 to the present, a total of `r pge[[1]] %>% nrow()` country-years.
+It can be accessed in two ways: via a user-friendly web application on the PGE website, which plots scores for as many as four countries for easy comparison of levels and trends, and via the Harvard Dataverse, where the entire dataset is available for download for use in statistical analysis.
+We will revise and update the dataset as new survey data on public gender egalitarianism becomes available.
 

### 2020-12-15 paper/dcpo_gender_roles.Rmd
rewrite cs_plot to facilitate varying the number of facets; other minor fussing

@@
 The second category, in turn, encompasses questions focusing on gender equality in the traditionally feminine private sphere of housework and childcare.
-A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only rarely included in surveys.^[One laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly becoming more common, is the item querying respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
+A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only rarely included in surveys.^[
+One laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly becoming more common, is the item querying respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
 The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.
 
-To avoid any potential multidimensionality in the Public Gender Egalitarianism data, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as the `tradroles` questions, "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE source data.
+To avoid any potential multidimensionality in the Public Gender Egalitarianism data, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[
+Items that fell into both the first category and another, such as the `tradroles` questions---those with stems of the form "A man's job is to earn money; a woman's job is to look after the home and family"---which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE source data.
 The complete list of gender egalitarianism items is included in the Appendix.]
@@
 
-```{r cs_plot, fig.cap="PGE Mean and Polarization Scores, Most Recent Available Year \\label{cs_mry}", fig.height=8}
+```{r cs_plot, fig.cap="PGE Scores, Most Recent Available Year \\label{cs_mry}", fig.height=4}
 load(here::here("data", "dcpo_input.rda"))
@@
 
-sigma_results <- DCPO::summarize_dcpo_results(dcpo_input,
-                                              dcpo_output,
-                                              "sigma")
+n_panes <- 3
 
@@
   ungroup() %>%
-    arrange(-mean) %>%
-    mutate(half = ntile(mean, 2),
-           country = paste0(country, " (", year, ")"))
-
-p1_data_a <- p1_data %>% 
-  filter(half==2) %>% 
-  mutate(ranked = as.factor(row_number(mean)))
-p1_data_b <- p1_data %>%
-  filter(half==1) %>%
-  mutate(ranked = as.factor(row_number(mean)),
-         country = str_replace(country, "’", "'"))
-
-p1a <- ggplot(p1_data_a, aes(x = mean,
-                             y = ranked)) +
-    geom_segment(aes(x = `10%`, xend = `90%`,
-                     y = ranked, yend = as.factor(ranked)),
-                 na.rm = TRUE) +
-    geom_point(fill = "black", shape = 21, size = 1.1, na.rm = TRUE) +
+  arrange(mean) %>%
+  transmute(country_year = paste0(country, " (", year, ")") %>% 
+              str_replace("’", "'"),
+            estimate = mean,
+            conf.high = `90%`,
+            conf.low = `10%`,
+            pane = n_panes - (ntile(mean, n_panes) - 1),
+            ranked = as.factor(ceiling(row_number())))
+
+p_theta <- ggplot(p1_data,
+                  aes(x = estimate, y = ranked)) +
+  geom_segment(aes(x = conf.low, xend = conf.high,
+                   y = ranked, yend = ranked),
+               na.rm = TRUE,
+               alpha = .2) +
+  geom_point(fill = "black", shape = 21, size = .5, na.rm = TRUE) +
   theme_bw() + theme(legend.position="none",
-                       axis.text.x  = element_text(size=8),
-                       axis.text.y  = element_text(size=8),
-                       axis.title.x = element_text(face="bold", size=8),
-                       legend.text = element_text(size = 7),
-                       legend.title = element_text(size=7, face = "bold"),
-                       legend.key.size = unit(.5, "line"),
-                       legend.background = element_rect(linetype = "solid",
-                                                        color = "grey80",
-                                                        size = .25),
-                       legend.key = element_rect(colour = "white")) +
-    scale_y_discrete(breaks = p1_data_a$ranked, labels=p1_data_a$country) +
+                     axis.text.x  = element_text(size=7,
+                                                 angle = 90,
+                                                 vjust = .45,
+                                                 hjust = .95),
+                     axis.text.y  = element_text(size=7),
+                     axis.title = element_blank(),
+                     strip.background = element_blank(), 
+                     strip.text = element_blank(),
+                     panel.grid.major = element_line(size = .3),
+                     panel.grid.minor = element_line(size = .15)) +
+  scale_y_discrete(breaks = p1_data$ranked, labels=p1_data$country_year) +
   coord_cartesian(xlim=c(0, 1)) +
-    labs(x = NULL, y = NULL)
-
-p1b <- ggplot(p1_data_b, aes(x = mean,
-                             y = ranked)) +
-    geom_segment(aes(x = `10%`, xend = `90%`,
-                     y = ranked, yend = ranked),
-                 na.rm = TRUE) +
-    geom_point(fill = "black", shape = 21, size = 1.1, na.rm = TRUE) +
-    theme_bw() + theme(legend.position="none",
-                       axis.text.x  = element_text(size=8),
-                       axis.text.y  = element_text(size=8),
-                       axis.title.x = element_text(face="bold", size=8)) +
-    scale_y_discrete(breaks = p1_data_b$ranked, labels=p1_data_b$country) +
-    coord_cartesian(xlim=c(0, 1)) +
-    labs(x = NULL, y = NULL)
-
-p1a + p1b
+  facet_wrap(vars(pane), scales = "free", nrow = 1)
+
+p_theta +
+  plot_annotation(caption = "Note: Gray whiskers represent 80% credible intervals.")
 
@@
 # Validating Public Gender Egalitarianism
-We consider now the validity of the PGE Mean scores.
-Like @Caughey2019 [684-685], we provide evidence of our new measures' validity with both convergent validation and construct validation tests.
+We consider now the validity of the PGE scores.
+Like @Caughey2019 [684-685], we provide evidence of our measure's validity with  convergent validation and construct validation.
 
@@
 
-```{r convergent, fig.cap="Convergent Validation: Correlations Between PGE Mean Scores and Individual PGE Source Data Survey Items \\label{conv_plot}", fig.height=4}
+```{r convergent, fig.cap="Convergent Validation: Correlations Between PGE Scores and Individual PGE Source Data Survey Items \\label{conv_plot}", fig.height=4}
 
@@
   scale_x_continuous(breaks=seq(.1, .9, 0.2)) +
-  labs(x = "PGE Mean Score", 
+  labs(x = "PGE Score", 
        y = '% Agreeing That "On the Whole, Men\nMake Better Political Leaders than Women Do"') + 
@@
         plot.title = element_text(hjust = 0.5, size = 11)) +
-  labs(x = "PGE Mean Score", 
+  labs(x = "PGE Score", 
        y = '% Opining That "Men Generally Make\nBetter Political Leaders Than Women"') + 
@@
   geom_point(aes(y = prop),
+             fill = "black",
+             shape = 21,
+             size = .5,
              na.rm = TRUE) +
@@
 
-Figure&nbsp;\ref{conv_plot} displays our tests of convergent validation.
-Convergent validation refers to demonstrating that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
-Here, we compare PGE Mean scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
+Figure&nbsp;\ref{conv_plot} displays our demonstrations of convergent validation.
+Convergent validation refers to showing that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
+Here, we compare PGE scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
 In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years.
@@
 <!-- Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders." -->
-Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the item with the largest number of observations for a single country, the `emopoli2` survey item, which asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women."
-<!-- Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country.
+Finally, in the right panel, to evaluate how well the PGE score captures change over time, we focus on the item with the largest number of observations for a single country, the `emopoli2` survey item, which asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women."
+<!-- Finally, in the right panel, to evaluate how well the PGE score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country.
 -->
@@
 -->
-In every case, the correlations---estimated taking into account the uncertainty in the measures^[The uncertainty in the PGE Mean score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the `polileader4` question, but failing to account for this uncertainty would overstate the correlation with the Pew `poliequal3` item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S.
+In every case, the correlations---estimated taking into account the uncertainty in the measures^[
+The uncertainty in the PGE score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the `polileader4` question, but failing to account for this uncertainty would overstate the correlation with the Pew `poliequal3` item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S.
 GSS `emopoli2` item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`.
@@
 
-```{r construct_validation_survey, fig.cap="Construct Validation: Correlations Between PGE Mean Scores and Individual 'Balancing' Gender Egalitarianism Survey Items \\label{surv_const_plot}", fig.height=4}
+```{r construct_validation_survey, fig.cap="Construct Validation: Correlations Between PGE Scores and Individual 'Balancing' Gender Egalitarianism Survey Items \\label{surv_const_plot}", fig.height=4}
 dcpo_input_balance <- DCPOtools::format_dcpo(dcpo_input_raw_balance1,
@@
   coord_cartesian(ylim=c(0,100)) +
-  labs(x = "PGE Mean Score", 
+  labs(x = "PGE Score", 
        y = '% Agreeing That "A Job is Alright But What\nMost Women Really Want is a Home and Children"') + 
@@
   coord_cartesian(ylim=c(0,100)) +
-  labs(x = "PGE Mean Score", 
+  labs(x = "PGE Score", 
        y = '% Agreeing That "The Most Important Role of a\nWoman is to Take Care of Her Home and Family"') + 
@@
 
-We turn to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
+We move on, then, to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
 In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
-Assuming that attitudes that women should prioritize housework and childcare over education, politics, and paid employment---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE Mean score.
-Exemplars of such items across all available country-years ("a job is alright but what most women really want is a home and children" from the WVS and EVS), in cross-section ("the most important role of a woman is to take care of her home and family" from the Eurobarometer 87.4), and in time series ("a pre-school child is likely to suffer if his or her mother works" from the German ALLBUS, WVS, and EVS) all show strong correlations with the PGE Mean scores.
+Assuming that attitudes that women should prioritize housework and childcare over education, politics, and paid employment---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE score.
+Exemplars of such items across all available country-years ("a job is alright but what most women really want is a home and children" from the WVS and EVS), in cross-section ("the most important role of a woman is to take care of her home and family" from the Eurobarometer 87.4), and in time series ("a pre-school child is likely to suffer if his or her mother works" from the German ALLBUS, WVS, and EVS) all show strong correlations with the PGE scores.
 <!-- Consider `wantch4`, an item depicted in the left pane asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children." -->
@@
 <!-- Or, similarly, `familywoman4`, an item plotted in the center pane from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family."  -->
-<!-- Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
+<!-- Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[
+One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
 -->
@@
 -->
-<!-- In either case, though, they provide evidence of the validity of the PGE Mean scores.] -->
+<!-- In either case, though, they provide evidence of the validity of the PGE scores.] -->
 <!-- In a slightly different vein, `preschoolwork4`, included in the German ALLBUS, the World Values Survey, and the European Values Survey, asked respondents the extent to which they agreed that "a pre-school child is likely to suffer if his or her mother works;" we plot the time series of the proportion of the population of Germany estimated to disagree or disagree strongly with this statement in the right pane.
@@
 <!-- The belief that mothers working cause harm to their children should be expected to lead to disfavoring gender equality in workforce to avoid this purported negative consequence.  -->
-<!-- With regard to all of these items, too, the correlations with the PGE Mean scores are strong. -->
-
-```{r cons_valid_plot, fig.cap="Construct Validation: Correlations Between PGE Mean Scores and Indicators of Workplace Gender Equality \\label{construct_plot}", fig.height=4}
+<!-- With regard to all of these items, too, the correlations with the PGE scores are strong. -->
+
+```{r cons_valid_plot, fig.cap="Construct Validation: Correlations Between PGE Scores and Indicators of Workplace Gender Equality \\label{construct_plot}", fig.height=4}
 
@@
   coord_cartesian(xlim=c(0, 1)) +
-  labs(x = "Mean Public Gender Egalitarianism, 2016", y = "Female to Male Labor Force Participation Ratio, 2016") +
+  labs(x = "Public Gender Egalitarianism, 2016", y = "Female to Male Labor Force Participation Ratio, 2016") +
   geom_label(data = lfpr_label, aes(label = label))
@@
   coord_cartesian(xlim=c(.2, 1)) +
-  labs(x = "Mean Public Gender Egalitarianism, 2017", y = "% Women, Boards of Directors of the \n Largest Publicly Listed Companies, 2017") +
+  labs(x = "Public Gender Egalitarianism, 2017", y = "% Women, Boards of Directors of the \n Largest Publicly Listed Companies, 2017") +
   geom_label(data = directors_label, aes(label = label))
@@
 Finally, Figure&nbsp;\ref{construct_plot} shows additional tests of construct validation.
-As attitudes toward gender egalitarianism in the public sphere plausibly both cause and are caused by women's gains in the workplace, strong relationships between the PGE Mean scores and measures of workplace gender equality provide construct validation for our measure.
-In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE Mean scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
-In the right panel, we plot the PGE Mean scores against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
+As attitudes toward gender egalitarianism in the public sphere plausibly both cause and are caused by women's gains in the workplace, strong relationships between the PGE scores and measures of workplace gender equality provide construct validation for our measure.
+In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
+In the right panel, we plot the PGE scores against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
 Both correlations are strong.
-Together, this evidence of construct validation and convergent validation attests to the validity of the PGE Mean scores as measures of public opinion towards gender equality in the public sphere.
+Together, this evidence of construct validation and convergent validation attests to the validity of the PGE scores as measures of public opinion towards gender equality in the public sphere.
 
 # Using the Public Gender Egalitarianism Dataset
-Version 1.0 of the PGE dataset includes PGE Mean and Polarization scores for `r pge[[1]] %>% distinct(country) %>% nrow()` countries for as many years as possible from 1972 to the present, a total of `r pge[[1]] %>% nrow()` country-years.
+Version 1.0 of the PGE dataset includes PGE scores for `r pge[[1]] %>% distinct(country) %>% nrow()` countries for as many years as possible from 1972 to the present, a total of `r pge[[1]] %>% nrow()` country-years.
 It can be accessed in two ways: via a user-friendly web application on the PGE website, which plots scores for as many as four countries for easy comparison of levels and trends, and via the Harvard Dataverse, where the entire dataset is available for download for use in statistical analysis.
@@
 One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the uncertainty in the estimates.
-But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE Mean scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
-Therefore, taking the uncertainty in the PGE Mean and Polarization scores into account is crucial to reaching well-grounded conclusions.
-
-The download includes pre-formatted data to facilitate incorporating the uncertainty in the PGE Mean and Polarization scores.
+But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
+Therefore, taking the uncertainty in the PGE scores into account is crucial to reaching well-grounded conclusions.
+
+The download includes pre-formatted data to facilitate incorporating the uncertainty in the PGE scores.
 In R, the functions of the \texttt{purrr} package [@Henry2019, also included in the widely-used \texttt{tidyverse} package [@Wickham2017a]] make it entirely straightforward to incorporate the uncertainty of the PGE estimates.
@@
 
-# Conclusion
-
 \pagebreak

### 2020-12-20 paper/dcpo_gender_roles.Rmd
draft section on estimation

@@
   group_by(country) %>% 
-  summarize(years = max(year) - min(year)) %>% 
+  summarize(years = max(year) - min(year) + 1) %>% 
   summarize(n = sum(years)) %>% 
@@
 
-Together, these survey items were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
-Considering that observations for every year in each country surveyed would number `r total_cy` and so a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations.
+Together, the survey items in the source data were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
+Considering that observations for every year in each country surveyed would number `r total_cy`, a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations.
 Viewed from this perspective of complete data, the available data can be seen to be very, very sparse.
@@
 
-The DCPO model is estimated using the `DCPO` package for R [@Solt2020a], which is written in the Stan probabilistic programming language [@StanDevTeam2019a; @StanDevTeam2019b].
+There has been a recent blossoming of scholarship developing latent variable models of public opinion based on cross-national survey data [see @Claassen2019; @Caughey2019; @McGann2019; @Kolczynska2020].
+To estimate public gender egalitarianism across countries and over time, we draw on the latest of these methods that is appropriate for data that is not only incomparable but also sparse, the Dynamic Comparative Public Opinion  (DCPO) model presented in @Solt2020c.^[
+@Solt2020 demonstrates that the DCPO model provides a better fit to survey data than the models put forward by @Claassen2019 or @Caughey2019.
+The @McGann2019 model depends on dense survey data unlike the sparse data on public gender egalitarianism described in the preceding section.
+@Kolczynska2020 is the very most recent of the five works and builds on each of the others, but the MRP approach developed in that piece is suitable only when the available survey data are dense and ancillary data on population characteristics are also available, so it is similarly inappropriate to this application.
+]
+
+The DCPO model is a population-level two-parameter ordinal logistic item response theory (IRT) model with country-specific item bias.
+That is, $\eta_{ktqr}$, the expected probability that a random person in country $k$ at time $t$ answers question $q$ with a response at least as positive as response $r$, is estimated as varying with the mean and standard deviation of the unbounded latent trait of public opinion, $\bar{\theta'}_{kt}$ and $\sigma_{kt}$; with the dispersion, $\alpha_{q}$, of the question and the difficulty, $\beta_{qr}$, of the question's response category; as well as with a term to capture how responses to particular questions in particular questions may be biased, $\delta_{kq}$: $\eta_{ktqr} = \textrm{logit}^{-1}(\frac{\bar{\theta'}_{kt} - (\beta_{qr} + \delta_{kq})}{\sqrt{\alpha_{q}^2 + (1.7*\sigma_{kt})^2}}) \label{eq:dcpo}$.
+A beta-binomial distribution is used to model the observed survey data given $\eta_{ktqr}$, random-walk priors are used to account for the dynamics in $\bar{\theta'}_{kt}$ and $\sigma_{kt}$, and weakly informative priors are placed on the other parameters.
+Finally, the logistic function is used to transform $\bar{\theta'}_{kt}$ to the unit interval and so give the bounded mean of latent public opinion, $\bar{\theta}_{kt}$, which is our parameter of interest here [see @Solt2020c, 3-8].
 
@@
 save(dcpo_output, file = here::here("data", "dcpo_output.rda"))
-
-dcpo_theta <- rstan::extract(dcpo_output, pars = "theta")
-
-save(dcpo_theta, file = here::here("data", "dcpo_theta.rda"))
-
-dcpo_sigma <- rstan::extract(dcpo_output, pars = "sigma")
-
-save(dcpo_theta, file = here::here("data", "dcpo_sigma.rda"))
-
-dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")
-
-save(dcpo_input, dcpo_y_r_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
-```
-
-```{r cs_plot, fig.cap="PGE Scores, Most Recent Available Year \\label{cs_mry}", fig.height=4}
+```
+
+```{r dcpo_results_summary}
 load(here::here("data", "dcpo_input.rda"))
@@
                                               "theta")
+
+res_cy <- nrow(theta_results) %>% 
+  scales::comma()
+
+res_c <- theta_results %>% 
+  pull(country) %>% 
+  unique() %>% 
+  length()
+```
+
+We used the `DCPO` package for R [@Solt2020a] to estimate this model on the public gender egalitarianism source data described above.
+The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.
+Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries in the dataset.
+
+```{r cs_plot, fig.cap="PGE Scores, Most Recent Available Year \\label{cs_mry}", fig.height=4}
 
@@
 ```
+
+The Scandinavian countries, France, and Spain are at the top of this list, followed by Puerto Rico, which has had women of both of its major parties serve as chief executive and as recently as 2020 had a woman from each party holding the two most prominent elected offices on the island.
+The latest scores for Egypt, Yemen, Pakistan, the Palestinian Territories, and Burkina Faso have them as the places where public opinion is least favorable to gender equality in the public sphere.
 

### 2020-12-23 paper/dcpo_gender_roles.Rmd
add ts plot

@@
 
+```{r ts_plots, fig.cap="PGE Scores Over Time, Selected Countries \\label{ts}", fig.height=3.5}
+countries <- c("Norway", "Australia", "United States", "Mexico", "Taiwan",
+                "Japan", "Turkey", "Nigeria", "Philippines", "Egypt")
+
+theta_results %>%
+  filter(country %in% countries) %>%
+  mutate(country = factor(country, levels = countries)) %>% 
+  ggplot(aes(x = year, y = mean)) +
+  geom_ribbon(aes(ymin = `10%`, ymax = `90%`, linetype=NA), alpha = .25) +
+  geom_line() +
+  theme_bw() +
+  theme(legend.position="none") +
+  coord_cartesian(xlim = c(1985, 2020), ylim = c(0, 1)) +
+  labs(x = NULL, y = "PGE Scores") +
+  facet_wrap(~country, nrow = 2) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        strip.background = element_rect(fill = "white", colour = "white"))
+```
+
+Figure&nbsp;\ref{ts} shows the time series of the PGE scores for ten countries.
+
 # Validating Public Gender Egalitarianism
@@
   annotate("text", x = 2012, y = .60, size = 2,
-           label = "PGE Mean") +
+           label = "PGE") +
   labs(x = "Year", 
@@
   annotate("text", x = 1986, y = .66, size = 2,
-           label = "PGE Mean") +
+           label = "PGE") +
   labs(x = "Year", 

### 2020-12-24 paper/dcpo_gender_roles.Rmd
expand ts_plots; add write up

@@
 
-```{r ts_plots, fig.cap="PGE Scores Over Time, Selected Countries \\label{ts}", fig.height=3.5}
-countries <- c("Norway", "Australia", "United States", "Mexico", "Taiwan",
-                "Japan", "Turkey", "Nigeria", "Philippines", "Egypt")
+```{r ts_plots, fig.cap="PGE Scores Over Time Within Selected Countries \\label{ts}", fig.height=3.6}
+countries <- c("Norway", "Australia", "United States", "Argentina",
+               "Brazil", "Poland", "South Africa", "Japan",
+               "Turkey", "China", "South Korea", "India", 
+               "Nigeria", "Philippines", "Indonesia", "Egypt")
+
+countries2 <- c("Norway", "Australia", "U.S.", "Argentina",
+               "Brazil", "Poland", "South Africa", "Japan",
+               "Turkey", "China", "South Korea", "India", 
+               "Nigeria", "Philippines", "Indonesia", "Egypt")
 
@@
   filter(country %in% countries) %>%
-  mutate(country = factor(country, levels = countries)) %>% 
+  mutate(country = str_replace(country, "United States", "U.S.") %>% 
+           factor(levels = countries2)) %>% 
   ggplot(aes(x = year, y = mean)) +
@@
   theme(legend.position="none") +
-  coord_cartesian(xlim = c(1985, 2020), ylim = c(0, 1)) +
+  coord_cartesian(xlim = c(1980, 2020), ylim = c(0, 1)) +
   labs(x = NULL, y = "PGE Scores") +
   facet_wrap(~country, nrow = 2) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        strip.background = element_rect(fill = "white", colour = "white"))
-```
-
-Figure&nbsp;\ref{ts} shows the time series of the PGE scores for ten countries.
+  theme(axis.text.x  = element_text(size=7,
+                                    angle = 90,
+                                    vjust = .45,
+                                    hjust = .95),
+        strip.background = element_rect(fill = "white", colour = "white")) +
+  plot_annotation(caption = "Note: Countries are ordered by their PGE scores in their most recent\navailable year; gray shading represents 80% credible intervals.")
+```
+
+Figure&nbsp;\ref{ts} displays how PGE scores have changed over time in sixteen countries.
+Like Figure&nbsp;\ref{cs_mry}, it underscores the geographic breadth of the PGE dataset, which allows the study of countries and regions too often neglected in political science research [see @Wilson2020].
+The figure also shows that while public opinion favoring gender equality in the public sphere has risen steadily in some countries, such as Norway and Australia, attitudes have changed little over time in others, like South Korea and the Philippines, or fallen, as in Indonesia.
+They have even advanced and retreated as in Brazil or have declined and recovered as in Nigeria.
+There is much to do to explain the causes and consequences of these trends in public gender egalitarianism.
 
 # Validating Public Gender Egalitarianism
-We consider now the validity of the PGE scores.
+Such future research, however, depends on the validity of the PGE scores.
 Like @Caughey2019 [684-685], we provide evidence of our measure's validity with  convergent validation and construct validation.

### 2020-12-25 paper/dcpo_gender_roles.Rmd
clean up

@@
 -->
-<!-- Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @erickson2002gender; @klein2013gender; @paxton1997women].
+<!-- Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @klein2013gender; @paxton1997women].
 -->
@@
 
-```{r ts_plots, fig.cap="PGE Scores Over Time Within Selected Countries \\label{ts}", fig.height=3.6}
+```{r ts_plots, fig.cap="PGE Scores Over Time Within Selected Countries \\label{ts}", fig.height=3.5}
 countries <- c("Norway", "Australia", "United States", "Argentina",
@@
 Figure&nbsp;\ref{ts} displays how PGE scores have changed over time in sixteen countries.
-Like Figure&nbsp;\ref{cs_mry}, it underscores the geographic breadth of the PGE dataset, which allows the study of countries and regions too often neglected in political science research [see @Wilson2020].
+Like Figure&nbsp;\ref{cs_mry}, it underscores the geographic breadth of the PGE dataset, which allows the study of countries and regions too often neglected in political science research [see @Wilson2021].
 The figure also shows that while public opinion favoring gender equality in the public sphere has risen steadily in some countries, such as Norway and Australia, attitudes have changed little over time in others, like South Korea and the Philippines, or fallen, as in Indonesia.
@@
 
-We move on, then, to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
+We continue, then, to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
 In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.

### 2020-12-27 paper/dcpo_gender_roles.Rmd
draft first paragraph

@@
 
-# Introduction
-
-<!-- Gender egalitarian attitude has been grown over the decades not only in developed countries but also in developing societies [@boehnke2011gender]. -->
-<!-- With the affluent variance in the gender egalitarian attitude around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants.
--->
-<!-- For example, the association between gender egalitarian attitudes and women's political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women's descriptive representation in parliaments [@paxton2003women] have been examined.
--->
-<!-- However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes. -->
-<!-- Very few cross-national time-series measures of gender egalitarianism exist and there is no consensus on the measures. -->
-<!-- Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004.
--->
-
-<!-- To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a].  -->
-<!-- Our new index is based on data from 62 survey datasets from 1972 to 2020, which includes 224,640 observations.  -->
-<!-- The newly developed gender egalitarian index provides opportunities for scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis.
--->
-<!-- The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors.
--->
-<!-- We also can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public opinion on the gender role.
--->
-<!-- Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @klein2013gender; @paxton1997women].
--->
-<!-- Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender].
--->
-
-<!-- This article proceeds with the following order.  -->
-<!-- First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector. -->
-<!-- Next, we illustrate the data source we used to build our index. -->
-<!-- Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced. -->
-<!-- Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.     -->
-<!-- Gender egalitarianism does not have only one dimension but a multi-dimension. -->
-<!-- Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
--->
-<!-- For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not. -->
-<!-- To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework. -->
-<!-- Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting. -->
-<!-- The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions. -->
-<!-- However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.
--->
-
-# Focusing on Public Opinion Toward Gender Equality in the Public Sphere
+Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture or ideology or public opinion---constitute one of the primary explanations for women's exclusion from political power and policy influence [see, e.g., @Yates2017, 103-104; @Paxton2021, 113-114].
+Yet even a half century after @RuleKrauss1974 [, 1719] called in the pages of the _APSR_ for more data to be collected on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
+In the decades since, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
+As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in other offices [see, e.g., @Claveria2014; @Barnes2018].
+Broadly cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained a topic for future research [@Paxton2010, 47].
 
@@
 ```
+
+In this letter, we present the Public Gender Egalitarianism (PGE) database,
 

### 2020-12-28 paper/dcpo_gender_roles.Rmd
drop description of four categories (to add to appendix later); finish intro; clean up

@@
 Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture or ideology or public opinion---constitute one of the primary explanations for women's exclusion from political power and policy influence [see, e.g., @Yates2017, 103-104; @Paxton2021, 113-114].
-Yet even a half century after @RuleKrauss1974 [, 1719] called in the pages of the _APSR_ for more data to be collected on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
+Yet even a half century after @RuleKrauss1974 [, 1719] called in the pages of the _APSR_ for more and better data on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
 In the decades since, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
-As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in other offices [see, e.g., @Claveria2014; @Barnes2018].
+As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].
 Broadly cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained a topic for future research [@Paxton2010, 47].
@@
 
-In this letter, we present the Public Gender Egalitarianism (PGE) database,
-
-We classified the available survey items on gender egalitarian attitudes into four categories.
-The first of these categories consists of questions asking respondents' views of gender equality in the traditionally masculine public sphere of education, paid work, and politics.
-The second category, in turn, encompasses questions focusing on gender equality in the traditionally feminine private sphere of housework and childcare.
-A third category we identified comprises questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not; it is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only rarely included in surveys.^[
-One laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly becoming more common, is the item querying respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
-The fourth and final category includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.
-
-To avoid any potential multidimensionality in the Public Gender Egalitarianism data, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[
-Items that fell into both the first category and another, such as the `tradroles` questions---those with stems of the form "A man's job is to earn money; a woman's job is to look after the home and family"---which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE source data.
-The complete list of gender egalitarianism items is included in the Appendix.]
-Thus, the "Public" in the name of the dataset does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to its attitudes specifically on this _public_ aspect of gender egalitarianism.
-In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.
-We describe these source data in detail in the next section.
+In this letter, we present the Public Gender Egalitarianism (PGE) dataset, which is based on the host of available survey data and recent advances in latent variable modeling of public opinion.
+It provides comparable estimates of the public's attitudes on gender equality in the public sphere of politics, paid work, and education across countries and over time.
+We show that these PGE scores are strongly correlated with responses to single survey items as well as with measures of women's participation in the workforce and in the boardroom.
+We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and effects of collective attitudes toward gender equality in the public sphere.
 
@@
 
+First, we consider the available survey data on attitudes toward equality for women and men in the public sphere.
+In all, we identified `r n_items` such survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.^[
+The complete list of public gender egalitarianism survey items is included in the Appendix.]
 Together, the survey items in the source data were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
-Considering that observations for every year in each country surveyed would number `r total_cy`, a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations.
+Observations for every year in each country surveyed would number `r total_cy`, and a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations.
 Viewed from this perspective of complete data, the available data can be seen to be very, very sparse.
 From a more optimistic standpoint, we note there there are `r n_cy` country-years in which we have at least _some_ information about the public gender egalitarianism of the population, that is, some `r {back_to_numeric(n_cy)/back_to_numeric(spanned_cy) * 100} %>% round()`% of the `r spanned_cy` country-years spanned by the data we collected.
-But there can be no gainsaying that the many different survey items employed renders these data difficult to use together.
+But there can be no gainsaying Claveria's [-@Claveria2014] observation that the many different survey items employed renders these data difficult to use together.
 
@@
 The @McGann2019 model depends on dense survey data unlike the sparse data on public gender egalitarianism described in the preceding section.
-@Kolczynska2020 is the very most recent of the five works and builds on each of the others, but the MRP approach developed in that piece is suitable only when the available survey data are dense and ancillary data on population characteristics are also available, so it is similarly inappropriate to this application.
+@Kolczynska2020 is the very most recent of the five works and builds on each of the others, but the MRP approach developed in that piece is suitable not only when the available survey data are dense but also when ancillary data on population characteristics are available, so it is similarly inappropriate to this application.
 ]
@@
 We continue, then, to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
-In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
+In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from a related category of gender egalitarianism, namely questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
 Assuming that attitudes that women should prioritize housework and childcare over education, politics, and paid employment---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE score.
 Exemplars of such items across all available country-years ("a job is alright but what most women really want is a home and children" from the WVS and EVS), in cross-section ("the most important role of a woman is to take care of her home and family" from the Eurobarometer 87.4), and in time series ("a pre-school child is likely to suffer if his or her mother works" from the German ALLBUS, WVS, and EVS) all show strong correlations with the PGE scores.
-<!-- Consider `wantch4`, an item depicted in the left pane asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children." -->
-<!-- As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
--->
-<!-- Or, similarly, `familywoman4`, an item plotted in the center pane from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family."  -->
-<!-- Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[
-One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
--->
-<!-- (Indeed, the `tradroles` series of questions, which couple the `familywoman4` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.) -->
-<!-- If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
--->
-<!-- In either case, though, they provide evidence of the validity of the PGE scores.] -->
-<!-- In a slightly different vein, `preschoolwork4`, included in the German ALLBUS, the World Values Survey, and the European Values Survey, asked respondents the extent to which they agreed that "a pre-school child is likely to suffer if his or her mother works;" we plot the time series of the proportion of the population of Germany estimated to disagree or disagree strongly with this statement in the right pane.
--->
-<!-- The belief that mothers working cause harm to their children should be expected to lead to disfavoring gender equality in workforce to avoid this purported negative consequence.  -->
-<!-- With regard to all of these items, too, the correlations with the PGE scores are strong. -->
 
@@
 # Using the Public Gender Egalitarianism Dataset
-Version 1.0 of the PGE dataset includes PGE scores for `r pge[[1]] %>% distinct(country) %>% nrow()` countries for as many years as possible from 1972 to the present, a total of `r pge[[1]] %>% nrow()` country-years.
+Version 1.0 of the PGE dataset includes PGE scores for `r pge[[1]] %>% distinct(country) %>% nrow()` countries for as many years as possible from 1972 to the present, a total of `r pge[[1]] %>% nrow() %>% scales::comma()` country-years.
 It can be accessed in two ways: via a user-friendly web application on the PGE website, which plots scores for as many as four countries for easy comparison of levels and trends, and via the Harvard Dataverse, where the entire dataset is available for download for use in statistical analysis.
@@
 
+The PGE dataset will allow researchers to not only better address such long-standing questions as how collective attitudes on gender roles have influenced the election of women to national legislatures and vice versa [see, e.g., @Paxton2003; @Alexander2012] but also pursue new and more nuanced lines of inquiry on issues of policy responsiveness and policy feedback [cf., @Kittilson2008; @Busemeyer2021].
+
 \pagebreak

### 2020-12-28 paper/dcpo_gender_roles.Rmd
clean up

@@
 To estimate public gender egalitarianism across countries and over time, we draw on the latest of these methods that is appropriate for data that is not only incomparable but also sparse, the Dynamic Comparative Public Opinion  (DCPO) model presented in @Solt2020c.^[
-@Solt2020 demonstrates that the DCPO model provides a better fit to survey data than the models put forward by @Claassen2019 or @Caughey2019.
+@Solt2020a demonstrates that the DCPO model provides a better fit to survey data than the models put forward by @Claassen2019 or @Caughey2019.
 The @McGann2019 model depends on dense survey data unlike the sparse data on public gender egalitarianism described in the preceding section.
@@
 # Validating Public Gender Egalitarianism
-Such future research, however, depends on the validity of the PGE scores.
-Like @Caughey2019 [684-685], we provide evidence of our measure's validity with  convergent validation and construct validation.
 
@@
 
+Such future research, however, depends on the validity of the PGE scores.
+Like @Caughey2019 [684-685], we provide evidence of our measure's validity with  convergent validation and construct validation.
 Figure&nbsp;\ref{conv_plot} displays our demonstrations of convergent validation.
@@
 In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from a related category of gender egalitarianism, namely questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
-Assuming that attitudes that women should prioritize housework and childcare over education, politics, and paid employment---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE score.
+Assuming that attitudes that women should prioritize housework and childcare over education, paid employment, and politics---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE score.
 Exemplars of such items across all available country-years ("a job is alright but what most women really want is a home and children" from the WVS and EVS), in cross-section ("the most important role of a woman is to take care of her home and family" from the Eurobarometer 87.4), and in time series ("a pre-school child is likely to suffer if his or her mother works" from the German ALLBUS, WVS, and EVS) all show strong correlations with the PGE scores.

### 2020-12-28 paper/dcpo_gender_roles.Rmd
add Tai2021

@@
 One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the uncertainty in the estimates.
-But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
+But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2021] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
 Therefore, taking the uncertainty in the PGE scores into account is crucial to reaching well-grounded conclusions.

### 2020-12-28 paper/dcpo_gender_roles.Rmd
finish focusing section

@@
 
+countries_cp <- dcpo_input_raw_public1 %>%
+  mutate(country = if_else(stringr::str_detect(country, "United"),
+                           stringr::str_replace(country, "((.).*) ((.).*)", "\\2.\\4."),
+                           country),
+         country = stringr::str_replace(country, "South", "S.")) %>% 
+  distinct(country, year, item) %>%
+  count(country) %>% 
+  arrange(desc(n)) %>% 
+  head(12) %>% 
+  pull(country)
+
+countries_cbyp <- dcpo_input_raw_public1 %>%
+  mutate(country = if_else(stringr::str_detect(country, "United"),
+                           stringr::str_replace(country, "((.).*) ((.).*)", "\\2.\\4."),
+                           country),
+         country = stringr::str_replace(country, "South", "S.")) %>% 
+  distinct(country, year) %>%
+  count(country) %>% 
+  arrange(desc(n)) %>% 
+  head(12) %>% 
+  pull(country)
+
+adding <- setdiff(countries_cbyp, countries_cp) %>% 
+  paste(collapse = ", ") %>% 
+  str_replace(", (\\w*)$", ", and \\1")
+
+dropping <- setdiff(countries_cp, countries_cbyp) %>% 
+  paste(collapse = ", ") %>% 
+  str_replace(", (\\w*)$", ", and \\1")
+
+y_peak_year <- dcpo_input_raw_public1 %>%
+  distinct(country, year) %>%
+  count(year, name = "nn") %>% 
+  filter(nn == max(nn)) %>% 
+  pull(year)
+
+y_peak_nn <- dcpo_input_raw_public1 %>%
+  distinct(country, year) %>%
+  count(year, name = "nn") %>% 
+  filter(nn == max(nn)) %>% 
+  pull(nn)
+
 data_poorest <- dcpo_input_raw_public1 %>%
@@
 
-The left panel of Figure&nbsp;\ref{item_country_plots} displays in how many country-years each of the twelve most-commonly asked survey items are available.
+The upper left panel of Figure&nbsp;\ref{item_country_plots} displays in how many country-years each of the twelve most-commonly asked survey items are available.
 The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
@@
 Which countries are the most data-rich?
-The right panel of Figure&nbsp;\ref{item_country_plots} shows the dozen countries with the highest count of country-year-item observations.
+The upper right panel of Figure&nbsp;\ref{item_country_plots} shows the dozen countries with the highest count of country-year-item observations.
 The United States, with `r us_obs` observations, is far and away the best represented country in the source data, followed by `r others`.
 At the other end of the spectrum, `r n_data_poorest` countries---`r data_poorest`---have only the minimum two observations required to be included in the source dataset at all.
+The lower left panel shows the twelve countries with the most years observed; this group is similar, but with `r adding` joining the list and `r dropping` dropping off.
+
+The lower right panel of Figure&nbsp;\ref{item_country_plots} counts the countries observed in each year and reveals just how few relevant survey items asked before 1990.
+Country coverage reached its peak in `r y_peak_year`, when surveys in `r y_peak_nn` countries included items on gender egalitarianism in the public sphere.
+In the next section, we describe how we are able to make use of all of this sparse and incomparable survey data to generate the PGE scores using a latent variable model.
 

### 2020-12-28 paper/dcpo_gender_roles.Rmd
add abstract

@@
 
-abstract: ""
+abstract: "Societal attitudes toward gender roles in education, the workplace, and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories.
+Drawing on recent advances in latent variable modeling of public opinion and a comprehensive collection of survey data, we present the Public Gender Egalitarianism dataset to address this need: comparable estimates of the public's attitudes on gender equality in the public sphere across more than one hundred countries over time.
+These PGE scores are strongly correlated with responses to single survey items as well as with measures of women's rates of participation in the labor force and on corporate boards.
+We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in the public sphere."
 keywords: "gender inequality, public opinion, measurement"
@@
 As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].
-Broadly cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained a topic for future research [@Paxton2010, 47].
+Cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained a topic for future research [@Paxton2010, 47].
 

### 2020-12-29 paper/dcpo_gender_roles.Rmd
add authors

@@
 author:
-
+- name: Byung-Deuk Woo
+  affiliation: University of Iowa
+- name: Lindsey Allemang
+  affiliation: University of Iowa
+- name: Frederick Solt
+  affiliation: University of Iowa
 abstract: "Societal attitudes toward gender roles in education, the workplace, and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories.
@@
 spacing: double
-bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "s.bib$", recursive = TRUE))`}
+bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
 # csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl

### 2020-12-29 paper/dcpo_gender_roles.Rmd
get abstract under 150 words; fuss a bit with intro; take stab at rounding off conclusion

@@
 Drawing on recent advances in latent variable modeling of public opinion and a comprehensive collection of survey data, we present the Public Gender Egalitarianism dataset to address this need: comparable estimates of the public's attitudes on gender equality in the public sphere across more than one hundred countries over time.
-These PGE scores are strongly correlated with responses to single survey items as well as with measures of women's rates of participation in the labor force and on corporate boards.
-We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in the public sphere."
-keywords: "gender inequality, public opinion, measurement"
+These PGE scores are strongly correlated with responses to individual survey items and with rates of participation in the labor force and corporate boards.
+We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in the public sphere.
+[148/150 words]"
+keywords: "gender roles, gender inequality, public opinion, political culture, measurement"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].
-Cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained a topic for future research [@Paxton2010, 47].
+Cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained persistently a topic for future research [@Paxton2010, 47].
 
@@
 It can be accessed in two ways: via a user-friendly web application on the PGE website, which plots scores for as many as four countries for easy comparison of levels and trends, and via the Harvard Dataverse, where the entire dataset is available for download for use in statistical analysis.
-We will revise and update the dataset as new survey data on public gender egalitarianism becomes available.
 
@@
 
-The PGE dataset will allow researchers to not only better address such long-standing questions as how collective attitudes on gender roles have influenced the election of women to national legislatures and vice versa [see, e.g., @Paxton2003; @Alexander2012] but also pursue new and more nuanced lines of inquiry on issues of policy responsiveness and policy feedback [cf., @Kittilson2008; @Busemeyer2021].
+The PGE dataset will allow researchers to not only better address such long-standing questions as how collective attitudes on gender roles have influenced the election of women to national legislatures and vice versa [see, e.g., @Paxton2003; @Alexander2012] but also, for example, to pursue both new and more nuanced lines of inquiry on issues of policy responsiveness and policy feedback [cf., @Kittilson2008; @Busemeyer2021].
+We will revise and update the dataset as new survey data on public gender egalitarianism becomes available, and we look forward to a rapid growth in research that advances our understanding of the relationships between collective attitudes on gender roles and a wide range of other political phenomena.
 

### 2021-01-01 paper/dcpo_gender_roles.Rmd
fix cite

@@
 To estimate public gender egalitarianism across countries and over time, we draw on the latest of these methods that is appropriate for data that is not only incomparable but also sparse, the Dynamic Comparative Public Opinion  (DCPO) model presented in @Solt2020c.^[
-@Solt2020a demonstrates that the DCPO model provides a better fit to survey data than the models put forward by @Claassen2019 or @Caughey2019.
+@Solt2020c demonstrates that the DCPO model provides a better fit to survey data than the models put forward by @Claassen2019 or @Caughey2019.
 The @McGann2019 model depends on dense survey data unlike the sparse data on public gender egalitarianism described in the preceding section.
@@
 But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2021] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
-Therefore, taking the uncertainty in the PGE scores into account is crucial to reaching well-grounded conclusions.
-
-The download includes pre-formatted data to facilitate incorporating the uncertainty in the PGE scores.
-In R, the functions of the \texttt{purrr} package [@Henry2019, also included in the widely-used \texttt{tidyverse} package [@Wickham2017a]] make it entirely straightforward to incorporate the uncertainty of the PGE estimates.
-In Stata, the \texttt{mi estimate:} command prefix originally developed for analyzing multiply imputed data can be used to automate the process of building uncertainty into nearly any analysis.
-Step-by-step instructions on how to use these tools, complete with examples, are included in the data download.
+Therefore, taking the uncertainty in the PGE scores into account (e.g., via the \texttt{purrr} package [@Henry2019] in R or the \texttt{mi estimate:} command prefix in Stata) is crucial to reaching well-grounded conclusions.
 

### 2021-01-05 paper/dcpo_gender_roles.Rmd
drop line 344, per @byngdeuk's comment here: https://github.com/fsolt/dcpo_gender_roles/issues/18#issuecomment-754095097
shrink dots and darken whiskers to try to make whiskers easier to see, per @lallemang's comment here: https://github.com/fsolt/dcpo_gender_roles/issues/18#issuecomment-754288959

@@
 
-Which countries are the most data-rich?
 The upper right panel of Figure&nbsp;\ref{item_country_plots} shows the dozen countries with the highest count of country-year-item observations.
@@
                na.rm = TRUE,
-               alpha = .2) +
-  geom_point(fill = "black", shape = 21, size = .5, na.rm = TRUE) +
+               alpha = .4) +
+  geom_point(fill = "black", shape = 21, size = .4, na.rm = TRUE) +
   theme_bw() + theme(legend.position="none",

### 2021-01-05 paper/dcpo_gender_roles.Rmd
foreshadow that DCPO is solution to sparse and incomparable data per @lallemang's comment here: https://github.com/fsolt/dcpo_gender_roles/issues/18#issuecomment-754288959

@@
 
-In this letter, we present the Public Gender Egalitarianism (PGE) dataset, which is based on the host of available survey data and recent advances in latent variable modeling of public opinion.
+In this letter, we present the Public Gender Egalitarianism (PGE) dataset, which is based on the host of survey data available and recent advances in latent variable modeling of public opinion that allow us to make use of this sparse and incomparable data.
 It provides comparable estimates of the public's attitudes on gender equality in the public sphere of politics, paid work, and education across countries and over time.
@@
 
-First, we consider the available survey data on attitudes toward equality for women and men in the public sphere.
+National and cross-national surveys have often included questions tapping attitudes toward equality for women and men in the public sphere over the past half-century, but the resulting data are both sparse, that is, unavailable for many countries and years, and incomparable, generated by many different survey items.
 In all, we identified `r n_items` such survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.^[
@@
 Observations for every year in each country surveyed would number `r total_cy`, and a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations.
-Viewed from this perspective of complete data, the available data can be seen to be very, very sparse.
+Viewed from this complete-data perspective, the available data can be seen to be very, very sparse.
 From a more optimistic standpoint, we note there there are `r n_cy` country-years in which we have at least _some_ information about the public gender egalitarianism of the population, that is, some `r {back_to_numeric(n_cy)/back_to_numeric(spanned_cy) * 100} %>% round()`% of the `r spanned_cy` country-years spanned by the data we collected.
-But there can be no gainsaying Claveria's [-@Claveria2014] observation that the many different survey items employed renders these data difficult to use together.
+But there can be no denying Claveria's [-@Claveria2014] observation that the many different survey items employed renders these data incomparable and difficult to use together.
 

### 2021-01-05 paper/dcpo_gender_roles.Rmd
revise description of using uncertainty per this @lallemang comment https://github.com/fsolt/dcpo_gender_roles/issues/18#issuecomment-754288959; clean up bibtex per this @byngdeuk comment https://github.com/fsolt/dcpo_gender_roles/issues/18#issuecomment-754095097

@@
 
-One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the uncertainty in the estimates.
-But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2021] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
-Therefore, taking the uncertainty in the PGE scores into account (e.g., via the \texttt{purrr} package [@Henry2019] in R or the \texttt{mi estimate:} command prefix in Stata) is crucial to reaching well-grounded conclusions.
+One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the quantified uncertainty in the estimates.
+But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2021] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
+Therefore, taking the uncertainty in the PGE scores into account is crucial to reaching well-grounded conclusions.
+Step-by-step instructions for doing this via simulations, with examples, are included in the data download.
 

### 2021-01-05 paper/dcpo_gender_roles.Rmd
edit to avoid our item labels, just to be sure to stay on right side of https://www.apsanet.org/APSR-Submission-Guidelines

@@
   affiliation: University of Iowa
+anonymous: false
 abstract: "Societal attitudes toward gender roles in education, the workplace, and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories.
@@
 
-```{r item_and_country_plots, fig.height = 3.5, fig.cap = "Items, Countries, and Years with the Most Observations in the PGE Source Data \\label{item_country_plots}"}
+```{r item_and_country_plots, fig.height = 3.5, fig.cap = "Countries and Years with the Most Observations in the PGE Source Data \\label{item_country_plots}"}
 items_plot <- dcpo_input_raw_public1 %>%
@@
   theme(axis.title.x = element_blank(),
-        axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
+        # axis.text.x  = element_text(angle = 90, vjust = .45, hjust = .95),
         axis.title.y = element_text(size = 9),
@@
 
-(items_plot + countries_plot) / (cby_plot + ybc_plot)
-```
-
-The upper left panel of Figure&nbsp;\ref{item_country_plots} displays in how many country-years each of the twelve most-commonly asked survey items are available.
-The `polileader4` item, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do," was the most frequently asked question in the data we collected.
+(countries_plot + cby_plot) / (ybc_plot)
+```
+
+Consider the most frequently asked item in the data we collected, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do."
 Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
-That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, `polileader4` is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
-
-The upper right panel of Figure&nbsp;\ref{item_country_plots} shows the dozen countries with the highest count of country-year-item observations.
+That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
+
+The upper left panel of Figure&nbsp;\ref{item_country_plots} shows the dozen countries with the highest count of country-year-item observations.
 The United States, with `r us_obs` observations, is far and away the best represented country in the source data, followed by `r others`.
 At the other end of the spectrum, `r n_data_poorest` countries---`r data_poorest`---have only the minimum two observations required to be included in the source dataset at all.
-The lower left panel shows the twelve countries with the most years observed; this group is similar, but with `r adding` joining the list and `r dropping` dropping off.
-
-The lower right panel of Figure&nbsp;\ref{item_country_plots} counts the countries observed in each year and reveals just how few relevant survey items asked before 1990.
+The upper left panel shows the twelve countries with the most years observed; this group is similar, but with `r adding` joining the list and `r dropping` dropping off.
+The bottom panel counts the countries observed in each year and reveals just how few relevant survey items were asked before 1990.
 Country coverage reached its peak in `r y_peak_year`, when surveys in `r y_peak_nn` countries included items on gender egalitarianism in the public sphere.
@@
 
-```{r cs_plot, fig.cap="PGE Scores, Most Recent Available Year \\label{cs_mry}", fig.height=4}
+```{r cs_plot, fig.cap="PGE Scores, Most Recent Available Year \\label{cs_mry}", fig.height=4.5}
 
@@
                alpha = .2) +
-  annotate("text", x = 1979, y = .72, size = 2,
-           label = 'emopoli2,\nU.S. GSS') +
+  annotate("text", x = 1979, y = .7, size = 2,
+           label = 'U.S. GSS') +
   annotate("text", x = 2012, y = .60, size = 2,
@@
 Here, we compare PGE scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
-In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years.
+In the left panel, we examine the four-point question on political leaders mentioned above, the most common item in the source data across all country-years.
 <!-- In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women." -->
-Then, in the center panel, we look at the question that provides most data-rich cross-section, the `poliequal3` item in Pew Global's Spring 2007 survey.
+Then, in the center panel, we look at the question that provides most data-rich cross-section, which asked whether respondents felt "men generally make better political leaders than women," included in Pew Global's Spring 2007 survey.
 <!-- Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders." -->
-Finally, in the right panel, to evaluate how well the PGE score captures change over time, we focus on the item with the largest number of observations for a single country, the `emopoli2` survey item, which asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women."
+Finally, in the right panel, to evaluate how well the PGE score captures change over time, we focus on the item with the largest number of observations for a single country, which asked respondents to the U.S.
+General Social Survey whether they agreed or disagreed that "most men are better suited emotionally for politics than are most women."
 <!-- Finally, in the right panel, to evaluate how well the PGE score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country.
@@
 In every case, the correlations---estimated taking into account the uncertainty in the measures^[
-The uncertainty in the PGE score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the `polileader4` question, but failing to account for this uncertainty would overstate the correlation with the Pew `poliequal3` item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S.
-GSS `emopoli2` item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`.
+The uncertainty in the PGE score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the political leadership question, but failing to account for this uncertainty would overstate the correlation with the Pew item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S.
+GSS item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`.
 We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.]---are in the expected direction and very strong.
@@
   annotate("text", x = 2010, y = .30, size = 2,
-           label = 'preschoolwork4,\nALLBUS, EVS, WVS') +
+           label = 'ALLBUS, EVS, WVS') +
   annotate("text", x = 1986, y = .66, size = 2,

### 2021-01-07 paper/dcpo_gender_roles.Rmd
make cs_mry plot bigger

@@
 
-We used the `DCPO` package for R [@Solt2020a] to estimate this model on the public gender egalitarianism source data described above.
-The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.
-Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries in the dataset.
-
-```{r cs_plot, fig.cap="PGE Scores, Most Recent Available Year \\label{cs_mry}", fig.height=4.5}
-
-n_panes <- 3
+```{r cs_plot, fig.cap="PGE Scores, Most Recent Available Year \\label{cs_mry}", fig.height=10, fig.width=8}
+
+n_panes <- 2
+axis_text_size <- 10
 
@@
                alpha = .4) +
-  geom_point(fill = "black", shape = 21, size = .4, na.rm = TRUE) +
+  geom_point(fill = "black", shape = 21, size = .5, na.rm = TRUE) +
   theme_bw() + theme(legend.position="none",
-                     axis.text.x  = element_text(size=7,
+                     axis.text.x  = element_text(size = axis_text_size,
                                                  angle = 90,
@@
                                                  hjust = .95),
-                     axis.text.y  = element_text(size=7),
+                     axis.text.y  = element_text(size = axis_text_size),
                      axis.title = element_blank(),
@@
 ```
+
+We used the `DCPO` package for R [@Solt2020a] to estimate this model on the public gender egalitarianism source data described above.
+The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.
+Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries in the dataset.
 

### 2021-01-08 paper/dcpo_gender_roles.Rmd
update

@@
 ```{r dcpo_results}
-load(here::here("data", "polileader4_2_4k_11-27.rda"))
+load(here::here("data", "polileader4_2_4k_01-08.rda"))
 
@@
 
-The Scandinavian countries, France, and Spain are at the top of this list, followed by Puerto Rico, which has had women of both of its major parties serve as chief executive and as recently as 2020 had a woman from each party holding the two most prominent elected offices on the island.
+The Scandinavian countries and France are at the top of this list, along with Puerto Rico, which has had women of both of its major parties serve as chief executive and as recently as 2020 had a woman from each party holding the two most prominent elected offices on the island.
 The latest scores for Egypt, Yemen, Pakistan, the Palestinian Territories, and Burkina Faso have them as the places where public opinion is least favorable to gender equality in the public sphere.

### 2021-01-09 paper/pge_appendix.Rmd
initial commit

---
title: 'Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative
  Public Opinion Toward Egalitarian Gender Roles in the Public Sphere'
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    pdf_document:
        toc: true
header-includes:
      - \usepackage{float}
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{booktabs}
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE)

# If `DCPOtools` is not yet installed:
# remotes::install_github("fsolt/DCPOtools")

library(DCPOtools)
library(DCPO)
library(tidyverse)
library(glue)
library(countrycode)
library(patchwork)
library(modelsummary)

set.seed(324)
```

# Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism

```{r pge_items}
load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_output.rda"))

dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
                                  col_types = "cdcddcd")

process_dcpo_input_raw <- function(dcpo_input_raw_df) {
  dcpo_input_raw_df %>% 
  DCPOtools::with_min_yrs(2) %>% 
  DCPOtools::with_min_cy(5) %>% 
  group_by(country) %>% 
  mutate(cc_rank = n()) %>% 
  ungroup() %>% 
  arrange(-cc_rank)
}

dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public)

pge_items <- read_csv(here::here("data-raw", "egr_questions.csv"),
                      col_types = "cccccc")

alpha_results <- DCPO::summarize_dcpo_results(dcpo_input,
                                              dcpo_output,
                                              "alpha") %>% 
    transmute(item = question,
              dispersion = mean)

beta_results <- DCPO::summarize_dcpo_results(dcpo_input,
                                              dcpo_output,
                                              "beta") %>% 
    group_by(question) %>% 
    summarize(difficulties0 = paste0(round(mean, 2), collapse = ", ")) %>% 
    mutate(item = question,
           cp = as.numeric(str_extract(item, "\\d")) - 1,
           term = str_glue("(( ?-?[0-9].[0-9][0-9]?,?){{{cp}}})"),
           difficulties = str_extract(difficulties0, 
                                      term) %>%
               str_replace(",$", "") %>% 
               str_trim()) %>% 
    transmute(item, difficulties)

items_summary <- dcpo_input_raw_public1 %>%
    dplyr::select(country, year, item, survey) %>%
    distinct() %>%
    separate(survey, c("surv1", "surv2", "surv3"), sep=", ", fill = "left") %>%
    pivot_longer(cols = starts_with("surv"), values_to = "survey") %>%
    filter(!is.na(survey)) %>% 
    group_by(item, survey) %>% 
    summarize(n_cy = n()) %>% 
    arrange(item, -n_cy) %>% 
    group_by(item) %>% 
    mutate(total_cy = sum(n_cy),
           all_surveys = paste0(survey, collapse = ", ")) %>% 
    slice(1) %>% 
    ungroup() %>% 
    left_join(pge_items %>% select(item, survey, question_text),
              by = c("item", "survey")) %>% 
    left_join(alpha_results, by = "item") %>% 
    left_join(beta_results, by = "item") %>% 
    arrange(-total_cy) %>% 
    select(-survey, -n_cy)
```

```{r pge_items_table1}    
items_summary[1:9,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

```{r pge_items_table2}    
items_summary[10:17,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

```{r pge_items_table3}    
items_summary[18:27,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

```{r pge_items_table4}    
items_summary[28:34,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

```{r pge_items_table5}    
items_summary[35:46,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
             ` Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

```{r pge_items_table6}    
items_summary[47:49,] %>% 
    transmute(`Survey\nItem\nCode` = item,
              `Country\nYears` = as.character(total_cy),
              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
              `Dispersion` = dispersion,
              `Difficulties`= difficulties,
              `Survey Dataset Codes` = all_surveys) %>% 
    modelsummary::datasummary_df(output = "kableExtra",
                                 note = "") %>% 
    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
    kableExtra::column_spec(5, width = "5em")
```

\vspace{-.45in}
Notes: Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found in the cross-national survey dataset.  Lower values of dispersion ($\alpha$) indicate questions that better identify publics with more public gender egalitarianism from those with less.  Items have one difficulty score ($\beta$) for each cutpoint; that is, one less than the number of response categories.  Survey dataset codes correspond to those used in the `DCPOtools` package.

### 2021-01-09 paper/pge_appendix.Rmd
refactor pge_items_table; add Appendix B re the other, excluded categories

@@
 # Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism 
-
 ```{r pge_items}
@@
 ```{r pge_items_table1}  
-items_summary[1:9,] %>% 
+pge_items_table <- function(x) {
+    items_summary %>% 
+        slice(x) %>% 
         transmute(`Survey\nItem\nCode` = item,
-              `Country\nYears` = as.character(total_cy),
-              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
-              `Dispersion` = dispersion,
-             ` Difficulties`= difficulties,
-              `Survey Dataset Codes` = all_surveys) %>% 
-    modelsummary::datasummary_df(output = "kableExtra") %>% 
-    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
-    kableExtra::column_spec(5, width = "5em")
-```
-
-```{r pge_items_table2}    
-items_summary[10:17,] %>% 
-    transmute(`Survey\nItem\nCode` = item,
-              `Country\nYears` = as.character(total_cy),
-              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
-              `Dispersion` = dispersion,
-             ` Difficulties`= difficulties,
-              `Survey Dataset Codes` = all_surveys) %>% 
-    modelsummary::datasummary_df(output = "kableExtra") %>% 
-    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
-    kableExtra::column_spec(5, width = "5em")
-```
-
-```{r pge_items_table3}    
-items_summary[18:27,] %>% 
-    transmute(`Survey\nItem\nCode` = item,
-              `Country\nYears` = as.character(total_cy),
-              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
-              `Dispersion` = dispersion,
-             ` Difficulties`= difficulties,
-              `Survey Dataset Codes` = all_surveys) %>% 
-    modelsummary::datasummary_df(output = "kableExtra") %>% 
-    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
-    kableExtra::column_spec(5, width = "5em")
-```
-
-```{r pge_items_table4}    
-items_summary[28:34,] %>% 
-    transmute(`Survey\nItem\nCode` = item,
-              `Country\nYears` = as.character(total_cy),
-              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
-              `Dispersion` = dispersion,
-             ` Difficulties`= difficulties,
-              `Survey Dataset Codes` = all_surveys) %>% 
-    modelsummary::datasummary_df(output = "kableExtra") %>% 
-    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
-    kableExtra::column_spec(5, width = "5em")
-```
-
-```{r pge_items_table5}    
-items_summary[35:46,] %>% 
-    transmute(`Survey\nItem\nCode` = item,
-              `Country\nYears` = as.character(total_cy),
-              `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
-              `Dispersion` = dispersion,
-             ` Difficulties`= difficulties,
-              `Survey Dataset Codes` = all_surveys) %>% 
-    modelsummary::datasummary_df(output = "kableExtra") %>% 
-    kableExtra::column_spec(c(3, 6), width = "10em") %>% 
-    kableExtra::column_spec(5, width = "5em")
-```
-
-```{r pge_items_table6}    
-items_summary[47:49,] %>% 
-    transmute(`Survey\nItem\nCode` = item,
-              `Country\nYears` = as.character(total_cy),
+                  `Country-Years` = as.character(total_cy),
                   `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
@@
         kableExtra::column_spec(5, width = "5em")
+}
+
+pge_items_table(1:9)
+```
+
+```{r pge_items_table2}    
+pge_items_table(10:17)
+```
+
+```{r pge_items_table3}    
+pge_items_table(18:27)
+```
+
+```{r pge_items_table4}    
+pge_items_table(28:34)
+```
+
+```{r pge_items_table5}    
+pge_items_table(35:46)
+```
+
+```{r pge_items_table6}    
+pge_items_table(47:49)
 ```
@@
 Items have one difficulty score ($\beta$) for each cutpoint; that is, one less than the number of response categories.
-Survey dataset codes correspond to those used in the `DCPOtools` package.
+Survey dataset codes correspond to those used in the `DCPOtools` R package; they appear in decreasing order of country-years contributed.
+
+# Appendix B: Excluded Survey Items
+To estimate the Public Gender Egalitarianism scores, we collected survey data on questions asking respondents' views of gender equality in the traditionally masculine public sphere of education, paid work, and politics.
+These included questions are nearly always explicit in comparing men and women (but see, for example, `unequalpol4`, which asked responses to the statement "Women do not have the necessary qualities and skills to fill positions of responsibility in politics") and nearly always explicitly invoke education, paid work, or politics, though they may also be broader (see, for example, `equalright2`, which asked "On a different subject, do you think women should have equal rights with men, or shouldn’t they?").
+
+We carefully distinguished these questions from three other categories of questions on gender equality.
+First, the PGE source data do not include the small set of questions focusing on gender equality in the traditionally feminine private sphere of housework and childcare, such as "Men should take as much responsibility as women for the home and children," asked (with differing response categories) in the European Values Survey and the European Social Survey.
+Second, as noted in the text, we also excluded questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not, asked in the World Values Survey and many others.
+Given that attitudes that women should prioritize housework and childcare over education, paid employment, and politics---or convictions that there will be negative consequences if they do not---can be expected to lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, this is clearly a very closely related set of items to those we sought, and there are many of them.^[
+It is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only rarely included in surveys; one laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly becoming more common, is the item querying respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
+The third and final category of excluded survey items includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.
+In each case, as the included questions are not _directly_ relevant to gender egalitarianism in the public sphere, we concluded that to ensure that the PGE scores tap only a single dimension of attitudes, we would exclude these others.
+Usefully, this decision also allows, when the available survey data permits, future research to take up the estimation of dynamic comparative public opinion of those concepts separately and their relationships to public gender egalitarianism.

### 2021-05-27 paper/pge_appendix.Rmd
update

@@
 Usefully, this decision also allows, when the available survey data permits, future research to take up the estimation of dynamic comparative public opinion of those concepts separately and their relationships to public gender egalitarianism.
+
+# Appendix C: 
+```{r create_pwe_indices}
+dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
+                                  col_types = "cdcddcd")
+public_items <- read_csv(here::here("data-raw", "public_items.csv"),
+                         col_types = "ccddd")
+
+process_dcpo_input_raw <- function(dcpo_input_raw_df) {
+  dcpo_input_raw_df %>% 
+  with_min_yrs(2) %>% 
+  with_min_cy(5) %>% 
+  group_by(country) %>% 
+  mutate(cc_rank = n()) %>% 
+  ungroup() %>% 
+  arrange(-cc_rank)
+}
+
+dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public) %>% 
+  left_join(public_items, by = "item")
+dcpo_input_raw_political1 <- dcpo_input_raw_public1 %>% 
+  filter(political==1)
+dcpo_input_raw_workplace1 <- dcpo_input_raw_public1 %>% 
+  filter(workplace==1)
+dcpo_input_raw_education1 <- dcpo_input_raw_public1 %>% 
+  filter(education==1)
+
+dcpo_input_public_political <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
+                                            scale_q = "polileader4",
+                                            scale_cp = 2)
+save(dcpo_input_political, file = here::here("data", "dcpo_input_political.rda"))
+
+dcpo_input_workplace <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
+                                            scale_q = "job3a",
+                                            scale_cp = 2)
+save(dcpo_input_workplace, file = here::here("data", "dcpo_input_workplace.rda"))
+
+dcpo_input_education <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
+                                            scale_q = "education4",
+                                            scale_cp = 2)
+save(dcpo_input_education, file = here::here("data", "dcpo_input_education.rda"))
+```
+
+```{r dcpo_political, eval=FALSE}
+iter <- 4000
+
+dcpo_output_political <- dcpo(dcpo_input_political,
+                              iter = iter,
+                              chains = 4,
+                              thin = iter/500, # this yields 250 draws per chain, 1000 draws total
+                              pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+```
+
+```{r dcpo_workplace, eval=FALSE}
+iter <- 5000
+
+dcpo_output_workplace <- dcpo(dcpo_input_workplace,
+                              iter = iter,
+                              chains = 4,
+                              thin = iter/500, # this yields 250 draws per chain, 1000 draws total
+                              pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+```
+
+```{r dcpo_education, eval=FALSE}
+iter <- 5000
+
+dcpo_output_education <- dcpo(dcpo_input_education,
+                              iter = iter,
+                              chains = 4,
+                              thin = iter/500, # this yields 250 draws per chain, 1000 draws total
+                              pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
+```
+
+```{r political}
+load(here::here("data", "political_polileader4_2_4k.rda"))
+
+dcpo_input_political <- dcpo_input
+
+dcpo_output_political <- dcpo_output
+
+save(dcpo_input_political, file = here::here("data", "dcpo_input_political.rda"))
+
+save(dcpo_output_political, file = here::here("data", "dcpo_output_political.rda"))
+```
+
+```{r workplace}
+load(here::here("data", "workplace_job3a_2_5k.rda"))
+
+dcpo_input_workplace <- dcpo_input
+
+dcpo_output_workplace <- dcpo_output
+
+save(dcpo_input_workplace, file = here::here("data", "dcpo_input_workplace.rda"))
+
+save(dcpo_output_workplace, file = here::here("data", "dcpo_output_workplace.rda"))
+```
+
+```{r education}
+load(here::here("data", "education_education4_2_5k.rda"))
+
+dcpo_input_education <- dcpo_input
+
+dcpo_output_education <- dcpo_output
+
+save(dcpo_input_education, file = here::here("data", "dcpo_input_education.rda"))
+
+save(dcpo_output_education, file = here::here("data", "dcpo_output_education.rda"))
+```
+
+```{r theta_res_political}
+load(here::here("data", "dcpo_input_political.rda"))
+load(here::here("data", "dcpo_output_political.rda"))
+
+dat <- dcpo_input_political$data
+
+qcodes <- dat %>%
+  dplyr::group_by(question) %>%
+  dplyr::summarize(qq = first(qq) %>%
+                     as.numeric())
+
+kcodes <- dat %>%
+  dplyr::group_by(country) %>%
+  dplyr::summarize(kk = first(kk) %>%
+                     as.numeric())
+
+tcodes <- dat %>%
+  dplyr::group_by(year) %>%
+  dplyr::summarize(tt = first(tt))
+
+ktcodes <- dat %>%
+  dplyr::group_by(country) %>%
+  dplyr::summarize(first_yr = min(year),
+                   last_yr = max(year))
+
+theta_res_political <- rstan::extract(dcpo_output_political, pars = "theta") %>%
+        dplyr::first() %>%
+        purrr::array_branch(1) %>%
+        purrr::map(function(x) {
+          tibble::as_tibble(x) %>%
+          dplyr::mutate(tt = dplyr::row_number()) %>%
+            dplyr::left_join(tcodes, by = "tt") %>%
+            tidyr::pivot_longer(cols = starts_with("V"),
+                                names_to = "kk",
+                                values_to = "pge_mean") %>%
+            dplyr::mutate(year = if_else(tt == 1,
+                                         as.integer(year),
+                                         as.integer(min(year, na.rm = TRUE) + tt - 1)),
+                          kk = stringr::str_replace(kk, "V", "") %>% as.numeric()) %>%
+            dplyr::left_join(kcodes, by = "kk") %>%
+            dplyr::left_join(ktcodes, by = "country") %>%
+            dplyr::filter(year >= first_yr & year <= last_yr) %>%
+            dplyr::arrange(kk, tt) %>%
+            dplyr::select(country, year, pge_mean) %>% 
+            dplyr::rename(political_mean = pge_mean)
+        })
+```
+
+```{r theta_res_workplace}
+load(here::here("data", "dcpo_input_workplace.rda"))
+load(here::here("data", "dcpo_output_workplace.rda"))
+
+dat <- dcpo_input_workplace$data
+
+qcodes <- dat %>%
+  dplyr::group_by(question) %>%
+  dplyr::summarize(qq = first(qq) %>%
+                     as.numeric())
+
+kcodes <- dat %>%
+  dplyr::group_by(country) %>%
+  dplyr::summarize(kk = first(kk) %>%
+                     as.numeric())
+
+tcodes <- dat %>%
+  dplyr::group_by(year) %>%
+  dplyr::summarize(tt = first(tt))
+
+ktcodes <- dat %>%
+  dplyr::group_by(country) %>%
+  dplyr::summarize(first_yr = min(year),
+                   last_yr = max(year))
+
+theta_res_workplace <- rstan::extract(dcpo_output_workplace, pars = "theta") %>%
+        dplyr::first() %>%
+        purrr::array_branch(1) %>%
+        purrr::map(function(x) {
+          tibble::as_tibble(x) %>%
+          dplyr::mutate(tt = dplyr::row_number()) %>%
+            dplyr::left_join(tcodes, by = "tt") %>%
+            tidyr::pivot_longer(cols = starts_with("V"),
+                                names_to = "kk",
+                                values_to = "pge_mean") %>%
+            dplyr::mutate(year = if_else(tt == 1,
+                                         as.integer(year),
+                                         as.integer(min(year, na.rm = TRUE) + tt - 1)),
+                          kk = stringr::str_replace(kk, "V", "") %>% as.numeric()) %>%
+            dplyr::left_join(kcodes, by = "kk") %>%
+            dplyr::left_join(ktcodes, by = "country") %>%
+            dplyr::filter(year >= first_yr & year <= last_yr) %>%
+            dplyr::arrange(kk, tt) %>%
+            dplyr::select(country, year, pge_mean) %>% 
+            dplyr::rename(workplace_mean = pge_mean)
+        })
+```
+
+```{r theta_res_education}
+load(here::here("data", "dcpo_input_education.rda"))
+load(here::here("data", "dcpo_output_education.rda"))
+
+dat <- dcpo_input_education$data
+
+qcodes <- dat %>%
+  dplyr::group_by(question) %>%
+  dplyr::summarize(qq = first(qq) %>%
+                     as.numeric())
+
+kcodes <- dat %>%
+  dplyr::group_by(country) %>%
+  dplyr::summarize(kk = first(kk) %>%
+                     as.numeric())
+
+tcodes <- dat %>%
+  dplyr::group_by(year) %>%
+  dplyr::summarize(tt = first(tt))
+
+ktcodes <- dat %>%
+  dplyr::group_by(country) %>%
+  dplyr::summarize(first_yr = min(year),
+                   last_yr = max(year))
+
+theta_res_education <- rstan::extract(dcpo_output_education, pars = "theta") %>%
+        dplyr::first() %>%
+        purrr::array_branch(1) %>%
+        purrr::map(function(x) {
+          tibble::as_tibble(x) %>%
+          dplyr::mutate(tt = dplyr::row_number()) %>%
+            dplyr::left_join(tcodes, by = "tt") %>%
+            tidyr::pivot_longer(cols = starts_with("V"),
+                                names_to = "kk",
+                                values_to = "pge_mean") %>%
+            dplyr::mutate(year = if_else(tt == 1,
+                                         as.integer(year),
+                                         as.integer(min(year, na.rm = TRUE) + tt - 1)),
+                          kk = stringr::str_replace(kk, "V", "") %>% as.numeric()) %>%
+            dplyr::left_join(kcodes, by = "kk") %>%
+            dplyr::left_join(ktcodes, by = "country") %>%
+            dplyr::filter(year >= first_yr & year <= last_yr) %>%
+            dplyr::arrange(kk, tt) %>%
+            dplyr::select(country, year, pge_mean) %>% 
+            dplyr::rename(education_mean = pge_mean)
+        })
+```
+
+```{r}
+load(here::here("data", "pge.rda"))
+load(here::here("data", "dcpo_input.rda"))
+
+pge_pw <- map(1:1000, function(x) {
+  pge[[x]] %>% 
+    left_join(theta_res_political[[x]], by = c("country", "year")) %>% 
+    left_join(theta_res_workplace[[x]], by = c("country", "year")) %>% 
+    left_join(theta_res_education[[x]], by = c("country", "year"))
+})
+
+pge_political_cor <- map(pge_pw, function(x) {
+  with(x, cor(pge_mean, political_mean, use = "pairwise.complete.obs"))
+  }) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2)
+
+pge_workplace_cor <- map(pge_pw, function(x) {
+  with(x, cor(pge_mean, workplace_mean, use = "pairwise.complete.obs"))
+  }) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2)
+
+pge_education_cor <- map(pge_pw, function(x) {
+  with(x, cor(pge_mean, education_mean, use = "pairwise.complete.obs"))
+  }) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2)
+
+political_workplace_cor <- map(pge_pw, function(x) {
+  with(x, cor(political_mean, workplace_mean, use = "pairwise.complete.obs"))
+  }) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2)
+
+political_education_cor <- map(pge_pw, function(x) {
+  with(x, cor(political_mean, education, use = "pairwise.complete.obs"))
+  }) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2)
+
+workplace_education_cor <- map(pge_pw, function(x) {
+  with(x, cor(workplace_mean, education, use = "pairwise.complete.obs"))
+  }) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2)
+```
+
+```{r workplace_construct}
+# https://genderstats.un.org/#/downloads
+lfpr_un <- read_csv(here::here("data", "3b - Labour force participation rate for persons aged 15+  by sex_data.csv"), skip = 1, col_types = "ccdcdcdccccccdddcc") %>% 
+  select(Country, Year, Sex, Value) %>% 
+  pivot_wider(names_from = Sex,
+              values_from = Value) %>% 
+  transmute(country = countrycode::countrycode(Country, 
+                                               origin = "country.name",
+                                               destination = "country.name"),
+            iso2c = countrycode::countrycode(country,
+                                             origin = "country.name",
+                                             destination = "iso2c"),
+            year = Year,
+            flfpr = Female,
+            f2m_ratio = round(Female/Male*100, 2)) %>% 
+  filter(!is.na(country) & !is.na(flfpr)) %>% 
+  left_join(pge[[1]], by = c("country", "year")) %>% 
+  filter(!is.na(pge_mean)) %>% 
+  select(-pge_mean, -pge_polarization)
+
+pge_pw_lfpr <- pge_pw %>% 
+  map(. %>% right_join(lfpr_un, 
+                       by = c("country", "year")))
+
+lfpr_cor <- map(pge_pw_lfpr, function(x) {
+  x %>% 
+    filter(year == 2016) %>% 
+    with(cor(workplace_mean, f2m_ratio, use = "pairwise.complete.obs"))
+  }) %>% 
+  unlist() %>% 
+  mean() %>% 
+  round(2) %>% 
+  paste0("R = ", .)
+
+```

### 2021-06-16 paper/dcpo_gender_roles.Rmd
update
poliwork only

@@
 ```{r dcpo, eval=FALSE}
-iter <- 4000
+iter <- 5000
 
@@
 ```{r dcpo_results}
-load(here::here("data", "polileader4_2_4k_01-08.rda"))
+load(here::here("data", "polileader4_2_5k_05-19.rda")) # poliwork
 
@@
 The Scandinavian countries and France are at the top of this list, along with Puerto Rico, which has had women of both of its major parties serve as chief executive and as recently as 2020 had a woman from each party holding the two most prominent elected offices on the island.
-The latest scores for Egypt, Yemen, Pakistan, the Palestinian Territories, and Burkina Faso have them as the places where public opinion is least favorable to gender equality in the public sphere.
+The latest available scores for Pakistan, Egypt, Yemen, Uzbekistan, and Burkina Faso have them as the places where public opinion is least favorable to gender equality in the public sphere.
 
 ```{r ts_plots, fig.cap="PGE Scores Over Time Within Selected Countries \\label{ts}", fig.height=3.5}
-countries <- c("Norway", "Australia", "United States", "Argentina",
-               "Brazil", "Poland", "South Africa", "Japan",
-               "Turkey", "China", "South Korea", "India", 
-               "Nigeria", "Philippines", "Indonesia", "Egypt")
-
-countries2 <- c("Norway", "Australia", "U.S.", "Argentina",
-               "Brazil", "Poland", "South Africa", "Japan",
-               "Turkey", "China", "South Korea", "India", 
-               "Nigeria", "Philippines", "Indonesia", "Egypt")
+countries <- c("Norway", "Australia", "United States", "Brazil",
+               "Argentina", "Poland", "Japan", "China",
+               "South Korea", "Turkey", "South Africa", "Philippines", 
+               "India", "Nigeria", "Indonesia", "Egypt")
+
+countries2 <- countries %>% 
+  str_replace("United States", "U.S.")
 
@@
 
-internal_cs_label <- tibble(mean = .7, prop = .77, label = internal_cs_cor)
+internal_cs_label <- tibble(mean = .69, prop = .76, label = internal_cs_cor)
 
@@
   x %>% 
-    filter(year == 2016) %>% 
+    filter(year == 2017) %>% 
     with(cor(pge_mean, f2m_ratio))
@@
   as_tibble() %>% 
+  filter(!COU=="OAVG") %>% 
   transmute(country = countrycode::countrycode(COU, "iso3c", "country.name"),
@@
 As attitudes toward gender egalitarianism in the public sphere plausibly both cause and are caused by women's gains in the workplace, strong relationships between the PGE scores and measures of workplace gender equality provide construct validation for our measure.
-In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
+In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2017))` countries in 2017, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
 In the right panel, we plot the PGE scores against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].

### 2021-06-16 paper/pge_appendix.Rmd
add Appendix C on pwe indices

@@
 # Appendix C: 
-```{r create_pwe_indices}
+```{r create_pwe_indices, eval=FALSE}
 dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
@@
 
-dcpo_input_public_political <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
+dcpo_input_political <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
                                             scale_q = "polileader4",
@@
 save(dcpo_input_education, file = here::here("data", "dcpo_input_education.rda"))
+```
+
+```{r dcpo_public_b, eval=FALSE}
+dcpo_input_raw_public_b <- dcpo_input_raw_public1 %>% 
+  filter(political==1 | workplace==1)
+
+dcpo_input_public_b <- DCPOtools::format_dcpo(dcpo_input_raw_public_b,
+                                            scale_q = "polileader4",
+                                            scale_cp = 2)
+save(dcpo_input_public_b, file = here::here("data", "dcpo_input_public_b.rda"))
+
 ```
@@
 
-```{r political}
+```{r political, eval=FALSE}
 load(here::here("data", "political_polileader4_2_4k.rda"))
@@
 
-```{r workplace}
+```{r workplace, eval=FALSE}
 load(here::here("data", "workplace_job3a_2_5k.rda"))
@@
 
-```{r education}
+```{r education, eval=FALSE}
 load(here::here("data", "education_education4_2_5k.rda"))
@@
     left_join(theta_res_education[[x]], by = c("country", "year"))
-})
+}) %>% 
+  map(. %>% left_join(dcpo_input$data %>% 
+                         filter(item == "education4 3 or higher") %>% 
+                         rowwise() %>% 
+                         transmute(country = country,
+                                   year = year,
+                                   prop = y_r/n_r,
+                                   se = sqrt((prop*(1-prop))/n),
+                                   edu = rnorm(1, mean = prop, sd = se)), 
+                       by = c("country", "year")))
 

### 2021-06-21 paper/dcpo_gender_roles.Rmd
update; add cite to Gray2006; fuss with caches; add fn re Appendix B; use knitr::combine_words; automate reference to bottom five countries

--- 2021-01-08 paper/dcpo_gender_roles.Rmd
@@
 Drawing on recent advances in latent variable modeling of public opinion and a comprehensive collection of survey data, we present the Public Gender Egalitarianism dataset to address this need: comparable estimates of the public's attitudes on gender equality in the public sphere across more than one hundred countries over time.
-These PGE scores are strongly correlated with responses to individual survey items and with rates of participation in the labor force and corporate boards.
+These PGE scores are strongly correlated with responses to individual survey items and with women's rates of participation in the labor force and corporate boards.
 We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in the public sphere.
-[148/150 words]"
+[149/150 words]"
 keywords: "gender roles, gender inequality, public opinion, political culture, measurement"
@@
 
-knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE,
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                       fig.width=7, fig.height=2.5)
@@
 
-Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture or ideology or public opinion---constitute one of the primary explanations for women's exclusion from political power and policy influence [see, e.g., @Yates2017, 103-104; @Paxton2021, 113-114].
-Yet even a half century after @RuleKrauss1974 [, 1719] called in the pages of the _APSR_ for more and better data on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
+Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture, norms, ideology or public opinion---constitute one of the primary explanations for women's exclusion from the traditionally masculine public sphere of education, the workforce, and political power and policy influence [see, e.g., @Gray2006, 299-302; @Yates2017, 103-104; @Paxton2021, 113-114].
+Yet even a half century after @RuleKrauss1974 [, 1719] called for more and better data on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
 In the decades since, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
@@
 
-```{r dcpo_input_raw, include=FALSE, cache.extra = tools::md5sum(here::here("data-raw", "surveys_egr.csv"))}
+```{r dcpo_input_raw, include=FALSE, cache = TRUE, cache.extra = tools::md5sum(here::here("data-raw", "surveys_egr.csv"))}
 surveys_egr <- read_csv(here::here("data-raw", "surveys_egr_classification.csv"),
@@
 
-```{r egr_summary_stats}
+```{r egr_summary_stats, cache = TRUE, cache.extra = tools::md5sum(here::here("data-raw", "dcpo_input_raw_public.csv"))}
 dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
@@
 In all, we identified `r n_items` such survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.^[
-The complete list of public gender egalitarianism survey items is included in the Appendix.]
+The complete list of public gender egalitarianism survey items is included in online Appendix A.
+A discussion of excluded survey items---those covering the related but distinct concepts of gender equality in the private sphere, how women should balance opportunities in the public sphere with their traditional duties in the private sphere, or issues of gender dominance such as sexual harassment---is found in online Appendix B.]
 Together, the survey items in the source data were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
@@
   pull(country) %>% 
-  paste(collapse = ", ") %>% 
-  str_replace(", (\\w+)$", ", and \\1")
+  knitr::combine_words()
 
@@
 adding <- setdiff(countries_cbyp, countries_cp) %>% 
-  paste(collapse = ", ") %>% 
-  str_replace(", (\\w*)$", ", and \\1")
+  knitr::combine_words()
 
 dropping <- setdiff(countries_cp, countries_cbyp) %>% 
-  paste(collapse = ", ") %>% 
-  str_replace(", (\\w*)$", ", and \\1")
+  knitr::combine_words()
 
@@
 
-```{r dcpo_results}
-load(here::here("data", "polileader4_2_4k_01-08.rda"))
+```{r dcpo_results, cache=TRUE}
+load(here::here("data", "polileader4_2_4k_2020-06-19.rda"))
 
@@
 
-```{r dcpo_results_summary}
+```{r dcpo_results_summary, cache=TRUE, cache.extra = tools::md5sum(here::here("data", "dcpo_output.rda"))}
 load(here::here("data", "dcpo_input.rda"))
@@
 
+bottom5 <- p1_data %>% 
+  arrange(ranked) %>% 
+  slice(1:5) %>% 
+  pull(country_year) %>% 
+  str_replace(" \\(.*", "") %>% 
+  str_replace("Palestinian", "the Palestinian") %>% 
+  knitr::combine_words()
+
 ```
@@
 The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.
-Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries in the dataset.
+Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries and territories in the dataset.
 
 The Scandinavian countries and France are at the top of this list, along with Puerto Rico, which has had women of both of its major parties serve as chief executive and as recently as 2020 had a woman from each party holding the two most prominent elected offices on the island.
-The latest scores for Egypt, Yemen, Pakistan, the Palestinian Territories, and Burkina Faso have them as the places where public opinion is least favorable to gender equality in the public sphere.
+The latest scores for `r bottom5` have them as the places where public opinion is least favorable to gender equality in the public sphere.
 
@@
             dplyr::mutate(year = if_else(tt == 1,
-                                         year, min(year, na.rm = TRUE) + tt - 1),
+                                         as.numeric(year),
+                                         min(year, na.rm = TRUE) + tt - 1),
                           kk = str_replace(kk, "V", "") %>% as.numeric()) %>%
@@
 
-```{r convergent, fig.cap="Convergent Validation: Correlations Between PGE Scores and Individual PGE Source Data Survey Items \\label{conv_plot}", fig.height=4}
+```{r convergent_setup, cache = TRUE, cache.extra = tools::md5sum(here::here("data", "pge.rda"))}
 
@@
 
-internal_cs_label <- tibble(mean = .7, prop = .77, label = internal_cs_cor)
+internal_cs_label <- tibble(mean = .7, prop = .73, label = internal_cs_cor)
 
@@
 
-internal_us_label <- tibble(year = 1980, mean = .82, label = internal_us_cor)
+internal_us_label <- tibble(year = 1980, mean = .87, label = internal_us_cor)
 
@@
 
+```
+
+```{r convergent, cache = TRUE, cache.extra = tools::md5sum(here::here("data", "pge.rda")), fig.cap="Convergent Validation: Correlations Between PGE Scores and Individual PGE Source Data Survey Items \\label{conv_plot}", fig.height=4}
+
 internal_plot + internal_cs_plot + internal_us_plot +
@@
 In the left panel, we examine the four-point question on political leaders mentioned above, the most common item in the source data across all country-years.
-<!-- In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women." -->
-Then, in the center panel, we look at the question that provides most data-rich cross-section, which asked whether respondents felt "men generally make better political leaders than women," included in Pew Global's Spring 2007 survey.
-<!-- Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders." -->
+Then, in the center panel, we look at the question that provides the most data-rich cross-section, which asked whether respondents felt "men generally make better political leaders than women" and was included in Pew Global's Spring 2007 survey.
 Finally, in the right panel, to evaluate how well the PGE score captures change over time, we focus on the item with the largest number of observations for a single country, which asked respondents to the U.S.
 General Social Survey whether they agreed or disagreed that "most men are better suited emotionally for politics than are most women."
-<!-- Finally, in the right panel, to evaluate how well the PGE score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country.
--->
-<!-- The U.S. General Social Survey asked this question 25 times from 1972 to 2016. -->
-<!-- It asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women"; to facilitate visual comparison of the longitudinal relationship, we plot the estimated population proportion that disagreed with the statement.
--->
 In every case, the correlations---estimated taking into account the uncertainty in the measures^[
@@
 
-```{r construct_validation_survey, fig.cap="Construct Validation: Correlations Between PGE Scores and Individual 'Balancing' Gender Egalitarianism Survey Items \\label{surv_const_plot}", fig.height=4}
+```{r construct_validation_survey, cache = TRUE, cache.extra = tools::md5sum(here::here("data", "pge.rda")), fig.cap="Construct Validation: Correlations Between PGE Scores and Individual 'Balancing' Gender Egalitarianism Survey Items \\label{surv_const_plot}", fig.height=4}
 dcpo_input_balance <- DCPOtools::format_dcpo(dcpo_input_raw_balance1,
@@
 
-```{r cons_valid_plot, fig.cap="Construct Validation: Correlations Between PGE Scores and Indicators of Workplace Gender Equality \\label{construct_plot}", fig.height=4}
+```{r cons_valid}
 
@@
   round(2) %>% 
+  sprintf("%.2f", .) %>% 
   paste0("R = ", .)
@@
   geom_label(data = directors_label, aes(label = label))
-
+```
+
+```{r cons_valid_plot, fig.cap="Construct Validation: Correlations Between PGE Scores and Indicators of Workplace Gender Equality \\label{construct_plot}", fig.height=4}
 lfpr_plot + dir_plot +
   plot_annotation(caption = "Note: Gray whiskers represent 80% credible intervals.")
+
 ```

### 2021-06-21 paper/dcpo_gender_roles.Rmd
clean up

@@
 The @McGann2019 model depends on dense survey data unlike the sparse data on public gender egalitarianism described in the preceding section.
-@Kolczynska2020 is the very most recent of the five works and builds on each of the others, but the MRP approach developed in that piece is suitable not only when the available survey data are dense but also when ancillary data on population characteristics are available, so it is similarly inappropriate to this application.
-]
+@Kolczynska2020 is the very most recent of the five works and builds on each of the others, but the MRP approach developed in that piece is suitable not only when the available survey data are dense but also when ancillary data on population characteristics are available, so it is similarly inappropriate to this application.]
 
@@
 Then, in the center panel, we look at the question that provides the most data-rich cross-section, which asked whether respondents felt "men generally make better political leaders than women" and was included in Pew Global's Spring 2007 survey.
-Finally, in the right panel, to evaluate how well the PGE score captures change over time, we focus on the item with the largest number of observations for a single country, which asked respondents to the U.S.
+Finally, in the right panel, to evaluate how well the PGE scores capture change over time, we focus on the item with the largest number of observations for a single country, which asked respondents to the U.S.
 General Social Survey whether they agreed or disagreed that "most men are better suited emotionally for politics than are most women."

### 2021-06-21 paper/pge_appendix.Rmd
add plot to Appendix C; clean up

--- 2021-05-27 paper/pge_appendix.Rmd
@@
 
+\pagebreak
 # Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism
+
 ```{r pge_items}
@@
     group_by(question) %>% 
-    summarize(difficulties0 = paste0(round(mean, 2), collapse = ", ")) %>% 
+    summarize(difficulties0 = paste0(sprintf("%.2f", round(mean, 2)),
+                                     collapse = ", ")) %>% 
     mutate(item = question,
@@
 
-pge_items_table(1:9)
+pge_items_table(1:7) %>%
+  kableExtra::kable_styling(latex_options = "HOLD_position")
 ```
@@
 ```{r pge_items_table2}    
-pge_items_table(10:17)
+pge_items_table(8:14)
 ```
@@
 ```{r pge_items_table3}    
-pge_items_table(18:27)
+pge_items_table(15:23)
 ```
@@
 ```{r pge_items_table4}    
-pge_items_table(28:34)
+pge_items_table(24:31)
 ```
@@
 ```{r pge_items_table5}    
-pge_items_table(35:46)
+pge_items_table(32:42)
 ```
 
+\pagebreak
 ```{r pge_items_table6}    
-pge_items_table(47:49)
+pge_items_table(43:50)
 ```
-
-\vspace{-.45in}
-Notes: Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found in the cross-national survey dataset.
+\vspace{-.95in}
+Notes: Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found within the typical cross-national survey dataset.
 Lower values of dispersion ($\alpha$) indicate questions that better identify publics with more public gender egalitarianism from those with less.
@@
 
+\pagebreak
 # Appendix B: Excluded Survey Items
@@
 
-# Appendix C: 
+\pagebreak
+# Appendix C: Confirming the Unidimensionality of Public Gender Egalitarianism
+
+To provide further confirmation of the unidimensionality of public gender egalitarianism, we used the survey items listed in Appendix A to estimate separate indices of gender egalitarianism in politics, in the workplace, and in education.
+As shown in Figure \ref{pge_pwe_corr_plot}, these three indices all correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years.
+
 ```{r create_pwe_indices}
@@
 
-```{r}
+```{r pge_pwe_corr}
 load(here::here("data", "pge.rda"))
@@
 political_education_cor <- map(pge_pw, function(x) {
-  with(x, cor(political_mean, education, use = "pairwise.complete.obs"))
+  with(x, cor(political_mean, education_mean, use = "pairwise.complete.obs"))
   }) %>% 
@@
 workplace_education_cor <- map(pge_pw, function(x) {
-  with(x, cor(workplace_mean, education, use = "pairwise.complete.obs"))
+  with(x, cor(workplace_mean, education_mean, use = "pairwise.complete.obs"))
   }) %>% 
@@
   round(2)
+
+pge_pwe_corr_matrix <- matrix(c(1, pge_political_cor, pge_workplace_cor, pge_education_cor,
+                                pge_political_cor, 1, political_workplace_cor, political_education_cor,
+                                pge_workplace_cor, political_workplace_cor, 1, workplace_education_cor,
+                                pge_education_cor, political_education_cor, workplace_education_cor, 1), ncol = 4)
+colnames(pge_pwe_corr_matrix) <- c("Public\nGender\nEgalitarianism", "Political\nGender\nEgalitarianism", "Workplace\nGender\nEgalitarianism", "Education\nGender\nEgalitarianism")
 ```
 
-```{r workplace_construct}
-# https://genderstats.un.org/#/downloads
-lfpr_un <- read_csv(here::here("data", "3b - Labour force participation rate for persons aged 15+  by sex_data.csv"), skip = 1, col_types = "ccdcdcdccccccdddcc") %>% 
-  select(Country, Year, Sex, Value) %>% 
-  pivot_wider(names_from = Sex,
-              values_from = Value) %>% 
-  transmute(country = countrycode::countrycode(Country, 
-                                               origin = "country.name",
-                                               destination = "country.name"),
-            iso2c = countrycode::countrycode(country,
-                                             origin = "country.name",
-                                             destination = "iso2c"),
-            year = Year,
-            flfpr = Female,
-            f2m_ratio = round(Female/Male*100, 2)) %>% 
-  filter(!is.na(country) & !is.na(flfpr)) %>% 
-  left_join(pge[[1]], by = c("country", "year")) %>% 
-  filter(!is.na(pge_mean)) %>% 
-  select(-pge_mean, -pge_polarization)
-
-pge_pw_lfpr <- pge_pw %>% 
-  map(. %>% right_join(lfpr_un, 
-                       by = c("country", "year")))
-
-lfpr_cor <- map(pge_pw_lfpr, function(x) {
-  x %>% 
-    filter(year == 2016) %>% 
-    with(cor(workplace_mean, f2m_ratio, use = "pairwise.complete.obs"))
-  }) %>% 
-  unlist() %>% 
-  mean() %>% 
-  round(2) %>% 
-  paste0("R = ", .)
-
+```{r pge_pwe_corr_plot, fig.width=7, fig.cap = "Pairwise Correlations Among PGE Index and Separate Political, Workplace, and Education Egalitarianism Indices  \\label{pge_pwe_corr_plot}"}
+corrplot::corrplot.mixed(pge_pwe_corr_matrix, tl.col = "black", tl.cex = .8, upper = "ellipse")
 ```

### 2021-06-21 paper/pge_appendix.Rmd
fix dcpo_input_* for separate indices in Appendix C

@@
 
-dcpo_input_political <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
+dcpo_input_political <- DCPOtools::format_dcpo(dcpo_input_raw_political1,
                                             scale_q = "polileader4",
@@
 
-dcpo_input_workplace <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
+dcpo_input_workplace <- DCPOtools::format_dcpo(dcpo_input_raw_workplace1,
                                             scale_q = "job3a",
@@
 
-dcpo_input_education <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
+dcpo_input_education <- DCPOtools::format_dcpo(dcpo_input_raw_education1,
                                             scale_q = "education4",

### 2021-06-22 paper/dcpo_gender_roles.Rmd
add footnote re Appendix C

@@
 We used the `DCPO` package for R [@Solt2020a] to estimate this model on the public gender egalitarianism source data described above.
+The dispersion parameters of the survey items indicate that all of them load well on the latent variable (see online Appendix A).^[
+To provide further confirmation of the unidimensionality of public gender egalitarianism, we divided the source data described above to estimate separate indices of gender egalitarianism in politics, in the workplace, and in education.
+The resulting indices all correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.]
 The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.

### 2021-06-22 paper/dcpo_gender_roles.Rmd

@@
 
-dcpo_input_raw_private <- DCPOtools::dcpo_setup(vars = surveys_egr_private,
-                                               datapath = here::here("..",
-                                                                     "data", "dcpo_surveys"),
-                                               file = here::here("data",
-                                                                 "dcpo_input_raw_private.csv"))
-
-dcpo_input_raw_balance <- DCPOtools::dcpo_setup(vars = surveys_egr_balance,
-                                               datapath = here::here("..",
-                                                                     "data", "dcpo_surveys"),
-                                               file = here::here("data",
-                                                                 "dcpo_input_raw_balance.csv"))
-
-dcpo_input_raw_dominance <- DCPOtools::dcpo_setup(vars = surveys_egr_dominance,
-                                               datapath = here::here("..",
-                                                                     "data", "dcpo_surveys"),
-                                               file = here::here("data",
-                                                                 "dcpo_input_raw_dominance.csv"))
 ```
@@
                                   col_types = "cdcddcd")
+
+public_items <- read_csv(here::here("data-raw", "public_items.csv"),
+                         col_types = "ccddd")
 
@@
 
-dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public)
+dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public) %>% 
+  left_join(public_items, by = "item")
+dcpo_input_raw_poliwork1 <- dcpo_input_raw_public1 %>% 
+  filter(political==1|workplace==1)
+
 dcpo_input_raw_private1 <- process_dcpo_input_raw(dcpo_input_raw_private)
@@
 
-n_items <- dcpo_input_raw_public1 %>%
+n_items <- dcpo_input_raw_poliwork1 %>%
   distinct(item) %>% 
@@
 
-n_countries <- dcpo_input_raw_public1 %>%
+n_countries <- dcpo_input_raw_poliwork1 %>%
   distinct(country) %>% 
@@
 
-n_cy <- dcpo_input_raw_public1 %>%
+n_cy <- dcpo_input_raw_poliwork1 %>%
   distinct(country, year) %>% 
@@
 
-n_years <- as.integer(summary(dcpo_input_raw_public1$year)[6]-summary(dcpo_input_raw_public1$year)[1])
-
-spanned_cy <- dcpo_input_raw_public1 %>% 
+n_years <- as.integer(summary(dcpo_input_raw_poliwork1$year)[6]-summary(dcpo_input_raw_poliwork1$year)[1])
+
+spanned_cy <- dcpo_input_raw_poliwork1 %>% 
   group_by(country) %>% 
@@
 year_range <- paste("from",
-                    summary(dcpo_input_raw_public1$year)[1],
+                    summary(dcpo_input_raw_poliwork1$year)[1],
                     "to",
-                    summary(dcpo_input_raw_public1$year)[6])
-
-n_cyi <- dcpo_input_raw_public1 %>% 
+                    summary(dcpo_input_raw_poliwork1$year)[6])
+
+n_cyi <- dcpo_input_raw_poliwork1 %>% 
   distinct(country, year, item) %>% 
@@
 ```{r item_and_country_plots, fig.height = 3.5, fig.cap = "Countries and Years with the Most Observations in the PGE Source Data \\label{item_country_plots}"}
-items_plot <- dcpo_input_raw_public1 %>%
+items_plot <- dcpo_input_raw_poliwork1 %>%
   distinct(country, year, item) %>%
@@
 
-polileader4_cy <- dcpo_input_raw_public1 %>% filter(item == "polileader4") %>% distinct(country, year) %>% nrow()
-
-polileader4_surveys <- dcpo_input_raw_public1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)
-
-countries_plot <- dcpo_input_raw_public1 %>%
+polileader4_cy <- dcpo_input_raw_poliwork1 %>% filter(item == "polileader4") %>% distinct(country, year) %>% nrow()
+
+polileader4_surveys <- dcpo_input_raw_poliwork1 %>% filter(item == "polileader4") %>% distinct(survey) %>% pull(survey)
+
+countries_plot <- dcpo_input_raw_poliwork1 %>%
   mutate(country = if_else(stringr::str_detect(country, "United"),
@@
 
-cby_plot <- dcpo_input_raw_public1 %>%
+cby_plot <- dcpo_input_raw_poliwork1 %>%
   mutate(country = if_else(stringr::str_detect(country, "United"),
@@
 
-ybc_plot <- dcpo_input_raw_public1 %>%
+ybc_plot <- dcpo_input_raw_poliwork1 %>%
   distinct(country, year) %>%
@@
 
-us_obs <- dcpo_input_raw_public1 %>% 
+us_obs <- dcpo_input_raw_poliwork1 %>% 
   distinct(country, year, item) %>%
@@
 
-others <- dcpo_input_raw_public1 %>%
+others <- dcpo_input_raw_poliwork1 %>%
   distinct(country, year, item) %>%
@@
 
-countries_cp <- dcpo_input_raw_public1 %>%
+countries_cp <- dcpo_input_raw_poliwork1 %>%
   mutate(country = if_else(stringr::str_detect(country, "United"),
@@
 
-countries_cbyp <- dcpo_input_raw_public1 %>%
+countries_cbyp <- dcpo_input_raw_poliwork1 %>%
   mutate(country = if_else(stringr::str_detect(country, "United"),
@@
 
-y_peak_year <- dcpo_input_raw_public1 %>%
+y_peak_year <- dcpo_input_raw_poliwork1 %>%
   distinct(country, year) %>%
@@
 
-y_peak_nn <- dcpo_input_raw_public1 %>%
+y_peak_nn <- dcpo_input_raw_poliwork1 %>%
   distinct(country, year) %>%
@@
 
-data_poorest <- dcpo_input_raw_public1 %>%
+data_poorest <- dcpo_input_raw_poliwork1 %>%
   distinct(country, year, item) %>%
@@
 ```{r dcpo_input_public}
-dcpo_input_public <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
+dcpo_input_poliwork <- DCPOtools::format_dcpo(dcpo_input_raw_poliwork1,
                                             scale_q = "polileader4",
                                             scale_cp = 2)
-save(dcpo_input_public, file = here::here("data", "dcpo_input_public.rda"))
+save(dcpo_input_poliwork, file = here::here("data", "dcpo_input_poliwork.rda"))
 ```
@@
 
-dcpo_input <- dcpo_input_public
+dcpo_input <- dcpo_input_poliwork
 
@@
 ```{r dcpo_results, cache=TRUE}
-load(here::here("data", "polileader4_2_4k_2020-06-19.rda"))
+load(here::here("data", "polileader4_2_5k_05-19.rda")) # poliwork
 
@@
 
-countries2 <- c("Norway", "Australia", "U.S.", "Argentina",
-               "Brazil", "Poland", "South Africa", "Japan",
-               "Turkey", "China", "South Korea", "India", 
-               "Nigeria", "Philippines", "Indonesia", "Egypt")
+countries2 <- countries %>% 
+  str_replace("United States", "U.S.")
 

### 2021-06-22 paper/dcpo_gender_roles.Rmd
update

@@
 
+dcpo_input_raw_private <- DCPOtools::dcpo_setup(vars = surveys_egr_private,
+                                               datapath = here::here("..",
+                                                                     "data", "dcpo_surveys"),
+                                               file = here::here("data",
+                                                                 "dcpo_input_raw_private.csv"))
+
+dcpo_input_raw_balance <- DCPOtools::dcpo_setup(vars = surveys_egr_balance,
+                                               datapath = here::here("..",
+                                                                     "data", "dcpo_surveys"),
+                                               file = here::here("data",
+                                                                 "dcpo_input_raw_balance.csv"))
+
+dcpo_input_raw_dominance <- DCPOtools::dcpo_setup(vars = surveys_egr_dominance,
+                                               datapath = here::here("..",
+                                                                     "data", "dcpo_surveys"),
+                                               file = here::here("data",
+                                                                 "dcpo_input_raw_dominance.csv"))
 ```
@@
 ```{r dcpo_results, cache=TRUE}
-load(here::here("data", "polileader4_2_5k_05-19.rda")) # poliwork
+load(here::here("data", "poliwork_polileader4_2_5k_05-19.rda"))
 

### 2021-06-23 paper/dcpo_gender_roles.Rmd
update; use 2017 for lfpr

@@
 ```{r dcpo_results, cache=TRUE}
-load(here::here("data", "poliwork_polileader4_2_5k_05-19.rda"))
+load(here::here("data", "poliwork_polileader4_2_2k.rda"))
 
@@
   coord_cartesian(xlim=c(0, 1)) +
-  labs(x = "Public Gender Egalitarianism, 2016", y = "Female to Male Labor Force Participation Ratio, 2016") +
+  labs(x = "Public Gender Egalitarianism, 2017", y = "Female to Male Labor Force Participation Ratio, 2017") +
   geom_label(data = lfpr_label, aes(label = label))
@@
 As attitudes toward gender egalitarianism in the public sphere plausibly both cause and are caused by women's gains in the workplace, strong relationships between the PGE scores and measures of workplace gender equality provide construct validation for our measure.
-In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
+In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2017))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
 In the right panel, we plot the PGE scores against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].

### 2021-06-30 paper/dcpo_gender_roles.Rmd
update; clean up

@@
 anonymous: false
-abstract: "Societal attitudes toward gender roles in education, the workplace, and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories.
+abstract: "Societal attitudes toward gender roles in the workplace and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories.
 Drawing on recent advances in latent variable modeling of public opinion and a comprehensive collection of survey data, we present the Public Gender Egalitarianism dataset to address this need: comparable estimates of the public's attitudes on gender equality in the public sphere across more than one hundred countries over time.
@@
 We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in the public sphere.
-[149/150 words]"
+[148/150 words]"
 keywords: "gender roles, gender inequality, public opinion, political culture, measurement"
@@
 
-Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture, norms, ideology or public opinion---constitute one of the primary explanations for women's exclusion from the traditionally masculine public sphere of education, the workforce, and political power and policy influence [see, e.g., @Gray2006, 299-302; @Yates2017, 103-104; @Paxton2021, 113-114].
+Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture, norms, ideology, or public opinion---constitute one of the primary explanations for women's exclusion from the traditionally masculine public sphere of the workforce, political power, and policy influence [see, e.g., @Gray2006, 299-302; @Yates2017, 103-104; @Paxton2021, 113-114].
 Yet even a half century after @RuleKrauss1974 [, 1719] called for more and better data on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
@@
 In this letter, we present the Public Gender Egalitarianism (PGE) dataset, which is based on the host of survey data available and recent advances in latent variable modeling of public opinion that allow us to make use of this sparse and incomparable data.
-It provides comparable estimates of the public's attitudes on gender equality in the public sphere of politics, paid work, and education across countries and over time.
+It provides comparable estimates of the public's attitudes on gender equality in the public sphere of politics and paid work across countries and over time.
 We show that these PGE scores are strongly correlated with responses to single survey items as well as with measures of women's participation in the workforce and in the boardroom.
@@
 The DCPO model is a population-level two-parameter ordinal logistic item response theory (IRT) model with country-specific item bias.
-That is, $\eta_{ktqr}$, the expected probability that a random person in country $k$ at time $t$ answers question $q$ with a response at least as positive as response $r$, is estimated as varying with the mean and standard deviation of the unbounded latent trait of public opinion, $\bar{\theta'}_{kt}$ and $\sigma_{kt}$; with the dispersion, $\alpha_{q}$, of the question and the difficulty, $\beta_{qr}$, of the question's response category; as well as with a term to capture how responses to particular questions in particular questions may be biased, $\delta_{kq}$: $\eta_{ktqr} = \textrm{logit}^{-1}(\frac{\bar{\theta'}_{kt} - (\beta_{qr} + \delta_{kq})}{\sqrt{\alpha_{q}^2 + (1.7*\sigma_{kt})^2}}) \label{eq:dcpo}$.
+That is, $\eta_{ktqr}$, the expected probability that a random person in country $k$ at time $t$ answers question $q$ with a response at least as positive as response $r$, is estimated as varying with the mean and standard deviation of the unbounded latent trait of public opinion, $\bar{\theta'}_{kt}$ and $\sigma_{kt}$; with the dispersion, $\alpha_{q}$, of the question and the difficulty, $\beta_{qr}$, of the question's response category; as well as with a term to capture how responses to particular questions in particular questions may be biased in particular countries, $\delta_{kq}$: $\eta_{ktqr} = \textrm{logit}^{-1}(\frac{\bar{\theta'}_{kt} - (\beta_{qr} + \delta_{kq})}{\sqrt{\alpha_{q}^2 + (1.7*\sigma_{kt})^2}}) \label{eq:dcpo}$.
 A beta-binomial distribution is used to model the observed survey data given $\eta_{ktqr}$, random-walk priors are used to account for the dynamics in $\bar{\theta'}_{kt}$ and $\sigma_{kt}$, and weakly informative priors are placed on the other parameters.
@@
 ```{r dcpo_results, cache=TRUE}
-load(here::here("data", "poliwork_polileader4_2_2k.rda"))
+load(here::here("data", "poliwork_polileader4_2_4k_06-23.rda"))
 
@@
 The dispersion parameters of the survey items indicate that all of them load well on the latent variable (see online Appendix A).^[
-To provide further confirmation of the unidimensionality of public gender egalitarianism, we divided the source data described above to estimate separate indices of gender egalitarianism in politics, in the workplace, and in education.
-The resulting indices all correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.]
+To provide further confirmation of the unidimensionality of public gender egalitarianism, we divided the source data described above to estimate separate indices of gender egalitarianism (a) in politics and (b) in the workplace.
+The two resulting indices correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.]
 The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.
@@
 Convergent validation refers to showing that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
-Here, we compare PGE scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
+Here, we compare PGE scores to responses to individual survey items that were included in the source data, that is, we provide an 'internal' validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
 In the left panel, we examine the four-point question on political leaders mentioned above, the most common item in the source data across all country-years.
@@
 In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from a related category of gender egalitarianism, namely questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
-Assuming that attitudes that women should prioritize housework and childcare over education, paid employment, and politics---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE score.
+Assuming that attitudes that women should prioritize housework and childcare over paid employment and politics---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE scores.
 Exemplars of such items across all available country-years ("a job is alright but what most women really want is a home and children" from the WVS and EVS), in cross-section ("the most important role of a woman is to take care of her home and family" from the Eurobarometer 87.4), and in time series ("a pre-school child is likely to suffer if his or her mother works" from the German ALLBUS, WVS, and EVS) all show strong correlations with the PGE scores.
@@
 As attitudes toward gender egalitarianism in the public sphere plausibly both cause and are caused by women's gains in the workplace, strong relationships between the PGE scores and measures of workplace gender equality provide construct validation for our measure.
-In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2017))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
-In the right panel, we plot the PGE scores against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
+In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2017))` countries in 2017, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
+In the right panel, we plot the PGE scores against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries, also in 2017 [see @OECD2020].
 Both correlations are strong.

### 2021-09-11 paper/dcpo_gender_roles.Rmd

@@
   affiliation: University of Iowa
-anonymous: false
+anonymous: true
 abstract: "Societal attitudes toward gender roles in the workplace and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories.
@@
 
-Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture, norms, ideology, or public opinion---constitute one of the primary explanations for women's exclusion from the traditionally masculine public sphere of the workforce, political power, and policy influence [see, e.g., @Gray2006, 299-302; @Yates2017, 103-104; @Paxton2021, 113-114].
+Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture, norms, ideology, or public opinion---constitute one of the primary explanations for women's exclusion from the traditionally masculine public sphere of the workforce, political power, and policy influence [see, e.g., @Paxton2021, 113-114].
 Yet even a half century after @RuleKrauss1974 [, 1719] called for more and better data on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
 In the decades since, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
-As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].
+As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].
 Cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained persistently a topic for future research [@Paxton2010, 47].
@@
 
-Consider the most frequently asked item in the data we collected, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do."
-Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
-That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
+<!-- Consider the most frequently asked item in the data we collected, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do." -->
+<!-- Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
+-->
+<!-- That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
+-->
 
@@
 We used the `DCPO` package for R [@Solt2020a] to estimate this model on the public gender egalitarianism source data described above.
-The dispersion parameters of the survey items indicate that all of them load well on the latent variable (see online Appendix A).^[
-To provide further confirmation of the unidimensionality of public gender egalitarianism, we divided the source data described above to estimate separate indices of gender egalitarianism (a) in politics and (b) in the workplace.
-The two resulting indices correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.]
-The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.
+The dispersion parameters of the survey items indicate that all of them load well on the latent variable (see online Appendix A).
+The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.^[
+To provide further confirmation of the unidimensionality of public gender egalitarianism, we estimated two separate indices of gender egalitarianism in politics and in the workplace.
+These indices correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.]
 Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries and territories in the dataset.

### 2021-09-11 paper/pge_appendix.Rmd

@@
 
+public_items <- read_csv(here::here("data-raw", "public_items.csv"),
+                         col_types = "ccddd")
+
 process_dcpo_input_raw <- function(dcpo_input_raw_df) {
@@
 
-dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public)
+dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public) %>% 
+  left_join(public_items, by = "item")
+dcpo_input_raw_poliwork1 <- dcpo_input_raw_public1 %>% 
+  filter(political==1|workplace==1)
 
@@
 
-items_summary <- dcpo_input_raw_public1 %>%
+items_summary <- dcpo_input_raw_poliwork1 %>%
     dplyr::select(country, year, item, survey) %>%
@@
 ```{r pge_items_table4}    
-pge_items_table(24:31)
+pge_items_table(24:30)
 ```
@@
 ```{r pge_items_table5}    
-pge_items_table(32:42)
+pge_items_table(31:41)
 ```
@@
 ```{r pge_items_table6}    
-pge_items_table(43:50)
+pge_items_table(42:50)
 ```
@@
 # Appendix B: Excluded Survey Items
-To estimate the Public Gender Egalitarianism scores, we collected survey data on questions asking respondents' views of gender equality in the traditionally masculine public sphere of education, paid work, and politics.
-These included questions are nearly always explicit in comparing men and women (but see, for example, `unequalpol4`, which asked responses to the statement "Women do not have the necessary qualities and skills to fill positions of responsibility in politics") and nearly always explicitly invoke education, paid work, or politics, though they may also be broader (see, for example, `equalright2`, which asked "On a different subject, do you think women should have equal rights with men, or shouldn’t they?").
+To estimate the Public Gender Egalitarianism scores, we collected survey data on questions asking respondents' views of gender equality in the traditionally masculine public sphere of paid work and politics.
+These included questions are nearly always explicit in comparing men and women (but see, for example, `unequalpol4`, which asked responses to the statement "Women do not have the necessary qualities and skills to fill positions of responsibility in politics") and nearly always explicitly invoke either paid work or politics, though they may also be broader (see, for example, `equalright2`, which asked "On a different subject, do you think women should have equal rights with men, or shouldn’t they?").
 
@@
 Second, as noted in the text, we also excluded questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not, asked in the World Values Survey and many others.
-Given that attitudes that women should prioritize housework and childcare over education, paid employment, and politics---or convictions that there will be negative consequences if they do not---can be expected to lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, this is clearly a very closely related set of items to those we sought, and there are many of them.^[
+Given that attitudes that women should prioritize housework and childcare over paid employment and politics---or convictions that there will be negative consequences if they do not---can be expected to lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, this is clearly a very closely related set of items to those we sought, and there are many of them.^[
 It is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only rarely included in surveys; one laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly becoming more common, is the item querying respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
-The third and final category of excluded survey items includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.
-In each case, as the included questions are not _directly_ relevant to gender egalitarianism in the public sphere, we concluded that to ensure that the PGE scores tap only a single dimension of attitudes, we would exclude these others.
+The third and final category of excluded survey items includes respondents' views on various forms of women's domination by men, from whether wives should always adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.
+In each case, as the included questions are not _directly_ relevant to gender egalitarianism in the public sphere, we concluded that to ensure that the PGE scores tap only a single dimension of attitudes, we would exclude these others (see also Appendix C).
 Usefully, this decision also allows, when the available survey data permits, future research to take up the estimation of dynamic comparative public opinion of those concepts separately and their relationships to public gender egalitarianism.
@@
 
-To provide further confirmation of the unidimensionality of public gender egalitarianism, we used the survey items listed in Appendix A to estimate separate indices of gender egalitarianism in politics, in the workplace, and in education.
-As shown in Figure \ref{pge_pwe_corr_plot}, these three indices all correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years.
+To provide further confirmation of the unidimensionality of public gender egalitarianism, we used the survey items listed in Appendix A to estimate separate indices of gender egalitarianism in politics and in the workplace.
+As shown in Figure \ref{pge_pwe_corr_plot}, these two indices both correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years.
 
@@
   filter(workplace==1)
-dcpo_input_raw_education1 <- dcpo_input_raw_public1 %>% 
-  filter(education==1)
 
@@
 
-dcpo_input_education <- DCPOtools::format_dcpo(dcpo_input_raw_education1,
-                                            scale_q = "education4",
-                                            scale_cp = 2)
-save(dcpo_input_education, file = here::here("data", "dcpo_input_education.rda"))
 ```
@@
 
-```{r dcpo_education, eval=FALSE}
-iter <- 5000
-
-dcpo_output_education <- dcpo(dcpo_input_education,
-                              iter = iter,
-                              chains = 4,
-                              thin = iter/500, # this yields 250 draws per chain, 1000 draws total
-                              pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
-```
-
-```{r political}
+```{r political, eval=FALSE}
 load(here::here("data", "political_polileader4_2_4k.rda"))
@@
 save(dcpo_output_workplace, file = here::here("data", "dcpo_output_workplace.rda"))
-```
-
-```{r education}
-load(here::here("data", "education_education4_2_5k.rda"))
-
-dcpo_input_education <- dcpo_input
-
-dcpo_output_education <- dcpo_output
-
-save(dcpo_input_education, file = here::here("data", "dcpo_input_education.rda"))
-
-save(dcpo_output_education, file = here::here("data", "dcpo_output_education.rda"))
 ```
@@
 
-```{r theta_res_education}
-load(here::here("data", "dcpo_input_education.rda"))
-load(here::here("data", "dcpo_output_education.rda"))
-
-dat <- dcpo_input_education$data
-
-qcodes <- dat %>%
-  dplyr::group_by(question) %>%
-  dplyr::summarize(qq = first(qq) %>%
-                     as.numeric())
-
-kcodes <- dat %>%
-  dplyr::group_by(country) %>%
-  dplyr::summarize(kk = first(kk) %>%
-                     as.numeric())
-
-tcodes <- dat %>%
-  dplyr::group_by(year) %>%
-  dplyr::summarize(tt = first(tt))
-
-ktcodes <- dat %>%
-  dplyr::group_by(country) %>%
-  dplyr::summarize(first_yr = min(year),
-                   last_yr = max(year))
-
-theta_res_education <- rstan::extract(dcpo_output_education, pars = "theta") %>%
-        dplyr::first() %>%
-        purrr::array_branch(1) %>%
-        purrr::map(function(x) {
-          tibble::as_tibble(x) %>%
-          dplyr::mutate(tt = dplyr::row_number()) %>%
-            dplyr::left_join(tcodes, by = "tt") %>%
-            tidyr::pivot_longer(cols = starts_with("V"),
-                                names_to = "kk",
-                                values_to = "pge_mean") %>%
-            dplyr::mutate(year = if_else(tt == 1,
-                                         as.integer(year),
-                                         as.integer(min(year, na.rm = TRUE) + tt - 1)),
-                          kk = stringr::str_replace(kk, "V", "") %>% as.numeric()) %>%
-            dplyr::left_join(kcodes, by = "kk") %>%
-            dplyr::left_join(ktcodes, by = "country") %>%
-            dplyr::filter(year >= first_yr & year <= last_yr) %>%
-            dplyr::arrange(kk, tt) %>%
-            dplyr::select(country, year, pge_mean) %>% 
-            dplyr::rename(education_mean = pge_mean)
-        })
-```
-
 ```{r pge_pwe_corr}
@@
     left_join(theta_res_political[[x]], by = c("country", "year")) %>% 
-    left_join(theta_res_workplace[[x]], by = c("country", "year")) %>% 
-    left_join(theta_res_education[[x]], by = c("country", "year"))
+    left_join(theta_res_workplace[[x]], by = c("country", "year"))
 })
@@
 
-pge_education_cor <- map(pge_pw, function(x) {
-  with(x, cor(pge_mean, education_mean, use = "pairwise.complete.obs"))
-  }) %>% 
-  unlist() %>% 
-  mean() %>% 
-  round(2)
-
 political_workplace_cor <- map(pge_pw, function(x) {
@@
 
-political_education_cor <- map(pge_pw, function(x) {
-  with(x, cor(political_mean, education_mean, use = "pairwise.complete.obs"))
-  }) %>% 
-  unlist() %>% 
-  mean() %>% 
-  round(2)
-
-workplace_education_cor <- map(pge_pw, function(x) {
-  with(x, cor(workplace_mean, education_mean, use = "pairwise.complete.obs"))
-  }) %>% 
-  unlist() %>% 
-  mean() %>% 
-  round(2)
-
-pge_pwe_corr_matrix <- matrix(c(1, pge_political_cor, pge_workplace_cor, pge_education_cor,
-                                pge_political_cor, 1, political_workplace_cor, political_education_cor,
-                                pge_workplace_cor, political_workplace_cor, 1, workplace_education_cor,
-                                pge_education_cor, political_education_cor, workplace_education_cor, 1), ncol = 4)
-colnames(pge_pwe_corr_matrix) <- c("Public\nGender\nEgalitarianism", "Political\nGender\nEgalitarianism", "Workplace\nGender\nEgalitarianism", "Education\nGender\nEgalitarianism")
+pge_pwe_corr_matrix <- matrix(c(1, pge_political_cor, pge_workplace_cor,
+                                pge_political_cor, 1, political_workplace_cor,
+                                pge_workplace_cor, political_workplace_cor, 1),
+                              ncol = 3)
+colnames(pge_pwe_corr_matrix) <- c("Public\nGender\nEgalitarianism", "Political\nGender\nEgalitarianism", "Workplace\nGender\nEgalitarianism")
 ```
 
-```{r pge_pwe_corr_plot, fig.width=7, fig.cap = "Pairwise Correlations Among PGE Index and Separate Political, Workplace, and Education Egalitarianism Indices  \\label{pge_pwe_corr_plot}"}
+```{r pge_pwe_corr_plot, fig.width=7, fig.cap = "Pairwise Correlations Among PGE Index and Separate Political and Workplace Egalitarianism Indices  \\label{pge_pwe_corr_plot}"}
 corrplot::corrplot.mixed(pge_pwe_corr_matrix, tl.col = "black", tl.cex = .8, upper = "ellipse")

### 2021-12-30 paper/dcpo_gender_roles.Rmd
fix minor language issues; closes #29 @byngdeuk

@@
 Observations for every year in each country surveyed would number `r total_cy`, and a complete set of country-year-items would encompass `r {n_countries * n_years * n_items} %>% scales::comma()` observations.
-Viewed from this complete-data perspective, the available data can be seen to be very, very sparse.
+Compared to this complete set of country-year-items, the available data can be seen to be very, very sparse.
 From a more optimistic standpoint, we note there there are `r n_cy` country-years in which we have at least _some_ information about the public gender egalitarianism of the population, that is, some `r {back_to_numeric(n_cy)/back_to_numeric(spanned_cy) * 100} %>% round()`% of the `r spanned_cy` country-years spanned by the data we collected.
@@
 At the other end of the spectrum, `r n_data_poorest` countries---`r data_poorest`---have only the minimum two observations required to be included in the source dataset at all.
-The upper left panel shows the twelve countries with the most years observed; this group is similar, but with `r adding` joining the list and `r dropping` dropping off.
+The upper right panel shows the twelve countries with the most years observed; this group is similar, but with `r adding` joining the list and `r dropping` dropping off.
 The bottom panel counts the countries observed in each year and reveals just how few relevant survey items were asked before 1990.
@@
 The DCPO model is a population-level two-parameter ordinal logistic item response theory (IRT) model with country-specific item bias.
-That is, $\eta_{ktqr}$, the expected probability that a random person in country $k$ at time $t$ answers question $q$ with a response at least as positive as response $r$, is estimated as varying with the mean and standard deviation of the unbounded latent trait of public opinion, $\bar{\theta'}_{kt}$ and $\sigma_{kt}$; with the dispersion, $\alpha_{q}$, of the question and the difficulty, $\beta_{qr}$, of the question's response category; as well as with a term to capture how responses to particular questions in particular questions may be biased in particular countries, $\delta_{kq}$: $\eta_{ktqr} = \textrm{logit}^{-1}(\frac{\bar{\theta'}_{kt} - (\beta_{qr} + \delta_{kq})}{\sqrt{\alpha_{q}^2 + (1.7*\sigma_{kt})^2}}) \label{eq:dcpo}$.
+That is, $\eta_{ktqr}$, the expected probability that a random person in country $k$ at time $t$ answers question $q$ with a response at least as positive as response $r$, is estimated as varying with the mean and standard deviation of the unbounded latent trait of public opinion, $\bar{\theta'}_{kt}$ and $\sigma_{kt}$; with the dispersion, $\alpha_{q}$, of the question and the difficulty, $\beta_{qr}$, of the question's response category; as well as with a term to capture how responses to particular questions may be biased in particular countries, $\delta_{kq}$: $\eta_{ktqr} = \textrm{logit}^{-1}(\frac{\bar{\theta'}_{kt} - (\beta_{qr} + \delta_{kq})}{\sqrt{\alpha_{q}^2 + (1.7*\sigma_{kt})^2}}) \label{eq:dcpo}$.
 A beta-binomial distribution is used to model the observed survey data given $\eta_{ktqr}$, random-walk priors are used to account for the dynamics in $\bar{\theta'}_{kt}$ and $\sigma_{kt}$, and weakly informative priors are placed on the other parameters.
@@
     filter(year == 2017) %>% 
-    with(cor(pge_mean, f2m_ratio))
+    with(cor(pge_mean, f2m_ratio, use = "pairwise.complete.obs"))
   }) %>% 

### 2021-12-30 paper/dcpo_gender_roles.Rmd
Clarify that we use both national and cross-national surveys; #25 R2

@@
 
-In this letter, we present the Public Gender Egalitarianism (PGE) dataset, which is based on the host of survey data available and recent advances in latent variable modeling of public opinion that allow us to make use of this sparse and incomparable data.
+In this letter, we present the Public Gender Egalitarianism (PGE) dataset, which is based on the host of national and cross-national survey data available and recent advances in latent variable modeling of public opinion that allow us to make use of this sparse and incomparable data.
 It provides comparable estimates of the public's attitudes on gender equality in the public sphere of politics and paid work across countries and over time.
@@
 The bottom panel counts the countries observed in each year and reveals just how few relevant survey items were asked before 1990.
-Country coverage reached its peak in `r y_peak_year`, when surveys in `r y_peak_nn` countries included items on gender egalitarianism in the public sphere.
+Country coverage reached its peak in `r y_peak_year`, when respondents in `r y_peak_nn` countries were asked items about gender egalitarianism in the public sphere.
 In the next section, we describe how we are able to make use of all of this sparse and incomparable survey data to generate the PGE scores using a latent variable model.

### 2021-12-30 paper/dcpo_gender_roles.Rmd
add discussion of estimation; closes #31 @byngdeuk

@@
 
-We used the `DCPO` package for R [@Solt2020a] to estimate this model on the public gender egalitarianism source data described above.
+We estimated the model using the `DCPO` package for R [@Solt2020a], running four chains for 4,000 iterations each, with the first half discarded as warmup and the remainder thinned by eight to leave us with 1,000 samples.
+The $\hat{R}$ diagnostic had a maximum value of 1.02, indicating the model converged.
+
 The dispersion parameters of the survey items indicate that all of them load well on the latent variable (see online Appendix A).
-The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.^[
-To provide further confirmation of the unidimensionality of public gender egalitarianism, we estimated two separate indices of gender egalitarianism in politics and in the workplace.
-These indices correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.]
+The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.
+<!-- ^[ -->
+<!-- To provide further confirmation of the unidimensionality of public gender egalitarianism, we estimated two separate indices of gender egalitarianism in politics and in the workplace.
+These indices correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.] -->
 Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries and territories in the dataset.

### 2021-12-30 paper/dcpo_gender_roles.Rmd
drop footnote on uncertainty to free up space

@@
 General Social Survey whether they agreed or disagreed that "most men are better suited emotionally for politics than are most women."
-In every case, the correlations---estimated taking into account the uncertainty in the measures^[
-The uncertainty in the PGE score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the political leadership question, but failing to account for this uncertainty would overstate the correlation with the Pew item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S.
+In every case, the correlations---estimated taking into account the uncertainty in the measures---are in the expected direction and very strong.
+<!-- ^[ -->
+<!-- The uncertainty in the PGE score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the political leadership question, but failing to account for this uncertainty would overstate the correlation with the Pew item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S.
 GSS item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`.
-We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.]---are in the expected direction and very strong.
+-->
+<!-- We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.] -->
 

### 2021-12-31 paper/dcpo_gender_roles.Rmd
fix transitory issue (not in previous submission) with DCPO::summarize_dcpo_results()
work toward more accessible model description

@@
 
-<!-- Consider the most frequently asked item in the data we collected, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do." -->
-<!-- Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
--->
-<!-- That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
--->
+Consider the most frequently asked item in the data we collected, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do."
+Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
+That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
 
@@
 There has been a recent blossoming of scholarship developing latent variable models of public opinion based on cross-national survey data [see @Claassen2019; @Caughey2019; @McGann2019; @Kolczynska2020].
-To estimate public gender egalitarianism across countries and over time, we draw on the latest of these methods that is appropriate for data that is not only incomparable but also sparse, the Dynamic Comparative Public Opinion  (DCPO) model presented in @Solt2020c.^[
-@Solt2020c demonstrates that the DCPO model provides a better fit to survey data than the models put forward by @Claassen2019 or @Caughey2019.
-The @McGann2019 model depends on dense survey data unlike the sparse data on public gender egalitarianism described in the preceding section.
-@Kolczynska2020 is the very most recent of the five works and builds on each of the others, but the MRP approach developed in that piece is suitable not only when the available survey data are dense but also when ancillary data on population characteristics are available, so it is similarly inappropriate to this application.]
-
-The DCPO model is a population-level two-parameter ordinal logistic item response theory (IRT) model with country-specific item bias.
-That is, $\eta_{ktqr}$, the expected probability that a random person in country $k$ at time $t$ answers question $q$ with a response at least as positive as response $r$, is estimated as varying with the mean and standard deviation of the unbounded latent trait of public opinion, $\bar{\theta'}_{kt}$ and $\sigma_{kt}$; with the dispersion, $\alpha_{q}$, of the question and the difficulty, $\beta_{qr}$, of the question's response category; as well as with a term to capture how responses to particular questions may be biased in particular countries, $\delta_{kq}$: $\eta_{ktqr} = \textrm{logit}^{-1}(\frac{\bar{\theta'}_{kt} - (\beta_{qr} + \delta_{kq})}{\sqrt{\alpha_{q}^2 + (1.7*\sigma_{kt})^2}}) \label{eq:dcpo}$.
-A beta-binomial distribution is used to model the observed survey data given $\eta_{ktqr}$, random-walk priors are used to account for the dynamics in $\bar{\theta'}_{kt}$ and $\sigma_{kt}$, and weakly informative priors are placed on the other parameters.
-Finally, the logistic function is used to transform $\bar{\theta'}_{kt}$ to the unit interval and so give the bounded mean of latent public opinion, $\bar{\theta}_{kt}$, which is our parameter of interest here [see @Solt2020c, 3-8].
+To estimate public gender egalitarianism across countries and over time, we draw on the latest of these methods that is appropriate for data that is not only incomparable but also sparse, the Dynamic Comparative Public Opinion (DCPO) model presented in @Solt2020c.
+This model accounts for the incomparability of different survey questions in two ways.
+First, it adjusts for the _difficulty_ of each question's responses, that is, how much egalitarianism is indicated by a given response. 
+That different question responses evince more or less of our trait is most easily seen with regard to the ordinal responses to the same question: strongly agreeing with the statement "both the husband and wife should contribute to household income," exhibits more public gender egalitarianism than responding "agree," which in turn is more egalitarian than responding "disagree" or "strongly disagree."
+But this is also true across questions.
+For example, we might suppose that strongly disagreeing that "on the whole, men make better business executives than women do" expresses even more egalitarianism than strongly agreeing merely that both spouses should have paid employment.
+Second, the DCPO model accounts for each question's _dispersion_, its noisiness with regard to our latent trait.
+The lower a question's dispersion, the better that changes in responses to the question map onto changes in public gender egalitarianism.
+Together, the difficulty and dispersion parameters adjust the observed survey data to generate
+
+To address the sparsity of the data---the fact that there are gaps in the source data in the time series of each country, and even many observed country-years have only one or few observed items---DCPO uses simple local-level dynamic linear models (i.e., random-walk priors).
+That is, within each country, each year's value of public gender egalitarianism is a function of the previous year's estimate plus some noise.
+These dynamic models smooth the estimates of public gender egalitarianism over time and allows estimation even in years for which no survey data is available.
+For more detail on the DCPO model, see Appendix C and @Solt2020c [, 3-8].
 
@@
 
-sigma_res <- rstan::extract(dcpo_output, pars = "sigma") %>%
-        dplyr::first() %>%
-        purrr::array_branch(1) %>%
-        purrr::map(function(x) {
-          tibble::as_tibble(x) %>%
-          dplyr::mutate(tt = row_number()) %>%
-            dplyr::left_join(tcodes, by = "tt") %>%
-            tidyr::pivot_longer(cols = starts_with("V"),
-                                names_to = "kk",
-                                values_to = "pge_polarization") %>%
-            dplyr::mutate(year = if_else(tt == 1,
-                                         as.numeric(year),
-                                         min(year, na.rm = TRUE) + tt - 1),
-                          kk = str_replace(kk, "V", "") %>% as.numeric()) %>%
-            dplyr::left_join(kcodes, by = "kk") %>%
-            dplyr::left_join(ktcodes, by = "country") %>%
-            dplyr::filter(year >= first_yr & year <= last_yr) %>%
-            dplyr::arrange(kk, tt) %>%
-            dplyr::select(country, year, pge_polarization)
-        })
-
-pge <- map2(theta_res, sigma_res, function(theta, sigma) {
-  left_join(theta, sigma, by = c("country", "year"))
-})
+pge <- theta_res
 

### 2021-12-31 paper/pge_appendix.Rmd
work toward more accessible model description

@@
 The third and final category of excluded survey items includes respondents' views on various forms of women's domination by men, from whether wives should always adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.
-In each case, as the included questions are not _directly_ relevant to gender egalitarianism in the public sphere, we concluded that to ensure that the PGE scores tap only a single dimension of attitudes, we would exclude these others (see also Appendix C).
+In each case, as the included questions are not _directly_ relevant to gender egalitarianism in the public sphere, we concluded that to ensure that the PGE scores tap only a single dimension of attitudes, we would exclude these others (see also Appendix D).
 Usefully, this decision also allows, when the available survey data permits, future research to take up the estimation of dynamic comparative public opinion of those concepts separately and their relationships to public gender egalitarianism.
@@
 \pagebreak
-# Appendix C: Confirming the Unidimensionality of Public Gender Egalitarianism
+# Appendix C: The DCPO Model
+
+There has been a recent blossoming of scholarship developing latent variable models of public opinion based on cross-national survey data [see @Claassen2019; @Caughey2019; @McGann2019; @Kolczynska2020].
+To estimate public gender egalitarianism across countries and over time, we draw on the latest of these methods that is appropriate for data that is not only incomparable but also sparse, the Dynamic Comparative Public Opinion (DCPO) model presented in @Solt2020c.
+@Solt2020c demonstrates that the DCPO model provides a better fit to survey data than the models put forward by @Claassen2019 or @Caughey2019.
+The @McGann2019 model depends on dense survey data unlike the sparse data on public gender egalitarianism described in the preceding section.
+@Kolczynska2020 is the very most recent of the five works and builds on each of the others, but the MRP approach developed in that piece is suitable not only when the available survey data are dense but also when ancillary data on population characteristics are available, so it is similarly inappropriate to this application.
+
+The DCPO model is a population-level two-parameter ordinal logistic item response theory (IRT) model with country-specific item bias.
+
+That is, $\eta_{ktqr}$, the expected probability that a random person in country $k$ at time $t$ answers question $q$ with a response at least as positive as response $r$, is estimated as varying with the mean and standard deviation of the unbounded latent trait of public opinion, $\bar{\theta'}_{kt}$ and $\sigma_{kt}$; with the dispersion, $\alpha_{q}$, of the question and the difficulty, $\beta_{qr}$, of the question's response category; as well as with a term to capture how responses to particular questions may be biased in particular countries, $\delta_{kq}$: $\eta_{ktqr} = \textrm{logit}^{-1}(\frac{\bar{\theta'}_{kt} - (\beta_{qr} + \delta_{kq})}{\sqrt{\alpha_{q}^2 + (1.7*\sigma_{kt})^2}}) \label{eq:dcpo}$.
+
+A beta-binomial distribution is used to model the observed survey data given $\eta_{ktqr}$, random-walk priors are used to account for the dynamics in $\bar{\theta'}_{kt}$ and $\sigma_{kt}$, and weakly informative priors are placed on the other parameters.
+
+Finally, the logistic function is used to transform $\bar{\theta'}_{kt}$ to the unit interval and so give the bounded mean of latent public opinion, $\bar{\theta}_{kt}$, which is our parameter of interest here [see @Solt2020c, 3-8].
+
+\pagebreak
+# Appendix D: Confirming the Unidimensionality of Public Gender Egalitarianism
 

### 2022-01-02 paper/dcpo_gender_roles.Rmd
more on model (#28)

@@
 To estimate public gender egalitarianism across countries and over time, we draw on the latest of these methods that is appropriate for data that is not only incomparable but also sparse, the Dynamic Comparative Public Opinion (DCPO) model presented in @Solt2020c.
-This model accounts for the incomparability of different survey questions in two ways.
-First, it adjusts for the _difficulty_ of each question's responses, that is, how much egalitarianism is indicated by a given response. 
+The DCPO model is a population-level two-parameter ordinal logistic item response theory (IRT) model with country-specific item-bias terms.
+For a detailed description of the DCPO model, see Appendix C and @Solt2020c [, 3-8]; here we focus on how it deals with the principal issues raised by the source data, incomparability and sparsity.
+
+The DCPO model accounts for the incomparability of different survey questions with two parameters.
+First, it incorporates the _difficulty_ of each question's responses, that is, how much public gender egalitarianism is indicated by a given response. 
 That different question responses evince more or less of our trait is most easily seen with regard to the ordinal responses to the same question: strongly agreeing with the statement "both the husband and wife should contribute to household income," exhibits more public gender egalitarianism than responding "agree," which in turn is more egalitarian than responding "disagree" or "strongly disagree."
 But this is also true across questions.
-For example, we might suppose that strongly disagreeing that "on the whole, men make better business executives than women do" expresses even more egalitarianism than strongly agreeing merely that both spouses should have paid employment.
+For example, we might deduce that strongly disagreeing that "on the whole, men make better business executives than women do" expresses even more egalitarianism than strongly agreeing merely that both spouses should have paid employment.
 Second, the DCPO model accounts for each question's _dispersion_, its noisiness with regard to our latent trait.
 The lower a question's dispersion, the better that changes in responses to the question map onto changes in public gender egalitarianism.
-Together, the difficulty and dispersion parameters adjust the observed survey data to generate
-
-To address the sparsity of the data---the fact that there are gaps in the source data in the time series of each country, and even many observed country-years have only one or few observed items---DCPO uses simple local-level dynamic linear models (i.e., random-walk priors).
-That is, within each country, each year's value of public gender egalitarianism is a function of the previous year's estimate plus some noise.
-These dynamic models smooth the estimates of public gender egalitarianism over time and allows estimation even in years for which no survey data is available.
-For more detail on the DCPO model, see Appendix C and @Solt2020c [, 3-8].
+Together, the difficulty and dispersion parameters work to generate comparable estimates of the latent variable of public gender egalitarianism from the available but incomparable source data.
+
+To address the sparsity of the source data---the fact that there are gaps in the time series of each country, and even many observed country-years have only one or few observed items---DCPO uses simple local-level dynamic linear models, i.e., random-walk priors, for each country.
+That is, within each country, each year's value of public gender egalitarianism is modeled as the previous year's estimate plus some noise.
+These dynamic models smooth the estimates of public gender egalitarianism over time and allow estimation even in years for which little or no survey data is available, albeit at the expense of greater measurement uncertainty.
 

### 2022-01-02 paper/dcpo_gender_roles.Rmd
clean up

@@
 The lower a question's dispersion, the better that changes in responses to the question map onto changes in public gender egalitarianism.
-Together, the difficulty and dispersion parameters work to generate comparable estimates of the latent variable of public gender egalitarianism from the available but incomparable source data.
+Together, the model's difficulty and dispersion estimates work to generate comparable estimates of the latent variable of public gender egalitarianism from the available but incomparable source data.
 
 To address the sparsity of the source data---the fact that there are gaps in the time series of each country, and even many observed country-years have only one or few observed items---DCPO uses simple local-level dynamic linear models, i.e., random-walk priors, for each country.
-That is, within each country, each year's value of public gender egalitarianism is modeled as the previous year's estimate plus some noise.
+That is, within each country, each year's value of public gender egalitarianism is modeled as the previous year's estimate plus a random shock.
 These dynamic models smooth the estimates of public gender egalitarianism over time and allow estimation even in years for which little or no survey data is available, albeit at the expense of greater measurement uncertainty.
@@
 
-We estimated the model using the `DCPO` package for R [@Solt2020a], running four chains for 4,000 iterations each, with the first half discarded as warmup and the remainder thinned by eight to leave us with 1,000 samples.
+We estimated the model using the `DCPO` package for R [@Solt2020a], running four chains for 4,000 iterations each, discarding the first half as warmup, and thinning the remainder by eight, which left us with 1,000 samples.
 The $\hat{R}$ diagnostic had a maximum value of 1.02, indicating the model converged.

### 2022-01-02 paper/dcpo_gender_roles.Rmd
revise discussion of model; closes #28

@@
 The DCPO model is a population-level two-parameter ordinal logistic item response theory (IRT) model with country-specific item-bias terms.
-For a detailed description of the DCPO model, see Appendix C and @Solt2020c [, 3-8]; here we focus on how it deals with the principal issues raised by the source data, incomparability and sparsity.
+For a detailed description of the DCPO model, see online Appendix C and @Solt2020c [, 3-8]; here, we focus on how it deals with the principal issues raised by our source data, incomparability and sparsity.
 
@@
 First, it incorporates the _difficulty_ of each question's responses, that is, how much public gender egalitarianism is indicated by a given response. 
-That different question responses evince more or less of our trait is most easily seen with regard to the ordinal responses to the same question: strongly agreeing with the statement "both the husband and wife should contribute to household income," exhibits more public gender egalitarianism than responding "agree," which in turn is more egalitarian than responding "disagree" or "strongly disagree."
+That each response evinces more or less of our trait is most easily seen with regard to the ordinal responses to the same question: strongly agreeing with the statement "both the husband and wife should contribute to household income," exhibits more public gender egalitarianism than responding "agree," which in turn is more egalitarian than responding "disagree" or "strongly disagree."
 But this is also true across questions.
-For example, we might deduce that strongly disagreeing that "on the whole, men make better business executives than women do" expresses even more egalitarianism than strongly agreeing merely that both spouses should have paid employment.
+For example, strongly disagreeing that "on the whole, men make better business executives than women do" likely expresses even more egalitarianism than strongly agreeing merely that both spouses should have paying jobs.
 Second, the DCPO model accounts for each question's _dispersion_, its noisiness with regard to our latent trait.
@@
 <!-- To provide further confirmation of the unidimensionality of public gender egalitarianism, we estimated two separate indices of gender egalitarianism in politics and in the workplace.
-These indices correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.] -->
+These indices correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix D.] -->
 Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries and territories in the dataset.

### 2022-01-04 paper/pge_appendix.Rmd
use cache, put text to Appendix A before tables

--- 2021-09-11 paper/pge_appendix.Rmd
@@
 date: "`r format(Sys.time(), '%B %d, %Y')`"
+bibliography: dcpo_gender_roles.bib
+biblio-style: apsr
+linestretch: 1.1
 output: 
@@
 
-knitr::opts_chunk$set(cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE)
 
@@
 # Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism 
+Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found within the typical cross-national survey dataset.
+Lower values of dispersion ($\alpha$) indicate questions that better identify publics with more public gender egalitarianism from those with less.
+Items have one less difficulty score ($\beta$) than the number of response categories.
+Survey dataset codes correspond to those used in the `DCPOtools` R package; they appear in decreasing order of country-years contributed.
 
-```{r pge_items}
+```{r pge_items, cache=TRUE}
 load(here::here("data", "dcpo_input.rda"))
@@
   dcpo_input_raw_df %>% 
-  DCPOtools::with_min_yrs(2) %>% 
-  DCPOtools::with_min_cy(5) %>% 
+  with_min_yrs(2) %>% 
+  with_min_cy(5) %>% 
   group_by(country) %>% 
@@
   filter(!is.na(survey)) %>% 
-    group_by(item, survey) %>% 
-    summarize(n_cy = n()) %>% 
-    arrange(item, -n_cy) %>% 
   group_by(item) %>% 
-    mutate(total_cy = sum(n_cy),
-           all_surveys = paste0(survey, collapse = ", ")) %>% 
-    slice(1) %>% 
+  mutate(all_surveys = paste0(unique(survey), collapse = ", ")) %>% 
   ungroup() %>% 
-    left_join(pge_items %>% select(item, survey, question_text),
-              by = c("item", "survey")) %>% 
+  distinct(country, year, item, .keep_all = TRUE) %>% 
+  group_by(item) %>% 
+  mutate(n_cy = n()) %>% 
+  ungroup() %>%
+  distinct(item, n_cy, all_surveys) %>% 
+  left_join(public_items %>% select(item, question_text),
+            by = "item") %>% 
   left_join(alpha_results, by = "item") %>% 
   left_join(beta_results, by = "item") %>% 
-    arrange(-total_cy) %>% 
-    select(-survey, -n_cy)
+  arrange(-n_cy)
 ```
@@
         transmute(`Survey\nItem\nCode` = item,
-                  `Country-Years` = as.character(total_cy),
+                  `Country-Years` = as.character(n_cy),
                   `Question Text` = str_replace(question_text, "([^(]*)\\(.*", "\\1"),
@@
 \vspace{-.95in}
-Notes: Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found within the typical cross-national survey dataset.
-Lower values of dispersion ($\alpha$) indicate questions that better identify publics with more public gender egalitarianism from those with less.
-Items have one difficulty score ($\beta$) for each cutpoint; that is, one less than the number of response categories.
-Survey dataset codes correspond to those used in the `DCPOtools` R package; they appear in decreasing order of country-years contributed.
 
@@
 \pagebreak
-# Appendix C: Confirming the Unidimensionality of Public Gender Egalitarianism
+# Appendix C: The DCPO Model
+
+There has been a recent blossoming of scholarship developing latent variable models of public opinion based on cross-national survey data [see @Claassen2019; @Caughey2019; @McGann2019; @Kolczynska2020].
+To estimate public gender egalitarianism across countries and over time, we draw on the latest of these methods that is appropriate for data that is not only incomparable but also sparse, the Dynamic Comparative Public Opinion (DCPO) model presented in @Solt2020c.^[
+@Solt2020c demonstrates that the DCPO model provides a better fit to survey data than the models put forward by @Claassen2019 or @Caughey2019.
+The @McGann2019 model depends on dense survey data unlike the sparse data on public gender egalitarianism described in the preceding section.
+@Kolczynska2020 is the very most recent of the five works and builds on each of the others, but the MRP approach developed in that piece is suitable not only when the available survey data are dense but also when ancillary data on population characteristics are available, so it is similarly inappropriate to this application.]
+The DCPO model is a population-level two-parameter ordinal logistic item response theory (IRT) model with country-specific item-bias terms.
+
+DCPO models the total number of survey responses expressing at least as much public gender egalitarianism as response category $r$ to each question $q$ in country $k$ at time $t$, $y_{ktqr}$, out of the total number of respondents surveyed, $n_{ktqr}$, using the beta-binomial distribution:
+
+\begin{equation}
+a_{ktqr} = \phi\eta_{ktqr} \label{eq:bb_a}
+\end{equation}
+\begin{equation}
+b_{ktqr} = \phi(1 - \eta_{ktqr}) \label{eq:bb_b}
+\end{equation}
+\begin{equation}
+y_{ktqr} \sim \textrm{BetaBinomial}(n_{ktqr}, a_{ktqr}, b_{ktqr}) \label{eq:betabinomial}
+\end{equation}
+
+where $\phi$ represents an overall dispersion parameter to account for additional sources of survey error beyond sampling error and $\eta_{ktqr}$ is the expected probability that a random person in country $k$ at time $t$ answers question $q$ with a response at least as positive as response $r$.^[
+The ordinal responses to question $q$ are coded to range from 1 (expressing the least public gender egalitarianism) to $R$ (expressing the most public gender egalitarianism), and $r$ takes on all values greater than 1 and less than or equal to $R$.]
+
+This expected probability, $\eta_{ktqr}$, is in turn estimated as follows:
+
+\begin{equation}
+\eta_{ktqr} = \textrm{logit}^{-1}(\frac{\bar{\theta'}_{kt} - (\beta_{qr} + \delta_{kq})}{\sqrt{\alpha_{q}^2 + (1.7*\sigma_{kt})^2}}) \label{eq:dcpo}
+\end{equation}
+
+In this equation, $\beta_{qr}$ represents the difficulty of response $r$ to question $q$, that is, the degree of public gender egalitarianism the response expresses.
+The $\delta_{kq}$ term represents country-specific item bias: the extent to which all responses to a particular question $q$ may be more (or less) difficult in a given country $k$ due to translation issues, cultural differences in response styles, or other idiosyncrasies that render the same survey item not equivalent across countries.^[
+Estimating $\delta_{kq}$ requires repeated administrations of question $q$ in country $k$, so
+when responses to question $q$ are observed in country $k$ in only a single year, the DCPO model sets $\delta_{kq}$ to zero by assumption, increasing the error of the model by any country-item bias that is present.
+Questions that are asked repeatedly over time in only a single country pose no risk of country-specific item bias, so $\delta_{kq}$ in such cases are also set to zero.]
+The dispersion of question $q$, its noisiness in relation to our latent variable, is $\alpha_{q}$.
+The mean and standard deviation of the unbounded latent trait of public gender egalitarianism are $\bar{\theta'}_{kt}$ and $\sigma_{kt}$, respectively.
+
+Random-walk priors are used to account for the dynamics in $\bar{\theta'}_{kt}$ and $\sigma_{kt}$, and weakly informative priors are placed on the other parameters.^[
+The dispersion parameters $\alpha_{q}$ are drawn from standard half-normal prior distributions, that is, the positive half of N(0, 1).
+The first difficulty parameters for each question, $\beta_{q1}$, are drawn from standard normal prior distributions, and the differences between $\beta$s for each $r$ for the same question $q$ are drawn from standard half-normal prior distributions.
+The item-bias parameters $\delta_{kq}$ receive normally-distributed hierarchical priors with mean 0 and standard deviations drawn from standard half-normal prior distributions.
+The initial value of the mean unbounded latent trait for each country, $\bar{\theta'}_{k1}$, is assigned a standard normal prior, as are the transition variances $\sigma_{\bar{\theta'}}^2$ and $\sigma_{\sigma}^2$; the initial value of the standard deviation of the unbounded latent trait for each country, $\sigma_{k1}$, is drawn from a standard lognormal prior distribution.
+The overall dispersion, $\phi$, receives a somewhat more informative prior drawn from a gamma(4, 0.1) distribution that yields values that are well scaled for that parameter.]
+The dispersion parameters $\alpha_q$ are constrained to be positive and all survey responses are coded with high values indicating more public gender egalitarianism to fix direction.
+The difficulty $\beta$ of "disagree" (on the four-point, "strongly agree" to "strongly disagree" scale) to the statement "On the whole, men make better political leaders than women do" is set to 1 to identify location, and for each question $q$ the difficulties for increasing response categories $r$ are constrained to be increasing.
+The sum of $\delta_{kq}$ across all countries $k$ is set to zero for each question $q$:
+
+\begin{equation}
+\sum_{k = 1}^K \delta_{kq} = 0
+\end{equation}
+
+Finally, the logistic function is used to transform $\bar{\theta'}_{kt}$ to the unit interval and so give the bounded mean of latent public gender egalitarianism, $\bar{\theta}_{kt}$, which is our parameter of interest here [see @Solt2020c, 3-8].
+
+\pagebreak
+# Appendix D: Confirming the Unidimensionality of Public Gender Egalitarianism
 
@@
 
-```{r create_pwe_indices}
+```{r create_pwe_indices, cache=TRUE}
 dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
@@
 
-```{r theta_res_political}
+```{r theta_res_political, cache=TRUE}
 load(here::here("data", "dcpo_input_political.rda"))
@@
 
-```{r theta_res_workplace}
+```{r theta_res_workplace, cache=TRUE}
 load(here::here("data", "dcpo_input_workplace.rda"))
@@
 
-```{r pge_pwe_corr}
+```{r pge_pwe_corr, cache=TRUE}
 load(here::here("data", "pge.rda"))
@@
 ```
+
+\pagebreak
+# References  {-}

### 2022-01-04 paper/dcpo_gender_roles.Rmd
fuss with text

@@
 Country coverage reached its peak in `r y_peak_year`, when respondents in `r y_peak_nn` countries were asked items about gender egalitarianism in the public sphere.
-In the next section, we describe how we are able to make use of all of this sparse and incomparable survey data to generate the PGE scores using a latent variable model.
+In the next section, we describe how we are able to make use of all of this sparse and incomparable survey data to generate complete, comparable time-series PGE scores using a latent variable model.
 
@@
 First, it incorporates the _difficulty_ of each question's responses, that is, how much public gender egalitarianism is indicated by a given response. 
-That each response evinces more or less of our trait is most easily seen with regard to the ordinal responses to the same question: strongly agreeing with the statement "both the husband and wife should contribute to household income," exhibits more public gender egalitarianism than responding "agree," which in turn is more egalitarian than responding "disagree" or "strongly disagree."
+That each response evinces more or less of our latent trait is most easily seen with regard to the ordinal responses to the same question: strongly agreeing with the statement "both the husband and wife should contribute to household income," exhibits more public gender egalitarianism than responding "agree," which in turn is more egalitarian than responding "disagree," which is a more egalitarian response than "strongly disagree."
 But this is also true across questions.

### 2022-01-04 paper/pge_appendix.Rmd
add plot of observations by country-year for #26; consider moving to text?

@@
 \vspace{-.95in}
+
+\pagebreak
+
+```{r obs_by_cy, fig.height = 9, fig.width = 6.5, fig.cap = "Source Data Observations by Country and Year \\label{obs_by_cy}"}
+dcpo_input_raw_poliwork1 %>% 
+  mutate(country = str_replace(country, "’", "'")) %>% 
+    distinct(country, year, item, cc_rank) %>% 
+    group_by(country, year) %>% 
+    summarize(n = n(),
+              cc_rank = cc_rank) %>% 
+    ungroup() %>% 
+    distinct() %>% 
+    ggplot(aes(x = year, 
+               y = forcats::fct_reorder(country, cc_rank),
+               fill = n)) + 
+    geom_tile() +
+    scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
+                      n.breaks = 7,
+                      show.limits = TRUE,
+                      right = FALSE,
+                      name = "Observations") +
+    labs(x = NULL, y = NULL) +
+    scale_x_continuous(breaks=seq(1972, 2020, 4)) +
+    theme(legend.justification=c(0, 0), 
+          legend.position=c(0.01, 0.01),
+          axis.text.y  = element_text(size = 7)) #+
+    # ggtitle("Source Data Observations by Country and Year")
+```
 

### 2022-01-05 paper/pge_appendix.Rmd
add figure on joint obs to App A; add more text to App A

--- 2022-01-04 paper/pge_appendix.Rmd
@@
 \pagebreak
-# Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism 
-Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found within the typical cross-national survey dataset.
-Lower values of dispersion ($\alpha$) indicate questions that better identify publics with more public gender egalitarianism from those with less.
-Items have one less difficulty score ($\beta$) than the number of response categories.
-Survey dataset codes correspond to those used in the `DCPOtools` R package; they appear in decreasing order of country-years contributed.
-
-```{r pge_items, cache=TRUE}
-load(here::here("data", "dcpo_input.rda"))
-load(here::here("data", "dcpo_output.rda"))
-
+# Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism and Their Distribution
+```{r egr_summary_stats, cache = TRUE, cache.extra = tools::md5sum(here::here("data-raw", "dcpo_input_raw_public.csv"))}
 dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),
@@
   filter(political==1|workplace==1)
+
+surveys_egr <- read_csv(here::here("data-raw", "surveys_egr_classification.csv"),
+                        col_types = "ccccnnn")
+
+n_surveys <- surveys_egr %>% 
+  filter(agreed == 1) %>%
+  distinct(survey) %>% 
+  nrow()
+
+n_items <- dcpo_input_raw_poliwork1 %>%
+  distinct(item) %>% 
+  nrow()
+
+n_countries <- dcpo_input_raw_poliwork1 %>%
+  distinct(country) %>% 
+  nrow()
+
+n_cy <- dcpo_input_raw_poliwork1 %>%
+  distinct(country, year) %>% 
+  nrow() %>% 
+  scales::comma()
+
+n_years <- as.integer(summary(dcpo_input_raw_poliwork1$year)[6]-summary(dcpo_input_raw_poliwork1$year)[1])
+
+spanned_cy <- dcpo_input_raw_poliwork1 %>% 
+  group_by(country) %>% 
+  summarize(years = max(year) - min(year) + 1) %>% 
+  summarize(n = sum(years)) %>% 
+  pull(n) %>% 
+  scales::comma()
+
+total_cy <- {n_countries * n_years} %>% 
+  scales::comma()
+
+year_range <- paste("from",
+                    summary(dcpo_input_raw_poliwork1$year)[1],
+                    "to",
+                    summary(dcpo_input_raw_poliwork1$year)[6])
+
+n_cyi <- dcpo_input_raw_poliwork1 %>% 
+  distinct(country, year, item) %>% 
+  nrow() %>% 
+  scales::comma()
+
+back_to_numeric <- function(string_number) {
+  string_number %>% 
+    str_replace(",", "") %>% 
+    as.numeric()
+}
+```
+National and cross-national surveys have often included questions tapping attitudes toward equality for women and men in the public sphere over the past half-century, but the resulting data are both sparse, that is, unavailable for many countries and years, and incomparable, generated by many different survey items.
+In all, we identified `r n_items` such survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.
+These items are listed in the table below, along with the dispersion ($\alpha$) and difficulty ($\beta$) scores estimated for each from the DCPO model.
+Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found within the typical cross-national survey dataset.
+Lower values of dispersion indicate questions that better identify publics with more public gender egalitarianism from those with less.
+Items have one less difficulty score than the number of response categories.
+Survey dataset codes correspond to those used in the `DCPOtools` R package; they appear in decreasing order of country-years contributed.
+
+Together, the survey items in the source data were asked in `r n_countries` different countries in at least two time points over `r n_years` years, `r year_range`, yielding a total of `r n_cyi` country-year-item observations.
+The number of items observed in the source data for each country-year is plotted in Figure \ref{obs_by_cy} below.
+The PGE scores of country-years with more observed items are likely to be estimated more precisely.
+The estimates for country-years with fewer (or no) observed items rely more heavily (or entirely) on the random-walk prior and are therefore less certain.
+Figure \ref{obs_by_item2} displays the distribution of the source data in yet another way, showing the (binned) number of country-years in which both members of each pair of items is observed.
+
+```{r pge_items, cache=TRUE}
+load(here::here("data", "dcpo_input.rda"))
+load(here::here("data", "dcpo_output.rda"))
 
@@
 ```
-\vspace{-.95in}
+
+\pagebreak
+```{r obs_by_cy, fig.height = 9, fig.width = 6.5, fig.cap = "Source Data Observations by Country and Year \\label{obs_by_cy}"}
+dcpo_input_raw_poliwork1 %>% 
+  mutate(country = str_replace(country, "’", "'")) %>% 
+    distinct(country, year, item, cc_rank) %>% 
+    group_by(country, year) %>% 
+    summarize(n = n(),
+              cc_rank = cc_rank) %>% 
+    ungroup() %>% 
+    distinct() %>% 
+    ggplot(aes(x = year, 
+               y = forcats::fct_reorder(country, cc_rank),
+               fill = n)) + 
+    geom_tile() +
+    scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
+                      n.breaks = 7,
+                      show.limits = TRUE,
+                      right = FALSE,
+                      name = "Observations") +
+    labs(x = NULL, y = NULL) +
+    scale_x_continuous(breaks=seq(1972, 2020, 4)) +
+    theme(legend.justification=c(0, 0), 
+          legend.position=c(0.01, 0.01),
+          axis.text.y  = element_text(size = 7)) #+
+    # ggtitle("Source Data Observations by Country and Year")
+```
+
+```{r obs_by_item2, fig.height = 9, fig.width = 6.5, fig.cap = "Joint Observations in the Source Data for Each Pair of Items \\label{obs_by_item2}"}
+items_by_obs <- dcpo_input_raw_poliwork1 %>%
+    distinct(country, year, item) %>%
+    count(item, name = "n_obs") %>%
+    arrange(desc(n_obs))
+
+dcpo_input_raw_poliwork1 %>% 
+    group_by(country, year, item) %>%
+    mutate(n = sum(n)) %>% 
+    distinct(country, year, item, n) %>% 
+    pivot_wider(names_from = "item", values_from = "n") %>% 
+    ungroup() %>% 
+    select(-country, -year) %>% 
+    psych::pairwiseCount() %>% 
+    as.data.frame() %>%
+    rownames_to_column(var = "item") %>% 
+    left_join(items_by_obs) %>%  
+    arrange(-n_obs) %>% 
+    select(item, any_of(items_by_obs %>% pull(item)), n_obs) %>% 
+    pivot_longer(cols = matches("\\d.?$"), names_to = "var2", values_to = "count") %>%
+    filter(count > 0) %>% 
+    mutate(item = forcats::fct_reorder(item, n_obs),
+           var2 = forcats::fct_relevel(var2, rev(levels(item)))) %>% 
+    ggplot(aes(x = var2, 
+               y = item,
+               fill = count)) + 
+    geom_tile() +
+    scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
+                      breaks = c(0, 1, 10, 20, 30, 50, 100),
+                      show.limits = TRUE,
+                      right = FALSE,
+                      trans = "log10",
+                      name = "Joint\nObservations") +
+    labs(x = NULL, y = NULL) +
+    theme(axis.text.x  = element_text(angle = 90, vjust = .5))
+
+```
 

### 2022-01-05 paper/pge_appendix.Rmd
move y-axis countries in Fig1 to right

@@
   scale_x_continuous(breaks=seq(1972, 2020, 4)) +
+  scale_y_discrete(position = "right") +
   theme(legend.justification=c(0, 0), 
         legend.position=c(0.01, 0.01),
-          axis.text.y  = element_text(size = 7)) #+
-    # ggtitle("Source Data Observations by Country and Year")
+        axis.text.y  = element_text(size = 7)) 
 ```
@@
   theme(axis.text.x  = element_text(angle = 90, vjust = .5))
-
 ```

### 2022-02-15 paper/dcpo_gender_roles.Rmd
fix for n_surveys
update

@@
     with_min_cy(5) %>% 
+    filter(year >= 1972) %>% 
     group_by(country) %>% 
@@
 n_surveys <- surveys_egr %>% 
+  filter(agreed == 1) %>%
   distinct(survey) %>% 
@@
 }
+
+covered_share_of_spanned <- {back_to_numeric(n_cy)/back_to_numeric(spanned_cy) * 100}
 ```
@@
 Compared to this complete set of country-year-items, the available data can be seen to be very, very sparse.
-From a more optimistic standpoint, we note there there are `r n_cy` country-years in which we have at least _some_ information about the public gender egalitarianism of the population, that is, some `r {back_to_numeric(n_cy)/back_to_numeric(spanned_cy) * 100} %>% round()`% of the `r spanned_cy` country-years spanned by the data we collected.
+From a more optimistic standpoint, we note there there are `r n_cy` country-years in which we have at least _some_ information about the public gender egalitarianism of the population, that is, some `r round(covered_share_of_spanned)`% of the `r spanned_cy` country-years spanned by the data we collected.
 But there can be no denying Claveria's [-@Claveria2014] observation that the many different survey items employed renders these data incomparable and difficult to use together.
@@
 
-theta_results %>%
+alpha_results <- DCPO::summarize_dcpo_results(dcpo_input,
+                                        dcpo_output,
+                                        "alpha")
+
+c_rawdata <- dcpo_input$data %>% 
+  filter(country %in% countries) %>%
+  mutate(mean = y_r/n_r,
+         country = str_replace(country, "United States", "U.S.") %>% 
+           factor(levels = countries2)) %>% 
+  left_join(alpha_results %>% select(question, alpha_mean = mean), by = "question")
+
+c_res <- theta_results %>% 
   filter(country %in% countries) %>%
   mutate(country = str_replace(country, "United States", "U.S.") %>% 
-           factor(levels = countries2)) %>% 
-  ggplot(aes(x = year, y = mean)) +
-  geom_ribbon(aes(ymin = `10%`, ymax = `90%`, linetype=NA), alpha = .25) +
-  geom_line() +
+           factor(levels = countries2))
+
+ggplot(data = c_rawdata, aes(x = year, y = mean)) +
+  geom_line(aes(color = item, alpha = 1/alpha_mean)) +
+  geom_point(aes(color = item, alpha = 1/alpha_mean)) +
   theme_bw() +
-  theme(legend.position="none") +
+  theme(legend.position = "none") +
   coord_cartesian(xlim = c(1980, 2020), ylim = c(0, 1)) +
   labs(x = NULL, y = "PGE Scores") +
+  geom_ribbon(data = c_res, aes(ymin = `10%`, ymax = `90%`, linetype=NA), alpha = .25) +
+  geom_line(data = c_res) +
   facet_wrap(~country, nrow = 2) +

### 2022-02-15 paper/pge_appendix.Rmd
prefix page, figure, and table numbers with A
use dev version of DCPO
update

@@
 
+\renewcommand{\thepage}{A\arabic{page}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+
 ```{r setup, include=FALSE}
@@
 # remotes::install_github("fsolt/DCPOtools")
+
+# If development version of `DCPO` is not yet installed:
+# remotes::install_github("fsolt/DCPO")
 
@@
 # Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism and Their Distribution
-```{r egr_summary_stats, cache = TRUE, cache.extra = tools::md5sum(here::here("data-raw", "dcpo_input_raw_public.csv"))}
+```{r egr_summary_stats, cache = FALSE, cache.extra = tools::md5sum(here::here("data-raw", "dcpo_input_raw_public.csv"))}
 dcpo_input_raw_public <- read_csv(here::here("data", "dcpo_input_raw_public.csv"),

### 2022-02-18 paper/pge_appendix.Rmd
duplicate x-axis on top of cy coverage plot

@@
   geom_tile() +
-  scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
-                    n.breaks = 7,
+  scale_fill_stepsn(colors = rev(hcl.colors(6, "inferno")),
+                    n.breaks = 6,
                     show.limits = TRUE,
@@
   labs(x = NULL, y = NULL) +
-  scale_x_continuous(breaks=seq(1972, 2020, 4)) +
+  scale_x_continuous(breaks=seq(1972, 2020, 4),
+                     sec.axis = dup_axis()) +
   scale_y_discrete(position = "right") +

### 2022-03-21 paper/response_memo.Rmd
add response_memo; comments on #25 and #28

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: xelatex
    template: ../svm-latex-ms2.tex
title: |
    | Public Gender Egalitarianism: A Dataset of Dynamic Comparative
  Public Opinion Toward Egalitarian Gender Roles in the Public Sphere
    | Memo to Reviewers
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: single
bibliography: dcpo_gender_roles.bib
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300)

# If you haven't install `DCPOtools`
# remotes::install_github("fsolt/DCPOtools")

if (!require(pacman)) install.packages("pacman")
library(pacman)
library(patchwork)
library(rsdmx)

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  broom, tidyverse, janitor, # data wrangling
  dotwhisker # visualization
)

# Functions preload
set.seed(313)

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}

```

Thank you for your helpful comments, as well as your general enthusiasm for this piece.
We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the text:

1. **Introduction** R2 asked if we were "only using cross-national surveys or whether you also incorporate single-country surveys."
We clarified that we are drawing on both cross-national and single-country surveys at the top of page 2.
We also revised the sentence on peak country coverage (at the bottom of p3) that prompted R2's question in an effort to avoid any confusion.

1. **Estimating Public Gender Egalitarianism** R2 suggested that our description of the model could be made more accessible given the broad audience of the _BJPS_ and the work's potential for use in the classroom.
We agree entirely.
We revised these paragraphs carefully for readability, shifting much of the technical discussion to an online appendix and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.

Thank you once more for the opportunity to make revisions.
We think the paper is much stronger as a result of your comments; in fact, with your assistance, we think it lives up to R3's assessment as an "exemplary demonstration" of the role of replication in scientific progress.
We hope you all agree.

# References

<div id="refs"></div>

### 2022-03-21 paper/response_memo.Rmd
address #29
address #31

@@
 
+1. **Examining the Source Data on Public Gender Egalitarianism** R1 noted three spots in the first few pages where our language was respectively unclear, mistaken, and repeated.
+We corrected each of these infelicities with gratitude.
+
 1.
@@
 We agree entirely.
-We revised these paragraphs carefully for readability, shifting much of the technical discussion to an online appendix and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.
+We revised these paragraphs carefully for readability, shifting much of the technical discussion to Appendix C and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.
+
+1.
+**Estimating Public Gender Egalitarianism** R1 requested "more description about how the estimates were obtained," specifically details about iterations, chains, warmup, thinning, and convergence.
+We added a short paragraph with this information at p5.
 
 Thank you once more for the opportunity to make revisions.
-We think the paper is much stronger as a result of your comments; in fact, with your assistance, we think it lives up to R3's assessment as an "exemplary demonstration" of the role of replication in scientific progress.
-We hope you all agree.
+We think the paper is much stronger as a result of your comments, and we hope you agree.
 

### 2022-03-23 paper/response_memo.Rmd
respond to #26

@@
 output: 
-  pdf_document:
-    citation_package: natbib
-    keep_tex: true
-    fig_caption: true
+  bookdown::pdf_document2:
+    fig_caption: yes
+    keep_tex: yes
+    toc: no
+    number_sections: yes
     latex_engine: xelatex
-    template: ../svm-latex-ms2.tex
+
 title: |
-    | Public Gender Egalitarianism: A Dataset of Dynamic Comparative
-  Public Opinion Toward Egalitarian Gender Roles in the Public Sphere
-    | Memo to Reviewers
+  | Public Gender Egalitarianism:
+  | A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere
+subtitle: "Memo to Reviewers"
+
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 1.
-**Estimating Public Gender Egalitarianism** R1 requested "more description about how the estimates were obtained," specifically details about iterations, chains, warmup, thinning, and convergence.
+**Estimating Public Gender Egalitarianism** Noting that the source data covers only "roughly 45 percent of the possible sample of country-years" and that it is decidedly unbalanced, R1 raised the question of whether this means that PGE estimates for country-years without source data were unavailable: if so, PGE would be limited in cross-national time-series applications due to listwise deletion and the complete series depicted in Figure 3 would be misleading.
+This is an important question.
+The DCPO model introduced in @Solt2020c that we employ here---as well as the models presented in @Claassen2019 that R1 referenced in making this point---was specifically designed for when survey data on the topic of interest is not available for all years in all countries, a problem referred to as sparsity.
+So we do actually have PGE estimates for country-years for which there is no source survey data available---and, more generally, the $k$-fold cross-validations presented in @Solt2020c [, 10-12] show that estimates generated by the DCPO model in such circumstances are very good.
+We have added a paragraph specifically addressing how this model deals with sparsity to ensure this point is clear to readers at p4-5.
+
+1. **Estimating Public Gender Egalitarianism** R1 requested "more description about how the estimates were obtained," specifically details about iterations, chains, warmup, thinning, and convergence.
 We added a short paragraph with this information at p5.
+
+We also took advantage of the opportunity to add more source data...
 

### 2022-03-23 paper/response_memo.Rmd
address #30; clean up

@@
 We agree entirely.
-We revised these paragraphs carefully for readability, shifting much of the technical discussion to Appendix C and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.
+We revised these paragraphs (now at pp4-5) carefully for readability, shifting much of the technical discussion to Appendix C and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.
 
 1.
-**Estimating Public Gender Egalitarianism** Noting that the source data covers only "roughly 45 percent of the possible sample of country-years" and that it is decidedly unbalanced, R1 raised the question of whether this means that PGE estimates for country-years without source data were unavailable: if so, PGE would be limited in cross-national time-series applications due to listwise deletion and the complete series depicted in Figure 3 would be misleading.
+**Estimating Public Gender Egalitarianism** R1 noted that the source data covers only "roughly 45 percent of the possible sample of country-years" and that it is decidedly unbalanced, and raised the question of whether this means that PGE estimates for country-years without source data were unavailable: if so, PGE would be limited in cross-national time-series applications due to listwise deletion and the complete series depicted in Figure 3 would be misleading.
 This is an important question.
 The DCPO model introduced in @Solt2020c that we employ here---as well as the models presented in @Claassen2019 that R1 referenced in making this point---was specifically designed for when survey data on the topic of interest is not available for all years in all countries, a problem referred to as sparsity.
-So we do actually have PGE estimates for country-years for which there is no source survey data available---and, more generally, the $k$-fold cross-validations presented in @Solt2020c [, 10-12] show that estimates generated by the DCPO model in such circumstances are very good.
-We have added a paragraph specifically addressing how this model deals with sparsity to ensure this point is clear to readers at p4-5.
+So we actually do have PGE estimates for country-years for which there is no source survey data available---and, more generally, the $k$-fold cross-validations presented in @Solt2020c [, 10-12] show that estimates generated by the DCPO model in such circumstances are very good.
+We have added a paragraph specifically addressing how this model deals with sparsity to ensure this point is clear to readers at pp4-5.
+
+1.
+**Estimating Public Gender Egalitarianism** R1 recommended including a discussion of difficulty and dispersion in the main text, and also suggested representing the estimates of these parameters in the text as in @Gandhi2020 [, 1552].
+We now discuss difficulty and dispersion at p4 to explain how the DCPO model we adopt addresses the incomparability of the available survey data.
+Regrettably, we were not able to able to carve out space in the text to represent and discuss the estimates of these parameters (understandable, we hope, given that we have some four times the number of indicators that @Gandhi2020 employed).
+We present these parameters in Appendix A.
 

### 2022-03-23 paper/response_memo.Rmd
clean up

@@
 We clarified that we are drawing on both cross-national and single-country surveys at the top of page 2.
-We also revised the sentence on peak country coverage (at the bottom of p3) that prompted R2's question in an effort to avoid any confusion.
+To try to avoid any confusion, we also revised the sentence on peak country coverage (at the bottom of p3) that prompted R2's question.
 
@@
 We agree entirely.
-We revised these paragraphs (now at pp4-5) carefully for readability, shifting much of the technical discussion to Appendix C and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.
+We revised these paragraphs (now at pages 4-5) carefully for readability, shifting much of the technical discussion to Appendix C and instead elaborating on how the model's terms address the twin limitations of the source survey data that we raise in the paper's previous section, their incomparability and their sparsity.
 
@@
 So we actually do have PGE estimates for country-years for which there is no source survey data available---and, more generally, the $k$-fold cross-validations presented in @Solt2020c [, 10-12] show that estimates generated by the DCPO model in such circumstances are very good.
-We have added a paragraph specifically addressing how this model deals with sparsity to ensure this point is clear to readers at pp4-5.
+We have added a paragraph specifically addressing how this model deals with sparsity to ensure this point is clear to readers at pages 4-5.
 
@@
 **Estimating Public Gender Egalitarianism** R1 recommended including a discussion of difficulty and dispersion in the main text, and also suggested representing the estimates of these parameters in the text as in @Gandhi2020 [, 1552].
-We now discuss difficulty and dispersion at p4 to explain how the DCPO model we adopt addresses the incomparability of the available survey data.
+We now discuss difficulty and dispersion at page 4 to explain how the DCPO model we adopt addresses the incomparability of the available survey data.
 Regrettably, we were not able to able to carve out space in the text to represent and discuss the estimates of these parameters (understandable, we hope, given that we have some four times the number of indicators that @Gandhi2020 employed).

### 2022-03-23 paper/dcpo_gender_roles.Rmd
update
clean up

@@
 
-Consider the most frequently asked item in the data we collected, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do."
+Consider the most frequently asked item in these data, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do."
 Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
-That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.
+That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse the available public opinion data is on this topic.
 
@@
 
-To address the sparsity of the source data---the fact that there are gaps in the time series of each country, and even many observed country-years have only one or few observed items---DCPO uses simple local-level dynamic linear models, i.e., random-walk priors, for each country.
+To address the sparsity of the source data---the fact that there are gaps in the time series of each country, and even many observed country-years have only one or few observed items---DCPO uses local-level dynamic linear models, i.e., random-walk priors, for each country.
 That is, within each country, each year's value of public gender egalitarianism is modeled as the previous year's estimate plus a random shock.
@@
 ```{r dcpo_results, cache=TRUE}
-load(here::here("data", "poliwork_polileader4_2_4k_06-23.rda"))
+load(here::here("data", "poliwork_polileader4_2_4k_02_16.rda"))
 
@@
 
-We estimated the model using the `DCPO` package for R [@Solt2020a], running four chains for 4,000 iterations each, discarding the first half as warmup, and thinning the remainder by eight, which left us with 1,000 samples.
+We estimated the model on our source data using the `DCPO` package for R [@Solt2020a], running four chains for 4,000 iterations each, discarding the first half as warmup, and thinning the remainder by eight, which left us with 1,000 samples.
 The $\hat{R}$ diagnostic had a maximum value of 1.02, indicating the model converged.
@@
 
-ggplot(data = c_rawdata, aes(x = year, y = mean)) +
-  geom_line(aes(color = item, alpha = 1/alpha_mean)) +
-  geom_point(aes(color = item, alpha = 1/alpha_mean)) +
+# ggplot(data = c_rawdata, aes(x = year, y = mean)) +
+#   geom_line(aes(color = item, alpha = 1/alpha_mean)) +
+#   geom_point(aes(color = item, alpha = 1/alpha_mean)) +
+ggplot(data = c_res, aes(x = year, y = mean)) +
   theme_bw() +
@@
 Like @Caughey2019 [684-685], we provide evidence of our measure's validity with convergent validation and construct validation.
-Figure&nbsp;\ref{conv_plot} displays our demonstrations of convergent validation.
 Convergent validation refers to showing that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
-Here, we compare PGE scores to responses to individual survey items that were included in the source data, that is, we provide an 'internal' validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
-In the left panel, we examine the four-point question on political leaders mentioned above, the most common item in the source data across all country-years.
-Then, in the center panel, we look at the question that provides the most data-rich cross-section, which asked whether respondents felt "men generally make better political leaders than women" and was included in Pew Global's Spring 2007 survey.
-Finally, in the right panel, to evaluate how well the PGE scores capture change over time, we focus on the item with the largest number of observations for a single country, which asked respondents to the U.S.
+Here, we compare PGE scores to responses to individual source-data survey items that were used to generate our estimates, that is, we provide an 'internal' validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
+In the left panel of Figure&nbsp;\ref{conv_plot}, we examine the four-point question on political leaders mentioned above, the most common item in the source data across all country-years.
+Then, in the center panel, we look at the question that provides the most data-rich cross-section in the source data, which asked whether respondents felt "men generally make better political leaders than women" and was included in Pew Global's Spring 2007 survey.
+Finally, in the right panel, to evaluate how well the PGE scores capture change over time, we focus on the item with the largest number of observations for a single country in the source data, which asked respondents to the U.S.
 General Social Survey whether they agreed or disagreed that "most men are better suited emotionally for politics than are most women."
@@
 We continue, then, to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
-In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from a related category of gender egalitarianism, namely questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
+In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items not included in our source data but tapping a related category of gender egalitarianism, namely questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
 Assuming that attitudes that women should prioritize housework and childcare over paid employment and politics---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE scores.

### 2022-03-23 paper/pge_appendix.Rmd
add para on overlap; drop obs_by_item2 plot

--- 2022-02-15 paper/pge_appendix.Rmd
@@
 The estimates for country-years with fewer (or no) observed items rely more heavily (or entirely) on the random-walk prior and are therefore less certain.
-Figure \ref{obs_by_item2} displays the distribution of the source data in yet another way, showing the (binned) number of country-years in which both members of each pair of items is observed.
+
+Overlap among items have not been a concern in the literature on generating latent-variable estimates of public opinion across countries and over time from sparse data, largely because the dynamic aspect of the models employed, that is, the random-walk prior, works to tie together items that do not overlap [see @Claassen2019; @Caughey2019; @Solt2020].
+Nevertheless, the most commonly observed item in the PGE source data, `polileader4`, effectively serves as the bridge between the other items: it has overlapping country-year observations with 39 of the other 50 items (which together cover 91% of the observed country-years), and only a single item (`politics4a`, which covers 22 country-years) had no observations within a year of a `polileader4` observation.
 
@@
                                  note = "") %>% 
-        kableExtra::column_spec(c(3, 6), width = "10em") %>% 
+    kableExtra::column_spec(2, width = "4em") %>%     
+    kableExtra::column_spec(c(3, 6), width = "11em") %>% 
     kableExtra::column_spec(5, width = "5em")
@@
 
-pge_items_table(1:7) %>%
+pge_items_table(1:2) %>%
   kableExtra::kable_styling(latex_options = "HOLD_position")
@@
 ```{r pge_items_table2}    
-pge_items_table(8:14)
+pge_items_table(3:10)
 ```
@@
 ```{r pge_items_table3}    
-pge_items_table(15:23)
+pge_items_table(11:15)
 ```
@@
 ```{r pge_items_table4}    
-pge_items_table(24:30)
+pge_items_table(16:24)
 ```
@@
 ```{r pge_items_table5}    
-pge_items_table(31:41)
+pge_items_table(25:32)
 ```
 
-\pagebreak
 ```{r pge_items_table6}    
-pge_items_table(42:50)
+pge_items_table(33:39)
 ```
 
-\pagebreak
+```{r pge_items_table7}    
+pge_items_table(40:51) %>%
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
 ```{r obs_by_cy, fig.height = 9, fig.width = 6.5, fig.cap = "Source Data Observations by Country and Year \\label{obs_by_cy}"}
@@
         axis.text.y  = element_text(size = 7)) 
-```
-
-```{r obs_by_item2, fig.height = 9, fig.width = 6.5, fig.cap = "Joint Observations in the Source Data for Each Pair of Items \\label{obs_by_item2}"}
-items_by_obs <- dcpo_input_raw_poliwork1 %>%
-  distinct(country, year, item) %>%
-  count(item, name = "n_obs") %>%
-  arrange(desc(n_obs))
-
-dcpo_input_raw_poliwork1 %>% 
-  group_by(country, year, item) %>%
-  mutate(n = sum(n)) %>% 
-  distinct(country, year, item, n) %>% 
-  pivot_wider(names_from = "item", values_from = "n") %>% 
-  ungroup() %>% 
-  select(-country, -year) %>% 
-  psych::pairwiseCount() %>% 
-  as.data.frame() %>%
-  rownames_to_column(var = "item") %>% 
-  left_join(items_by_obs) %>%  
-  arrange(-n_obs) %>% 
-  select(item, any_of(items_by_obs %>% pull(item)), n_obs) %>% 
-  pivot_longer(cols = matches("\\d.?$"), names_to = "var2", values_to = "count") %>%
-  filter(count > 0) %>% 
-  mutate(item = forcats::fct_reorder(item, n_obs),
-         var2 = forcats::fct_relevel(var2, rev(levels(item)))) %>% 
-  ggplot(aes(x = var2, 
-             y = item,
-             fill = count)) + 
-  geom_tile() +
-  scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
-                    breaks = c(0, 1, 10, 20, 30, 50, 100),
-                    show.limits = TRUE,
-                    right = FALSE,
-                    trans = "log10",
-                    name = "Joint\nObservations") +
-  labs(x = NULL, y = NULL) +
-  theme(axis.text.x  = element_text(angle = 90, vjust = .5))
 ```

### 2022-03-23 paper/response_memo.Rmd
address #27

@@
 Thank you for your helpful comments, as well as your general enthusiasm for this piece.
-We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the text:
+We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the article:
 
@@
 
+1. **Validating Public Gender Egalitarianism** R2 also advicated including more examples of the questions we used in the text rather than relegating all of them to the appendix.
+We are glad for this suggestion.
+Our new discussion of how the model addresses the incomparabilty of different survey items found on page 4 provided a good opportunity to bring in some specific illustrative examples.
+
 1.
@@
 This is an important question.
-The DCPO model introduced in @Solt2020c that we employ here---as well as the models presented in @Claassen2019 that R1 referenced in making this point---was specifically designed for when survey data on the topic of interest is not available for all years in all countries, a problem referred to as sparsity.
-So we actually do have PGE estimates for country-years for which there is no source survey data available---and, more generally, the $k$-fold cross-validations presented in @Solt2020c [, 10-12] show that estimates generated by the DCPO model in such circumstances are very good.
+The DCPO model introduced in @Solt2020c that we employ here---as well as the models presented in @Claassen2019 that R1 referenced in making this point---was specifically designed to address the situation when survey data on the topic of interest is not available for all years in all countries.
+This, and the related issue R1 raised about estimates based on only one or two  is the problem referred to as sparsity.
+By using the DCPO model, then, we actually do have PGE estimates for country-years for which there is no source survey data available---and, more generally, the $k$-fold cross-validations presented in @Solt2020c [, 10-12] show that estimates generated by the DCPO model when there is no source data are very good: estimates for excluded source data on average differ from their actual values by only 5.5 percentage points, with more than 75% of the actual values falling within the estimated 80% confidence intervals.
 We have added a paragraph specifically addressing how this model deals with sparsity to ensure this point is clear to readers at pages 4-5.
+
+1. **Estimating Public Gender Egalitarianism** R1 also raised the related issue of estimates based on only one or two survey items.
+This is another, though less dire, example of sparsity.
+As discussed above, the DCPO model does a very good job of dealing with sparse data.
+Again, we discuss sparsity at pages 4-5.
+For interested readers interested, we also plot the number of observed items for each country-year in Figure A1 in Appendix A.
 
@@
 
-We also took advantage of the opportunity to add more source data...
+1. **Validating Public Gender Egalitarianism** R2 asked us for more clarity on which questions we were using to generate the PGE estimates and which were only used for external validation checks.
+We worked to reinforce throughout the piece that the 'source-data' questions---those asking about gender roles in the public sphere of politics and the workplace---are the ones we used to generate estimates.
+We were particularly careful to underscore in this section that our internal test of convergent validation depicted in Figure 5 uses source-data items and that the initial test of construct validation shown in Figure 6 uses items _not_ used to generate the PGE estimates.
+
+1. **Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism and Their Distribution** R1 and R2 both raised the issue of overlap and bridging among the survey items in the source data.
+Bridging and overlap have not been a concern in the literature on generating latent-variable estimates of public opinion across countries and over time from sparse data [see @Claassen2019; @Caughey2019; @Solt2020].
+This is largely, we think, because the dynamic aspect of the models, that is, the random-walk prior that links the estimate for each country-year to the one before and the one following, are considered to do the work to tie together items that do not overlap (although this surely leads to increased uncertainty in these items' parameters for dispersion and difficulty).
+Still, the most commonly observed item in our source data, `polileader4` ("On the whole, men make better political leaders than women do"), effectively serves as the bridge between the other items: it overlaps with 39 of the other 50 items, which together cover 91% of the observed country-years, and only a single item (covering 22 country-years) had no observations within a year of a `polileader4` observation.
+We have included a short discussion of overlap and bridging in Appendix A.
+
+We also took advantage of the opportunity to add more source data, increasing the number of observed country-year-items from 2,710 to 2,999.
+As we wrote at page 11, we will continue to update the source data and the PGE estimates as more data become available.
 

### 2022-03-25 paper/pge_appendix.Rmd
fix cite

@@
 
-Overlap among items have not been a concern in the literature on generating latent-variable estimates of public opinion across countries and over time from sparse data, largely because the dynamic aspect of the models employed, that is, the random-walk prior, works to tie together items that do not overlap [see @Claassen2019; @Caughey2019; @Solt2020].
+Overlap among items have not been a concern in the literature on generating latent-variable estimates of public opinion across countries and over time from sparse data, largely because the dynamic aspect of the models employed, that is, the random-walk prior, works to tie together items that do not overlap [see @Claassen2019; @Caughey2019; @Solt2020c].
 Nevertheless, the most commonly observed item in the PGE source data, `polileader4`, effectively serves as the bridge between the other items: it has overlapping country-year observations with 39 of the other 50 items (which together cover 91% of the observed country-years), and only a single item (`politics4a`, which covers 22 country-years) had no observations within a year of a `polileader4` observation.

### 2022-03-25 paper/response_memo.Rmd
clean up

@@
 
-Thank you for your helpful comments, as well as your general enthusiasm for this piece.
+Thank you for your helpful comments, as well as your general enthusiasm for this piece and the dataset it presents.
 We set out a list of the specific points raised in the reviews and our responses to them below, roughly in the order they appear in the article:
@@
 1. **Appendix A: Survey Items Used to Estimate Public Gender Egalitarianism and Their Distribution** R1 and R2 both raised the issue of overlap and bridging among the survey items in the source data.
-Bridging and overlap have not been a concern in the literature on generating latent-variable estimates of public opinion across countries and over time from sparse data [see @Claassen2019; @Caughey2019; @Solt2020].
+Bridging and overlap have not been a concern in the literature on generating latent-variable estimates of public opinion across countries and over time from sparse data [see @Claassen2019; @Caughey2019; @Solt2020c].
 This is largely, we think, because the dynamic aspect of the models, that is, the random-walk prior that links the estimate for each country-year to the one before and the one following, are considered to do the work to tie together items that do not overlap (although this surely leads to increased uncertainty in these items' parameters for dispersion and difficulty).

### 2022-03-25 paper/dcpo_gender_roles.Rmd
clean up

@@
 These PGE scores are strongly correlated with responses to individual survey items and with women's rates of participation in the labor force and corporate boards.
-We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in the public sphere.
-[148/150 words]"
+We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in politics and the economy.
+[149/150 words]"
 keywords: "gender roles, gender inequality, public opinion, political culture, measurement"
@@
 One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the quantified uncertainty in the estimates.
-But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2021] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
+But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2022] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
 Therefore, taking the uncertainty in the PGE scores into account is crucial to reaching well-grounded conclusions.

### 2022-03-27 paper/dcpo_gender_roles.Rmd
update

@@
 - name: Byung-Deuk Woo
-  affiliation: University of Iowa
-- name: Lindsey Allemang
-  affiliation: University of Iowa
+  affiliation: Pohang University of Science and Technology
+- name: Lindsey A. Goldberg
+  affiliation: University of Florida
 - name: Frederick Solt
   affiliation: University of Iowa
-anonymous: true
+anonymous: false
 abstract: "Societal attitudes toward gender roles in the workplace and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories.

### 2022-04-16 paper/pge_appendix.Rmd
use 'Supplementary Materials' in title

@@
 ---
-title: 'Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative
+title: 'Supplementary Materials to Public Gender Egalitarianism: A Dataset of Dynamic Comparative
   Public Opinion Toward Egalitarian Gender Roles in the Public Sphere'
@@
 
-\renewcommand{\thepage}{A\arabic{page}}
+\renewcommand{\thepage}{S\arabic{page}}
 \setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
+\renewcommand{\thefigure}{S\arabic{figure}}
 \setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\thetable}{S\arabic{table}}
 
